---
title: "Aleah's Proposal"
author: "Kelsey Sanchez"
date: "`r Sys.Date()`"
header-includes:  
  \usepackage[labelformat=empty]{caption}
  \usepackage{placeins}
  \usepackage{booktabs}
  \usepackage{pdflscape}


output:
  pdf_document:
    extra_dependencies: ["float"]
    toc: true
    keep_tex: yes
    fig_width: 7
    fig_height: 5
    fig_caption: true
    df_print: paged 

---


This report compares the counts of successful digital, traditional, and other marketing tactics across different demographics and analyses the significance of their differences. 

Digital marketing recruitment methods include: Connect Web, IHCS Web, Email/Text Invite, Patient Portal Invite, Social Media Post, IHCS Newsletter, and Video. 

Traditional marketing recruitment methods include: Mailed Letter, Phone Invite, Dr/Staff, Connect Staff at IHCS, Connect in News, Local News/TV/Radio, Family/Friend, Another Participant, Poster at IHCS, Table at Event, Recorded Message. 

Those who did not answer how they heard about the study, as well as those who only selected 'other' recruiting methods, are excluded.

```{r libraries, include=FALSE}

#All libraries are listed up top; authentication for BQ will be necessary.
#Functions used included before the start of the analysis .
#Currently filtered by gender, and will eventually be done by age groups as well (D_117249500).



rm(list = ls())
library(bigrquery)
library(foreach)
library(stringr)
#library(plyr)
#library(expss) ###to add labels
library(epiDisplay) ##recommended applied here crosstable, tab1
library(gmodels) ##recommended
library(magrittr)
library(arsenal)
library(gtsummary)
library(rio)



library(ggplot2)
library(gridExtra)
library(scales)
library(gt)
#install(tinytex)
library(tinytex)
library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(reshape)  ###to work on transition from long to wide or wide to long data
library(listr) ###to work on a list of vector, files or..
library(sqldf) ##sql
library(lubridate) ###date time
library(stringr) ###to work on patterns, charaters
library(kableExtra)
library(janitor)


options(tinytex.verbose = TRUE)

bq_auth()
```


```{r M1merge, include=FALSE}


## Pull in both versions of Mod1, merge together, and merge in demogrpahic variables from participants table

dictionary <- rio::import("https://episphere.github.io/conceptGithubActions/aggregate.json",format = "json")
dd <- dplyr::bind_rows(dictionary,.id="CID")
dd <-rbindlist(dictionary,fill=TRUE,use.names=TRUE,idcol="CID")
dd$`Variable Label`[is.na(dd$`Variable Label`)] <- replace_na(dd$'Variable Name')

dd <- as.data.frame.matrix(do.call("rbind",dictionary)) 
dd$CID <- rownames(dd)
#https://shaivyakodan.medium.com/7-useful-r-packages-for-analysis-7f60d28dca98
devtools::install_github("tidyverse/reprex")

project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" ##project and billing should be consistent
##517311251 Date/time Status of Completion of Background and Overall Health                         SrvBOH_TmComplete_v1r0
##949302066 Flag for Baseline Module Background and Overall Health                        SrvBOH_BaseStatus_v1r0
recr_M1 <- bq_project_query(project, query="SELECT token,Connect_ID, d_821247024, d_914594314,  d_827220437,d_512820379,
                            d_949302066 , d_517311251  FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` WHERE  d_821247024='197316935' and d_949302066 ='231311385'")
recr_m1 <- bq_table_download(recr_M1,bigint = "integer64")
cnames <- names(recr_m1)
# Check that it doesn't match any non-number
numbers_only <- function(x) !grepl("\\D", x)
# to check variables in recr_noinact_wl1
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(recr_m1,varname)
  recr_m1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}

sql_M1_1 <- bq_project_query(project, query="SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v1_JP` where Connect_ID is not null")
sql_M1_2 <- bq_project_query(project, query="SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2_JP` where Connect_ID is not null")


M1_V1 <- bq_table_download(sql_M1_1,bigint = "integer64") #1436 #1436 vars: 1507 01112023 
M1_V2 <- bq_table_download(sql_M1_2,bigint = "integer64") #2333 #3033 01112023 var:1531 #6339 obs 1893 vars 05022023

mod1_v1 <- M1_V1
cnames <- names(M1_V1)
###to check variables and convert to numeric
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(mod1_v1,varname)
  mod1_v1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}
mod1_v2 <- M1_V2
cnames <- names(M1_V2)
###to check variables and convert to numeric
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(mod1_v2,varname)
  mod1_v2[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}

M1_V1.var <- colnames(M1_V1)
M1_V2.var <- colnames(M1_V2)
var.matched <- M1_V1.var[which(M1_V1.var %in% M1_V2.var)]
length(var.matched)  #1275 #1278 vars 01112023 #1348 vars 05022023

V1_only_vars <- colnames(M1_V1)[colnames(M1_V1) %nin% var.matched] #232 #229 01112023 #159 05022023
V2_only_vars <- colnames(M1_V2)[colnames(M1_V2) %nin% var.matched] #253 #253 01112023 #545 05022023

length(M1_V1$Connect_ID[M1_V1$Connect_ID %in% M1_V2$Connect_ID])
#[1] 59 with the completion of two versions of Module1 
#[1] 62 with completing both versions of M1 ###double checked 03/28/2023
#68 double checked 05/02/2023

common.IDs <- M1_V1$Connect_ID[M1_V1$Connect_ID %in% M1_V2$Connect_ID]
M1_V1_common <- mod1_v1[,var.matched]

M1_V2_common <- mod1_v2[,var.matched]
M1_V1_common$version <- 1
M1_V2_common$version <- 2

##to check the completion of M1 among these duplicates
partM1_dups <- recr_m1[which(recr_m1$Connect_ID %in% common.IDs),]
table(partM1_dups$d_949302066)

M1_common  <- rbind(M1_V1_common, M1_V2_common) #including 136 duplicates (version 1 and version 2) from 68 participants 05022023
#M1_response <- matrix(data=NA, nrow=118, ncol=967)

m1_v1_only <- mod1_v1[,c("Connect_ID", V1_only_vars)] #230 vars 03282023 #160 vars 05/02/2023
m1_v2_only <- mod1_v2[,c("Connect_ID", V2_only_vars)] #255 vars 03282023 #546 vars 05/02/2023
m1_v1_only$version <- 1
m1_v2_only$version <- 2
#for (i in 1:length)
##to check the completion in each version
length(recr_m1$Connect_ID[which(recr_m1$Connect_ID %in% m1_v1_only$Connect_ID & recr_m1$d_949302066 ==231311385)]) #1364 03282023 # 1370 05022023
length(recr_m1$Connect_ID[which(recr_m1$Connect_ID %in% m1_v2_only$Connect_ID & recr_m1$d_949302066 ==231311385)]) #4870 03282023 # 5731 05022023

#library(janitor)

m1_common <- rbind(M1_V1_common,M1_V2_common)
m1_common_v1 <- base::merge(m1_common, m1_v1_only, by=c("Connect_ID","version"),all.x=TRUE)
m1_combined_v1v2 <- base::merge(m1_common_v1,m1_v2_only,by=c("Connect_ID","version"),all.x=TRUE)
m1_complete <- m1_combined_v1v2[which(m1_combined_v1v2$Connect_ID %in% recr_m1$Connect_ID[which(recr_m1$d_949302066 ==231311385 )]),] #7289 including duplicates 05022023

m1_complete <- m1_complete %>% arrange(desc(version)) 


m1_complete_nodup <- m1_complete[!duplicated(m1_complete$Connect_ID),] 
table(m1_complete_nodup$version)



demo <- "SELECT 
Connect_ID, token,
d_827220437, state_d_706256705, state_d_934298480, d_142654897_d_177402915, d_142654897_d_196856782, d_142654897_d_206879104, d_142654897_d_241590841, d_142654897_d_285130077, d_142654897_d_326825649, d_142654897_d_461488577, d_142654897_d_462314689, d_142654897_d_520301146, d_142654897_d_549687190, d_142654897_d_607081902, d_142654897_d_639721694, d_142654897_d_642287621, d_142654897_d_684726272, d_142654897_d_791389099, d_142654897_d_819377306, d_142654897_d_829269606, d_142654897_d_942255248, d_142654897_d_967372009, d_335767902, d_914594314, state_d_849518448, state_d_706256705, d_949302066,
d_512820379
 FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` where d_919254129= '353358909' and d_821247024='197316935'"
demo_table <- bq_project_query(project, demo)
site_demographics <- bq_table_download(demo_table, bigint = "integer64")

site_demographics$Connect_ID <- as.numeric(site_demographics$Connect_ID) ###need to convert type- m1... is double and demo is character

proposal= left_join(m1_complete_nodup, site_demographics, by="Connect_ID") 
dim(proposal)
```



```{r labeling, warning=FALSE, echo=FALSE, message=FALSE}


# Creating and labeling the demogrpahics 


#Race
multi_race=0    
for (i in 1:length(proposal$Connect_ID)){
  AI=ifelse((proposal$D_384191091_D_384191091_D_583826374[[i]]==1 & (proposal$D_384191091_D_384191091_D_636411467[[i]]==1 | proposal$D_384191091_D_384191091_D_458435048[[i]]==1|
                                                                      proposal$D_384191091_D_384191091_D_706998638[[i]]==1 | proposal$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_586825330[[i]]==1 | proposal$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  As=ifelse((proposal$D_384191091_D_384191091_D_636411467[[i]]==1 & (proposal$D_384191091_D_384191091_D_583826374[[i]]==1 | proposal$D_384191091_D_384191091_D_458435048[[i]]==1|
                                                                      proposal$D_384191091_D_384191091_D_706998638[[i]]==1 | proposal$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_586825330[[i]]==1 | proposal$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Bl=ifelse((proposal$D_384191091_D_384191091_D_458435048[[i]]==1 & (proposal$D_384191091_D_384191091_D_583826374[[i]]==1 | proposal$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                                      proposal$D_384191091_D_384191091_D_706998638[[i]]==1 | proposal$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_586825330[[i]]==1 | proposal$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Hs=ifelse((proposal$D_384191091_D_384191091_D_706998638[[i]]==1 & (proposal$D_384191091_D_384191091_D_583826374[[i]]==1 | proposal$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                                      proposal$D_384191091_D_384191091_D_458435048[[i]]==1 | proposal$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_586825330[[i]]==1 | proposal$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Me=ifelse((proposal$D_384191091_D_384191091_D_973565052[[i]]==1 & (proposal$D_384191091_D_384191091_D_583826374[[i]]==1 | proposal$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                                      proposal$D_384191091_D_384191091_D_458435048[[i]]==1 | proposal$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_586825330[[i]]==1 | proposal$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Hw=ifelse((proposal$D_384191091_D_384191091_D_586825330[[i]]==1 & (proposal$D_384191091_D_384191091_D_583826374[[i]]==1 | proposal$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                                      proposal$D_384191091_D_384191091_D_458435048[[i]]==1 | proposal$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_973565052[[i]]==1 | proposal$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Wh=ifelse((proposal$D_384191091_D_384191091_D_412790539[[i]]==1 & (proposal$D_384191091_D_384191091_D_583826374[[i]]==1 | proposal$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                                      proposal$D_384191091_D_384191091_D_458435048[[i]]==1 | proposal$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_586825330[[i]]==1 | proposal$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Ot=ifelse((proposal$D_384191091_D_384191091_D_807835037[[i]]==1 & (proposal$D_384191091_D_384191091_D_583826374[[i]]==1 | proposal$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                                      proposal$D_384191091_D_384191091_D_458435048[[i]]==1 | proposal$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_586825330[[i]]==1 | proposal$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                                      proposal$D_384191091_D_384191091_D_412790539[[i]]==1)), 1, 0)
  multi_race= multi_race + sum(AI+As+Bl+Hs+Me+Hw+Wh+Ot, na.rm=T)
  
}



proposal$multi_racial <- c(rep(1, times=multi_race), rep(0, times=(dim(proposal)[1]- multi_race)))


proposal= proposal %>%  mutate(Race= case_when(multi_racial==1 ~ "Multi-Racial",
                                                    D_384191091_D_384191091_D_583826374==1 ~ "American Indian or Native American",
                                                    D_384191091_D_384191091_D_636411467==1 ~ "Asian/Asian American",
                                                    D_384191091_D_384191091_D_458435048==1 ~ "Black, African American, or African",
                                                    D_384191091_D_384191091_D_706998638==1 ~ "Hispanic, Latino, or Spanish",
                                                    D_384191091_D_384191091_D_973565052==1 ~ "Middle Eastern or North African",
                                                    D_384191091_D_384191091_D_586825330==1 ~ "Hawaiian or Pacific Islander",
                                                    D_384191091_D_384191091_D_412790539==1 ~ "White",
                                                    #D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Other",
                                                    #D_384191091_D_384191091_D_746038746==1 ~ "Prefer Not to Answer",
                                                    TRUE  ~ "Unknown"),
                               Income= case_when(D_759004335==209571450 ~ "35,000-49,000",
                                                  D_759004335==212249150 ~ "50,000-74,000",
                                                  D_759004335==374508062 ~ "0-9,000",
                                                  #D_759004335==530094502 ~ "Error- Unlisted Response Selected", 
                                                  D_759004335==742032816 ~ "200,000+", 
                                                  D_759004335==745561936 ~ "25,000-34,000",
                                                  #D_759004335==746038746 ~ "Prefer not to Answer",
                                                  D_759004335==777814771 ~ "75,000-99,000", 
                                                  D_759004335==913602274 ~ "150,000-199,000", 
                                                  D_759004335==922395188 ~ "100,000-149,000",
                                                  D_759004335==976555124 ~ "10,000-24,000",
                                                  #D_759004335==178420302 ~ "Unknown",
                                                  TRUE ~ "Prefer Not to Answer or Unknown"),
                               Education= case_when(D_367803647_D_367803647==978204320 ~ "Grade School(Grades 1-8)",
                                                  D_367803647_D_367803647==935502060 ~ "Some High School, No Diploma",
                                                  D_367803647_D_367803647==404564707 ~ "High School Graduate or GED",
                                                  D_367803647_D_367803647==432193665 ~ "Some College, No Degree",
                                                  D_367803647_D_367803647==890756124 ~ "Technical or Trade School After High School",
                                                  D_367803647_D_367803647==766964355 ~ "Associate's Degree",
                                                  D_367803647_D_367803647==875342283 ~ "Bachelor's Degree",
                                                  D_367803647_D_367803647==598242454 ~ "Advanced Degree",
                                                  #D_367803647_D_367803647==807835037 ~ "Other",
                                                  TRUE ~ "Prefer Not to Answer or Unknown"),
                               Sex = case_when(D_407056417 == 536341288 ~ "Female",
                                               D_407056417 == 654207589 ~ "Male",
                                               D_407056417 == 576796184 ~ "Intersex or Other",
                                               TRUE ~ "Unknown"),
                        Age = case_when(state_d_934298480 == 713781738 ~ "30-34",
                                        state_d_934298480 == 631272782 ~ "35-39",
                                        state_d_934298480 == 124276120 ~ "40-45",
                                        state_d_934298480 == 450985724 ~ "46-50",
                                        state_d_934298480 == 363147933 ~ "51-55",
                                        state_d_934298480 == 636706443 ~ "56-60",
                                        state_d_934298480 == 771230670 ~ "61-65",
                                        state_d_934298480 == 722846087 ~ "66-70"),
                        Site= case_when(d_827220437 == 531629870 ~ "HealthPartners", 
                                        d_827220437 ==548392715 ~ "Henry Ford Health System", 
                                        d_827220437 == 125001209 ~ "Kaiser Permanente Colorado",
                                        d_827220437 == 327912200 ~ "Kaiser Permanente Georgia",
                                        d_827220437 == 300267574 ~ "Kaiser Permanente Hawaii",
                                        d_827220437 == 452412599 ~ "Kaiser Permanente Northwest",
                                        d_827220437 == 303349821 ~ "Marshfield Clinic Health System",
                                        d_827220437 == 657167265 ~ "Sanford Health", 
                                        d_827220437 == 809703864 ~ "University of Chicago Medicine",
                                        d_827220437 == 517700004 | d_827220437 == 13 ~ "National Cancer Institute",
                                        TRUE ~ "Unknown"),
                        Recruit = case_when(d_512820379==486306141 ~ "Active",
                                            TRUE ~ "Passive")) %>%  filter(Sex!="Unknown" & Race!="Unknown")

proposal$Income <- factor(proposal$Income,levels=c("0-9,000","10,000-24,000","25,000-34,000","35,000-49,000","50,000-74,000","75,000-99,000","100,000-149,000","150,000-199,000",
                                         "200,000+","Prefer Not to Answer or Unknown"))
proposal$Education <- factor(proposal$Education,levels=c("Grade School(Grades 1-8)", "Some High School, No Diploma", "High School Graduate or GED","Some College, No Degree","Technical or Trade School After High School","Associate's Degree","Bachelor's Degree","Advanced Degree", "Prefer Not to Answer or Unknown"))
proposal$Age <- factor(proposal$Age,levels=c("30-34","35-39","40-45","46-50","51-55","56-60","61-65","66-70"))
proposal$Sex <- factor(proposal$Sex,levels=c("Female","Male","Intersex or Other"))



```



\newpage
# Module 1 Completed: All demographics defined
\FloatBarrier

```{r tables_sepatated, warning=FALSE, echo=FALSE, message=FALSE, results='asis'}

#Aleah needs these to be consented participants only with All consented participants from the start of recruitment in June 2021 until March 1st, 2024.


#Dates refer to verification date
proposal_aleah <- proposal %>%  filter( as.Date(d_914594314) < "2024-03-02")


#digital includes:  Connect Web, IHCS Web, Email/Text Invite, Patient Portal, Social Media Post, IHCS Newsletter, Video
#traditional includes: Mailed Letter, Phone Invite, Dr/Staff, Connect Staff at IHCS, Connect in News, Local News/TV/Radio, Family/Friend, Another Participant, Poster at IHCS, Table at Event, Recorded Message
# For the those who selected “other”, see if those people selected a traditional and/or digital option. If they did select one of those options, count them in the respective group. If the only option they selected is “other”, then we can drop the from the analysis.
proposal_aleah <- proposal_aleah %>%  mutate(marketing = case_when(((d_142654897_d_461488577==353358909 | d_142654897_d_607081902==353358909 |
                                                                      d_142654897_d_241590841==353358909 | d_142654897_d_206879104==353358909 |
                                                                      d_142654897_d_642287621==353358909 | d_142654897_d_285130077==353358909|
                                                                      d_142654897_d_684726272==353358909) &
                                                                   (d_142654897_d_942255248==353358909 | d_142654897_d_639721694==353358909 |
                                                                      d_142654897_d_196856782==353358909 | d_142654897_d_177402915==353358909 |
                                                                      d_142654897_d_791389099==353358909 | d_142654897_d_520301146==353358909|
                                                                      d_142654897_d_549687190==353358909 | d_142654897_d_326825649==353358909 | 
                                                                      d_142654897_d_819377306==353358909 | d_142654897_d_829269606==353358909 |
                                                                      d_142654897_d_967372009==353358909)) ~ "Both",
                                                                    (d_142654897_d_461488577==353358909 | d_142654897_d_607081902==353358909 |
                                                                      d_142654897_d_241590841==353358909 | d_142654897_d_206879104==353358909 |
                                                                      d_142654897_d_642287621==353358909 | d_142654897_d_285130077==353358909|
                                                                      d_142654897_d_684726272==353358909)~ "Digital",
                                                                   (d_142654897_d_942255248==353358909 | d_142654897_d_639721694==353358909 |
                                                                      d_142654897_d_196856782==353358909 | d_142654897_d_177402915==353358909 |
                                                                      d_142654897_d_791389099==353358909 | d_142654897_d_520301146==353358909|
                                                                      d_142654897_d_549687190==353358909 | d_142654897_d_326825649==353358909 | 
                                                                      d_142654897_d_819377306==353358909 | d_142654897_d_829269606==353358909 |
                                                                      d_142654897_d_967372009==353358909)~ "Traditional",
                                                                  TRUE ~ "Skipped")) %>%  filter(marketing!="Skipped")




# 11577  digital
# 12589  traditional
# 2407 both




proposal_aleah$marketing <- factor(proposal_aleah$marketing,levels=c("Digital","Traditional", "Both"))

# Define your demographic variables
demographics <- c("Age", "Race", "Sex", "Income", "Education", "Site")

#Don't want both in chi squaured test 
#proposal_aleah2 <- proposal_aleah %>%  filter(marketing!="Both")
#proposal_aleah2$marketing <- factor(proposal_aleah2$marketing,levels=c("Digital","Traditional"))

# Loop through each demographic
for (demo in demographics) {

  #Remove 'both; for chi squared
proposal_aleah2 <- proposal_aleah %>%  filter(marketing!="Both")
proposal_aleah2$marketing <- factor(proposal_aleah2$marketing,levels=c("Digital","Traditional"))

### Need one table stratified by recruitment status and chi squared with it  
  active_data <- proposal_aleah %>%
    filter(Recruit == "Active")
  
  passive_data <- proposal_aleah %>%
    filter(Recruit == "Passive")
  
  # Generate cross-tabulation
  compare_active <- active_data %>%
    tbl_cross(
      row = !!sym(demo),
      col = marketing,
      label = list(marketing ~ "Recruitment Strategies", !!sym(demo) ~ demo),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total Consented Recruits"
    )
  
   compare_passive <- passive_data %>%
    tbl_cross(
      row = !!sym(demo),
      col = marketing,
      label = list(marketing ~ "Recruitment Strategies", !!sym(demo) ~ demo),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total Consented Recruits"
    )
   

compare_combined <- cbind(as.data.frame(compare_active), as.data.frame(compare_passive))
colnames(compare_combined)[1] <- demo
colnames(compare_combined)[6] <- demo
compare_combined <- compare_combined[c(-1),]
   
   
compare_combined_table <- knitr::kable(compare_combined,caption=paste0("Self-reported Recruitment Strategies Among Self-reported ", demo, "\n Stratefied by Recruitment Status"), row.names=FALSE, booktabs = T, linesep = "", format.args = list(big.mark = ","), align = c("l", "c", "c","c", "c", "c", "c", "c", "c", "c")) %>% kable_styling(latex_options = "scale_down")  %>% add_header_above(c(" "=1, "Recruitment Strategies" =3, " " = 2,"Recruitment Strategies" =3, " " = 1 )) %>%  add_header_above(c("Active Participants" = 5, "Passive Participants" = 5))  %>% landscape() 

   
   


    active_data2 <- proposal_aleah2 %>%
    filter(Recruit == "Active")

  passive_data2 <- proposal_aleah2 %>%
    filter(Recruit == "Passive")

  chi_active <- chisq.test(table(active_data2[[demo]], active_data2$marketing))
  chi_passive <- chisq.test(table(passive_data2[[demo]], passive_data2$marketing))
  
foot_note <- paste("Note: With a p-value of", 
                    ifelse(chi_active$p.value < 0.05, (paste0("< 0.05 for active recruits,  we have evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, ".")),(paste0(" over 0.05, we have no evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, "."))))
  
# foot_note2 <- paste("Note: With a p-value of",
#                     ifelse(chi_passive$p.value < 0.05, (paste0("< 0.05 for passive recruits,  we have evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, ".")),(paste0(" over 0.05, we have no evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, "."))))

if (!is.na(chi_passive$p.value)) {
  if (chi_passive$p.value < 0.05) {
    foot_note2 <- paste("Note: With a p-value of < 0.05 for passive recruits, we have evidence that there is a significance in the difference of digital marketing success and traditional marketing success by", demo, ".")
  } else if (chi_passive$p.value >= 0.05) {
    foot_note2 <- paste("Note: With a p-value of over 0.05 for passive recruits, we have no evidence that there is a significance in the difference of digital marketing success and traditional marketing success by", demo, ".")
  } else {
    foot_note2 <- paste("Note: With a p-value of NA for passive recruits, a Fischer's exact test may provide better results.")
  }
} else {
  foot_note2 <- "Note: With a p-value of NA for passive recruits, a Fischer's exact test may provide better results."
}
   
foot_note3 <-  paste("Those who selected both Recruitment Strategies were removed from the chi-squared analysis.")
                    
  
  compare_combined_table <- add_footnote(compare_combined_table, foot_note, notation = "none")
    compare_combined_table <- add_footnote(compare_combined_table, foot_note2, notation = "none")
        compare_combined_table <- add_footnote(compare_combined_table, foot_note3, notation = "none")
  
  # Print or save the table as desired
  print(compare_combined_table)
  
  
  
  
  
 #### Then need one table with all recruit status and chi squared
  compare_all <- proposal_aleah %>%
    tbl_cross(
      row = !!sym(demo),
      col = marketing,
      label = list(marketing ~ "Recruitment Strategies", !!sym(demo) ~ demo),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total Consented Recruits"
    )
  
compare_all <- compare_all %>%
  #bold_labels() %>%
  #italicize_levels() %>%
  modify_header() %>%
  modify_caption(paste0("Self-reported Recruitment Strategies Among Self-reported ", demo)) %>% ## used to be Table 8
  as_kable_extra() %>% kable_styling(latex_options = "scale_down")


chi <- chisq.test(table(proposal_aleah2[[demo]], proposal_aleah2$marketing))

footnote <- ifelse(chi$p.value < 0.05,
                   paste0("With a p-value of < 0.05 we have evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, "."),
                   paste0("With a p-value over 0.05, we have no evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, "."))


compare_all <- add_footnote(compare_all, footnote)

print(compare_all)

  
  
  
  
  
  
  
  
  
  
  
  
}
  



```


```{r}


methods <- c("d_142654897_d_461488577","d_142654897_d_607081902","d_142654897_d_241590841","d_142654897_d_206879104","d_142654897_d_642287621 ","d_142654897_d_285130077",
              "d_142654897_d_684726272","d_142654897_d_942255248", "d_142654897_d_639721694","d_142654897_d_196856782", "d_142654897_d_177402915","d_142654897_d_791389099", 
             "d_142654897_d_520301146","d_142654897_d_549687190", "d_142654897_d_326825649", "d_142654897_d_819377306", "d_142654897_d_829269606","d_142654897_d_967372009")
# Remove leading or trailing spaces from method names
methods <- trimws(methods)

# Define the list of demographics
demographics <- c("Age", "Race", "Sex", "Income", "Education", "Site")

# Initialize an empty list to store results
all_results <- list()



# Iterate over each demographic
for (demo in demographics) {
  # Initialize an empty list to store results for the current demographic
  result_list <- list()
  
  # Iterate over each method
  for (method in methods) {
    # Subset the data to include only rows where the current method is 353358909
    subset_data <- subset(proposal_aleah, get(method) == 353358909)
    
    # Use table() to get counts of each demographic category
    counts <- table(subset_data[[demo]])
    
    # Store the result in the list
    result_list[[method]] <- counts
  }
  
  # Combine all results for the current demographic into a single data frame
  final_result <- as.data.frame(do.call(cbind, result_list))
    colnames(final_result) <- methods
  
  # Add demographic category as a column
  final_result[[demo]] <- row.names(final_result)
  
  # Reorder the columns
  final_result <- final_result[, c(demo, methods)]
  
  # Rename the columns to match DD
   colnames(final_result) <- c(demo, "Email/Text Invite","Patient Portal Invite","IHCS Web","Connect Web","Social Media Post", "Video", "IHCS Newsletter","Mailed Letter", "Phone Invite", "Dr/Staff", "Connect Staff at IHCS", "Connect in News",  "Local News/TV/Radio","Family/Friend", "Another Participant", "Poster at IHCS", "Table at Event","Recorded Message")
  
   # Add a row for total counts and percentage
  total_counts <- colSums(final_result[, 2:ncol(final_result)])
  total_percentage <- round((total_counts / nrow(proposal_aleah)) * 100, 1)
  total_row <- c("Total", paste(total_counts, " (", total_percentage, "%)", sep = ""))
  final_result <- rbind(final_result, total_row)
  
   # Save the result as a CSV file
  file_name <- paste0(demo, "_counts.csv")
  write.csv(final_result, file = file_name, row.names = FALSE)
  
  # Store the result for the current demographic in the overall list
  all_results[[demo]] <- final_result
}

# Print the results for all demographics
for (demo in demographics) {
  print(all_results[[demo]])
}




```



\FloatBarrier
\newpage
\newpage
# Module 1 not completed: Site defined demographics
\vspace{-0.5em}
\FloatBarrier

```{r site_labeling_separated, warning=FALSE, echo=FALSE, message=FALSE}



#digital includes:  Connect Web, IHCS Web, Email/Text Invite, Patient Portal, Social Media Post, IHCS Newsletter, Video
#traditional includes: Mailed Letter, Phone Invite, Dr/Staff, Connect Staff at IHCS, Connect in News, Local News/TV/Radio, Family/Friend, Another Participant, Poster at IHCS, Table at Event, Recorded Message
# For the those who selected “other”, see if those people selected a traditional and/or digital option. If they did select one of those options, count them in the respective group. If the only option they selected is “other”, then we can drop the from the analysis.

site_demographics= site_demographics %>%  filter(d_949302066 !=231311385) %>% 
                                mutate(Race= case_when(state_d_849518448==768826601 ~ "White, Non-Hispanic",
                                                       TRUE ~ "Other/Unknown"),
                                                       #state_d_849518448==181769837 ~ "Other",
                                                       #state_d_849518448==178420302 ~ "Unavailable/Unknown"),
                               Sex = case_when(state_d_706256705 == 536341288 ~ "Female",
                                               state_d_706256705 == 654207589 ~ "Male",
                                               state_d_706256705 == 830573274 ~ "Intersex or Other",
                                               state_d_706256705==178420302 ~ "Unavailable/Unknown"),
                        Age = case_when(state_d_934298480 == 713781738 ~ "30-34",
                                        state_d_934298480 == 631272782 ~ "35-39",
                                        state_d_934298480 == 124276120 ~ "40-45",
                                        state_d_934298480 == 450985724 ~ "46-50",
                                        state_d_934298480 == 363147933 ~ "51-55",
                                        state_d_934298480 == 636706443 ~ "56-60",
                                        state_d_934298480 == 771230670 ~ "61-65",
                                        state_d_934298480 == 722846087 ~ "66-70"),
                        Site= case_when(d_827220437 == 531629870 ~ "HealthPartners", 
                                        d_827220437 ==548392715 ~ "Henry Ford Health System", 
                                        d_827220437 == 125001209 ~ "Kaiser Permanente Colorado",
                                        d_827220437 == 327912200 ~ "Kaiser Permanente Georgia",
                                        d_827220437 == 300267574 ~ "Kaiser Permanente Hawaii",
                                        d_827220437 == 452412599 ~ "Kaiser Permanente Northwest",
                                        d_827220437 == 303349821 ~ "Marshfield Clinic Health System",
                                        d_827220437 == 657167265 ~ "Sanford Health", 
                                        d_827220437 == 809703864 ~ "University of Chicago Medicine",
                                        d_827220437 == 517700004 | d_827220437 == 13 ~ "National Cancer Institute",
                                        d_827220437 == 181769837 ~ "Other"),
                        Recruit = case_when(d_512820379==486306141 ~ "Active",
                                            TRUE ~ "Passive")) %>% filter(Sex!="Unavailable/Unknown")

site_demographics$Age <- factor(site_demographics$Age,levels=c("30-34","35-39","40-45","46-50","51-55","56-60","61-65","66-70"))

```
\FloatBarrier


```{r site_tables_separated, warning=FALSE, echo=FALSE, message=FALSE, results='asis'}



#Aleah needs these to be consented participants only with All consented participants from the start of recruitment in June 2021 until March 1st, 2024.


#Dates refer to verification date
site_demographics <- site_demographics %>%  filter( as.Date(d_914594314) < "2024-03-02")


#digital includes:  Connect Web, IHCS Web, Email/Text Invite, Patient Portal, Social Media Post, IHCS Newsletter, Video
#traditional includes: Mailed Letter, Phone Invite, Dr/Staff, Connect Staff at IHCS, Connect in News, Local News/TV/Radio, Family/Friend, Another Participant, Poster at IHCS, Table at Event, Recorded Message
site_demographics <- site_demographics %>%  mutate(marketing = case_when(((d_142654897_d_461488577==353358909 | d_142654897_d_607081902==353358909 |
                                                                      d_142654897_d_241590841==353358909 | d_142654897_d_206879104==353358909 |
                                                                      d_142654897_d_642287621==353358909 | d_142654897_d_285130077==353358909|
                                                                      d_142654897_d_684726272==353358909) &
                                                                   (d_142654897_d_942255248==353358909 | d_142654897_d_639721694==353358909 |
                                                                      d_142654897_d_196856782==353358909 | d_142654897_d_177402915==353358909 |
                                                                      d_142654897_d_791389099==353358909 | d_142654897_d_520301146==353358909|
                                                                      d_142654897_d_549687190==353358909 | d_142654897_d_326825649==353358909 | 
                                                                      d_142654897_d_819377306==353358909 | d_142654897_d_829269606==353358909 |
                                                                      d_142654897_d_967372009==353358909)) ~ "Both",
                                                                    (d_142654897_d_461488577==353358909 | d_142654897_d_607081902==353358909 |
                                                                      d_142654897_d_241590841==353358909 | d_142654897_d_206879104==353358909 |
                                                                      d_142654897_d_642287621==353358909 | d_142654897_d_285130077==353358909|
                                                                      d_142654897_d_684726272==353358909)~ "Digital",
                                                                   (d_142654897_d_942255248==353358909 | d_142654897_d_639721694==353358909 |
                                                                      d_142654897_d_196856782==353358909 | d_142654897_d_177402915==353358909 |
                                                                      d_142654897_d_791389099==353358909 | d_142654897_d_520301146==353358909|
                                                                      d_142654897_d_549687190==353358909 | d_142654897_d_326825649==353358909 | 
                                                                      d_142654897_d_819377306==353358909 | d_142654897_d_829269606==353358909 |
                                                                      d_142654897_d_967372009==353358909)~ "Traditional",
                                                                  TRUE ~ "Skipped")) %>%  filter(marketing!="Skipped")
site_demographics$marketing <- factor(site_demographics$marketing,levels=c("Digital","Traditional", "Both"))

# 14493 digital
# 15397 traiditional
# 2828 both 



# Define your demographic variables
demographics <- c("Age", "Race", "Sex",  "Site")



# Loop through each demographic
for (demo in demographics) {
  
  #Remove 'both; for chi squared
site_demographics2 <- site_demographics %>%  filter(marketing!="Both")
site_demographics2$marketing <- factor(site_demographics2$marketing,levels=c("Digital","Traditional"))
  
  active_data <- site_demographics %>%
    filter(Recruit == "Active")
  
  passive_data <- site_demographics %>%
    filter(Recruit == "Passive")
  
  # Generate cross-tabulation
  compare_active <- active_data %>%
    tbl_cross(
      row = !!sym(demo),
      col = marketing,
      label = list(marketing ~ "Recruitment Strategies", !!sym(demo) ~ demo),
      percent = "row",
      digits = c(0, 2),
      missing="no",
      margin_text = "Total Consented Recruits"
    )
  
   compare_passive <- passive_data %>%
    tbl_cross(
      row = !!sym(demo),
      col = marketing,
      label = list(marketing ~ "Recruitment Strategies", !!sym(demo) ~ demo),
      percent = "row",
      digits = c(0, 2),
      missing="no",
      margin_text = "Total Consented Recruits"
    )
   
   compare_combined <- cbind(as.data.frame(compare_active), as.data.frame(compare_passive))
   #colnames(compare_combined) <- c("Race", "Digital", "Traditional", "Both", "Total Recruits", "Race2", "Digital2", "Traditional2", "Both2", "Total Recruits2")
   compare_combined <- compare_combined[c(-1),]
   colnames(compare_combined)[1] <- demo
   colnames(compare_combined)[6] <- demo
   
   
compare_combined_table <- knitr::kable(compare_combined, caption=paste0("Self-reported Recruitment Strategies Among Site Reported ", demo, "\n Stratefied by Recruitment Status"),  row.names=FALSE, booktabs = T, linesep = "", format.args = list(big.mark = ","), align = c("l", "c", "c","c", "c", "c", "c", "c", "c", "c")) %>% kable_styling(latex_options = "scale_down")  %>% add_header_above(c(" "=1, "Recruitment Strategies" =3, " " = 2,"Recruitment Strategies" =3, " " = 1 )) %>%  add_header_above(c("Active Participants" = 5, "Passive Participants" = 5))  %>% landscape() 

   
 
  active_data2 <- site_demographics2 %>%
    filter(Recruit == "Active")
  
  passive_data2 <- site_demographics2 %>%
    filter(Recruit == "Passive")
  
  chi_active <- chisq.test(table(active_data2[[demo]], active_data2$marketing))
  chi_passive <- chisq.test(table(passive_data2[[demo]], passive_data2$marketing))
  
  foot_note <- paste("Note: With a p-value of", 
                    ifelse(chi_active$p.value < 0.05, (paste0("< 0.05 for active recruits, we have evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, ".")), (paste0(" over 0.05 for active recruits, we have no evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, "."))))
  
   # foot_note2 <- paste("Note: With a p-value of",
   #                  ifelse(chi_passive$p.value < 0.05, (paste0("< 0.05 for passive recruits,  we have evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, ".")),
   #                         ifelse(chi_passive$p.value >= 0.05,
   #                                (paste0(" over 0.05 for passive recruits, we have no evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, ".")),
   #                                " NA for passive recruits, a Fischer's exact test may provide better results.")))
   
if (!is.na(chi_passive$p.value)) {
  if (chi_passive$p.value < 0.05) {
    foot_note2 <- paste("Note: With a p-value of < 0.05 for passive recruits, we have evidence that there is a significance in the difference of digital marketing success and traditional marketing success by", demo, ".")
  } else if (chi_passive$p.value >= 0.05) {
    foot_note2 <- paste("Note: With a p-value of over 0.05 for passive recruits, we have no evidence that there is a significance in the difference of digital marketing success and traditional marketing success by", demo, ".")
  } else {
    foot_note2 <- paste("Note: With a p-value of NA for passive recruits, a Fischer's exact test may provide better results.")
  }
} else {
  foot_note2 <- "Note: With a p-value of NA for passive recruits, a Fischer's exact test may provide better results."
}
   
      foot_note3 <-  paste("Those who selected both Recruitment Strategies were removed from the chi-squared analysis.")
                    
  
  compare_combined_table <- add_footnote(compare_combined_table, foot_note, notation = "none")
    compare_combined_table <- add_footnote(compare_combined_table, foot_note2, notation = "none")
        compare_combined_table <- add_footnote(compare_combined_table, foot_note3, notation = "none")
  
  # Print or save the table as desired
  print(compare_combined_table)
  
  
  
  
  
  
  
  
  
  
  
 #### Then need one table with all recruit status and chi squared
  compare_all <- site_demographics %>%
    tbl_cross(
      row = !!sym(demo),
      col = marketing,
      label = list(marketing ~ "Recruitment Strategies", !!sym(demo) ~ demo),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total Consented Recruits"
    )
  
compare_all <- compare_all %>%
  #bold_labels() %>%
  #italicize_levels() %>%
  modify_header() %>%
  modify_caption(paste0("Self-reported Recruitment Strategies Among Site Reported ", demo)) %>% ## used to be Table 8
  as_kable_extra() %>% kable_styling(latex_options = "scale_down")


chi <- chisq.test(table(site_demographics2[[demo]], site_demographics2$marketing))

footnote <- ifelse(chi$p.value < 0.05,
                   paste0("With a p-value of < 0.05 we have evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, "."),
                   paste0("With a p-value over 0.05, we have no evidence that there is a significance in the difference of digital marketing success and traditional marketing success by ", demo, "."))


compare_all <- add_footnote(compare_all, footnote)

print(compare_all)

  
}






```



```{r}


methods <- c("d_142654897_d_461488577","d_142654897_d_607081902","d_142654897_d_241590841","d_142654897_d_206879104","d_142654897_d_642287621 ","d_142654897_d_285130077",
              "d_142654897_d_684726272","d_142654897_d_942255248", "d_142654897_d_639721694","d_142654897_d_196856782", "d_142654897_d_177402915","d_142654897_d_791389099", 
             "d_142654897_d_520301146","d_142654897_d_549687190", "d_142654897_d_326825649", "d_142654897_d_819377306", "d_142654897_d_829269606","d_142654897_d_967372009")
# Remove leading or trailing spaces from method names
methods <- trimws(methods)

# Define the list of demographics
demographics <- c("Age", "Race", "Sex",  "Site")

# Initialize an empty list to store results
all_results <- list()

# Iterate over each demographic
for (demo in demographics) {
  # Initialize an empty list to store results for the current demographic
  result_list <- list()
  
  # Iterate over each method
  for (method in methods) {
    # Subset the data to include only rows where the current method is 353358909
    subset_data <- subset(site_demographics, get(method) == 353358909)
    
    # Use table() to get counts of each demographic category
    counts <- table(subset_data[[demo]])
    
    # Store the result in the list
    result_list[[method]] <- counts
  }
  
  # Combine all results for the current demographic into a single data frame
  final_result <- as.data.frame(do.call(cbind, result_list))
    colnames(final_result) <- methods
  
  # Add demographic category as a column
  final_result[[demo]] <- row.names(final_result)
  
  # Reorder the columns
  final_result <- final_result[, c(demo, methods)]
  
  # Rename the columns to match DD
   colnames(final_result) <- c(demo, "Email/Text Invite","Patient Portal Invite","IHCS Web","Connect Web","Social Media Post", "Video", "IHCS Newsletter","Mailed Letter", "Phone Invite", "Dr/Staff", "Connect Staff at IHCS", "Connect in News",  "Local News/TV/Radio","Family/Friend", "Another Participant", "Poster at IHCS", "Table at Event","Recorded Message")
  
        # Add a row for total counts and percentage
  total_counts <- colSums(final_result[, 2:ncol(final_result)])
  total_percentage <- round((total_counts / nrow(site_demographics)) * 100, 1)
  total_row <- c("Total", paste(total_counts, " (", total_percentage, "%)", sep = ""))
  final_result <- rbind(final_result, total_row)
  
   # Save the result as a CSV file
  file_name <- paste0("Site_", demo, "_counts.csv")
  write.csv(final_result, file = file_name, row.names = FALSE)
  
  
  # Store the result for the current demographic in the overall list
  all_results[[demo]] <- final_result
}

# Print the results for all demographics
for (demo in demographics) {
  print(all_results[[demo]])
}


```
