---
title: "Cancer Screening Summary Statistics"
author: "Kelsey Sanchez"
date: "`r Sys.Date()`"
header-includes: 
  \usepackage[labelformat=empty]{caption} 
  \usepackage{placeins} 
  \usepackage{booktabs}
  \usepackage{pdflscape}
  
output:
  pdf_document:
    latex_engine: xelatex
    extra_dependencies: ["float"]
    toc: yes
    keep_tex: yes
    fig_width: 7
    fig_height: 5
    fig_caption: yes
    df_print: paged
---


```{r libraries, include=FALSE}

library(bigrquery)
library(foreach)
library(stringr)
#library(plyr)
#library(expss) ###to add labels
library(epiDisplay) ##recommended applied here crosstable, tab1
library(gmodels) ##recommended
library(magrittr)
library(arsenal)
library(gtsummary)
library(rio)



library(ggplot2)
library(gridExtra)
library(scales)
library(gt)
#install(tinytex)
library(tinytex)
library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(reshape)  ###to work on transition from long to wide or wide to long data
library(listr) ###to work on a list of vector, files or..
library(sqldf) ##sql
library(lubridate) ###date time
library(stringr) ###to work on patterns, characters


bq_auth()

```


```{r BQ Pull, include=FALSE}

project <- "nih-nci-dceg-connect-prod-6d04"


pt_pull <- "SELECT Connect_ID,  d_827220437, d_987563196, d_821247024
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` 
where Connect_ID IS NOT NULL and (d_512820379='486306141' OR d_512820379='854703046') and d_821247024='197316935' and 
(d_919254129='353358909') and (d_699625233='353358909') and 
(d_176068627='231311385')"  

CSH_pull <- "SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.cancerScreeningHistorySurvey_JP` 
where Connect_ID is not null" 


pt_pull_table <- bq_project_query(project, pt_pull)
data_pt <- bq_table_download(pt_pull_table, bigint = "integer64")

CSH_pull_table <- bq_project_query(project, CSH_pull)
data_CSH <- bq_table_download(CSH_pull_table, bigint = "integer64")

screening <- left_join(data_pt, data_CSH, by="Connect_ID")


screen= as_tibble(screening)

```




```{r functions, include=FALSE}

dict <- list("353358909"="Yes", "104430631"="No",  "178420302"="Do not Know", 
             "145235510"="Yes, because of puberty or hormones already in my body",
             "801218076"="Yes, because of hormonal medication or device",
             "461386928"="Less than 1 year ago",
             "729845236"="More than 1 year ago, but less than 2 years ago",
             "669023414"="More than 2 years ago, but less than 5 years ago",
             "786431761"="More than 5 years ago, but less than 10 years ago",
             "640520411"="Over 10 years ago",
             "236949684"="Once",
             "506053626"="Twice",
             "462661976"="3 or more times",
             "119809731"="3 to 5 times",
             "282580702"="6 to 10 times",
             "934779560"="Over 10 time",
             "441766026"="2D Mammogram/Conventional Digital Mammography", "510907305"="3D Mammogram/Digital Breast Tomosynthesis",
             "113771607" = "Surgery to Remove One Kidney","668256654" = "Surgery to Remove Both Kidneys", 
             "308633554"="Both Breasts Removed During One Surgery", "967156738"="Both Breasts Removed, Each During a Separate Surgery",
             "333647143"= "One Ovary Removed",'109972911'="Both Ovaries Removed",
             "448068764"="One Fallopian Tube Removed","537173119"="Both Fallopian Tubes Removed",
             "770550588"="One Testicle Removed","970716952"="Both Testicles Removed",
             "524029283"="Part of Prostate Removed","500023550"="Whole Prostate Removed",
             "535003378"="None of the Above")



#GT table for questions asked to all (no skip logic)
simple_funct <- function(CID, Title){  
  CID_SYM <- rlang::ensym(CID)
  dt_select <- screen %>%  select(Connect_ID, !!CID_SYM)
  gt_yn <- dt_select  %>% dplyr::group_by(!!CID_SYM) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup() %>% dplyr::mutate(answer=recode(!!CID_SYM, !!!dict)) %>% replace_na(list(answer="Skipped this Question")) %>%  dplyr::select(answer, n, percentage)
  
  gt_yn %>%  gt::gt()  %>%  
    fmt_number(columns = "percentage", decimals = 2) %>% 
    tab_header(title = md(Title)) %>% 
    cols_label(n= md("**N**"), answer = md("**Answer**"), percentage = md("**%**")) %>%  
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
    tab_options(
      stub.font.weight = "bold"
    ) %>%
    tab_style(
      style = list(
        cell_text(weight = "bold")
      ),
      locations = cells_body(
        columns = answer,
      )
    ) 
}


#GT table with one filter/skip logic
one_logic_funct <- function(CID, CID_prev, Prev_Answer, Title){  
  CID_SYM <- rlang::ensym(CID)
  CID_SYM_P <- rlang::ensym(CID_prev)
  dt_select <- screen %>%  filter(!!CID_SYM_P == Prev_Answer) %>%  select(Connect_ID, !!CID_SYM) 
  gt_yn <- dt_select  %>% dplyr::group_by(!!CID_SYM) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup() %>% dplyr::mutate(answer=recode(!!CID_SYM, !!!dict)) %>% replace_na(list(answer="Skipped this Question")) %>%  dplyr::select(answer, n, percentage)
  
  gt_yn %>%  gt::gt(rowname_col = "row_lab")  %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md(Title)) %>% 
  cols_label(n= md("**N**"),  answer = md("**Answer**"), percentage = md("**%**")) %>% 
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = answer,
    )
  ) 
}


#GT table with two filter/skip logics
two_logic_funct <- function(CID, CID_prev, Prev_Answer1, Prev_Answer2,  Title){  
  CID_SYM <- rlang::ensym(CID)
  CID_SYM_P <- rlang::ensym(CID_prev)
  dt_select <- screen %>%  filter(!!CID_SYM_P == Prev_Answer1 | !!CID_SYM_P == Prev_Answer2) %>%  select(Connect_ID, !!CID_SYM) 
  gt_yn <- dt_select  %>% dplyr::group_by(!!CID_SYM) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup() %>% dplyr::mutate(answer=recode(!!CID_SYM, !!!dict)) %>% replace_na(list(answer="Skipped this Question")) %>%  dplyr::select(answer, n, percentage)
  
  gt_yn %>%  gt::gt(rowname_col = "row_lab")  %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md(Title)) %>% 
  cols_label(n= md("**N**"),  answer = md("**Answer**"), percentage = md("**%**")) %>% 
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = answer,
    )
  ) 
}



#GT table with three filter/skip logics
three_logic_funct <- function(CID, CID_prev, Prev_Answer1, Prev_Answer2, Prev_Answer3,  Title){  
  CID_SYM <- rlang::ensym(CID)
  CID_SYM_P <- rlang::ensym(CID_prev)
  dt_select <- screen %>%  filter(!!CID_SYM_P == Prev_Answer1 | !!CID_SYM_P == Prev_Answer2| !!CID_SYM_P == Prev_Answer3) %>%  
    select(Connect_ID, !!CID_SYM) 
  gt_yn <- dt_select  %>% dplyr::group_by(!!CID_SYM) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup() %>% dplyr::mutate(answer=recode(!!CID_SYM, !!!dict)) %>% replace_na(list(answer="Skipped this Question")) %>%  dplyr::select(answer, n, percentage)
  
  gt_yn %>%  gt::gt(rowname_col = "row_lab")  %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md(Title)) %>% 
  cols_label(n= md("**N**"),  answer = md("**Answer**"), percentage = md("**%**")) %>% 
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = answer,
    )
  ) 
}



#GT table with four filter/skip logics
four_logic_funct <- function(CID, CID_prev, Prev_Answer1, Prev_Answer2, Prev_Answer3, Prev_Answer4,  Title){  
  CID_SYM <- rlang::ensym(CID)
  CID_SYM_P <- rlang::ensym(CID_prev)
  dt_select <- screen %>%  filter(!!CID_SYM_P == Prev_Answer1 | !!CID_SYM_P == Prev_Answer2| !!CID_SYM_P == Prev_Answer3| !!CID_SYM_P == Prev_Answer4) %>%  
    select(Connect_ID, !!CID_SYM) 
  gt_yn <- dt_select  %>% dplyr::group_by(!!CID_SYM) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup() %>% dplyr::mutate(answer=recode(!!CID_SYM, !!!dict)) %>% replace_na(list(answer="Skipped this Question")) %>%  dplyr::select(answer, n, percentage)
  
  gt_yn %>%  gt::gt(rowname_col = "row_lab")  %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md(Title)) %>% 
  cols_label(n= md("**N**"),  answer = md("**Answer**"), percentage = md("**%**")) %>% 
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = answer,
    )
  ) 
}




#GT table with five filter/skip logics
five_logic_funct <- function(CID, CID_prev, Prev_Answer1, Prev_Answer2, Prev_Answer3, Prev_Answer4, Prev_Answer5,  Title){  
  CID_SYM <- rlang::ensym(CID)
  CID_SYM_P <- rlang::ensym(CID_prev)
  dt_select <- screen %>%  filter(!!CID_SYM_P == Prev_Answer1 | !!CID_SYM_P == Prev_Answer2| !!CID_SYM_P == Prev_Answer3| !!CID_SYM_P == Prev_Answer4| !!CID_SYM_P == Prev_Answer5) %>%  
    select(Connect_ID, !!CID_SYM) 
  gt_yn <- dt_select  %>% dplyr::group_by(!!CID_SYM) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup() %>% dplyr::mutate(answer=recode(!!CID_SYM, !!!dict)) %>% replace_na(list(answer="Skipped this Question")) %>%  dplyr::select(answer, n, percentage)
  
  gt_yn %>%  gt::gt(rowname_col = "row_lab")  %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md(Title)) %>% 
  cols_label(n= md("**N**"),  answer = md("**Answer**"), percentage = md("**%**")) %>% 
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = answer,
    )
  ) 
}



#Boxplot
boxp_funct <- function(CID,Title, Xlab) {
  CID_SYM <- rlang::ensym(CID)
  screen %>% mutate(!!CID_SYM:=as.numeric(!!CID_SYM)) %>%
    filter(!is.na(!!CID_SYM)) %>%
    ggplot(aes(x=!!CID_SYM))+
    xlab(Xlab) + geom_boxplot()+  ggtitle(Title)+
    theme(axis.text.y=element_blank(),  #remove y axis labels
        axis.ticks.y=element_blank()  #remove y axis ticks
        )
}


```

\newpage

```{r Sex, warning=FALSE, echo=FALSE, message=FALSE}

which_sex2 <- screen %>%
  mutate(
    Penis = if_else(D_890391968_D_582784267 == 1, 1, 0),
    Testes = if_else(D_890391968_D_751402477 == 1, 1, 0),
    `Prostate Gland` = if_else(D_890391968_D_700100953 == 1, 1, 0),
    Vagina = if_else(D_890391968_D_846483618 == 1, 1, 0),
    Cervix = if_else(D_890391968_D_505282171 == 1, 1, 0),
    Uterus = if_else(D_890391968_D_578416151 == 1, 1, 0),
    Ovaries = if_else(D_890391968_D_434651539 == 1, 1, 0),
    `Fallopian Tubes` = if_else(D_890391968_D_108025529 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_890391968_D_")) == 0 | is.na(select(., starts_with("D_890391968_D_")))) == ncol(select(., starts_with("D_890391968_D_"))), 1, 0)
  )


pivot_sex <- which_sex2 %>%
  select(`Penis`:Skipped) %>%
  pivot_longer(cols = everything(), names_to = "Body_Parts", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  group_by(Body_Parts) %>%
  summarise(Frequency = n()) %>%
  ungroup() %>%
  mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

dt_sex <- pivot_sex %>%
  gt() %>%
  fmt_number(columns = "Percentage", decimals = 2) %>% 
  fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
  tab_header(title = md("Body Parts Born With")) %>%
  cols_label(Frequency = md("**N**"), 
             Percentage = md("**%**"), 
             Body_Parts = md("**Answer**")) %>%
  tab_options(stub.font.weight = "bold") %>%
  tab_style(
    style = list(cell_text(weight = "bold")),
    locations = cells_body(columns = Body_Parts)
  ) %>%
  tab_footnote(
    footnote = "As this is a select all question, participants may select multiple responses.",
    locations = cells_column_labels(columns = Percentage)
  ) 

dt_sex



```


```{r BRSTTISS, warning=FALSE, echo=FALSE, message=FALSE}

screen$D_413039729 <- factor(screen$D_413039729, levels=c(104430631,145235510,801218076,178420302, "Skipped this Question"))
simple_funct(D_413039729, "Had Breasts or Breast Tissue Growth")

```


\newpage
# MH GROUP9
```{r MhGroup9, warning=FALSE, echo=FALSE, message=FALSE}



mhgroup9 <- screen %>%
  mutate(
    `Tonsillectomy` = if_else(D_729984625_D_797189152 == 1, 1, 0),
    Cholecystectomy = if_else(D_729984625_D_633546100 == 1, 1, 0),
    Appendectomy = if_else(D_729984625_D_866002271 == 1, 1, 0),
    Splenectomy = if_else(D_729984625_D_209101810 == 1, 1, 0),
    Thyroidectomy = if_else(D_729984625_D_413734739 == 1, 1, 0),
    Nephrectomy = if_else(D_729984625_D_215525943 == 1, 1, 0),
    Liposuction = if_else(D_729984625_D_118789503 == 1, 1, 0),
    `Gastric Bypass` = if_else(D_729984625_D_715563991 == 1, 1, 0),
    `Breast Surgery` = if_else(D_729984625_D_533491176 == 1, 1, 0),
    Hysterectomy = if_else(D_729984625_D_220755749 == 1, 1, 0),
    `Tubal Ligation` = if_else(D_729984625_D_465318416 == 1, 1, 0),
    Oophorectomy = if_else(D_729984625_D_630100221 == 1, 1, 0),
    Salpingectomy = if_else(D_729984625_D_692881833 == 1, 1, 0),
    Vasectomy = if_else(D_729984625_D_654450030 == 1, 1, 0),
    `Orchiectomy or Orchidectomy` = if_else(D_729984625_D_532603425 == 1, 1, 0),
    Prostatectomy = if_else(D_729984625_D_733236542 == 1, 1, 0),
    Penectomy = if_else(D_729984625_D_961987554 == 1, 1, 0),
    None = if_else(D_729984625_D_535003378 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_729984625_D_")) == 0 | is.na(select(., starts_with("D_729984625_D_")))) == ncol(select(., starts_with("D_729984625_D_"))), 1, 0)
  )

pivot_data9 <- mhgroup9 %>%
  select(`Tonsillectomy`:Skipped) %>%
  pivot_longer(cols = everything(), names_to = "Surgery", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  group_by(Surgery) %>%
  summarise(Frequency = n()) %>%
  ungroup() %>%
  mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

dt_mgr9 <- pivot_data9 %>%
  gt() %>%
  fmt_number(columns = "Percentage", decimals = 2) %>% 
  fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
  tab_header(title = md("MHGROUP9: Surgeries")) %>%
  cols_label(Frequency = md("**N**"), 
             Percentage = md("**%**"), 
             Surgery = md("**Answer**")) %>%
  tab_options(stub.font.weight = "bold") %>%
  tab_style(
    style = list(cell_text(weight = "bold")),
    locations = cells_body(columns = Surgery)
  ) %>%
  tab_footnote(
    footnote = "As this is a select all question, participants may select multiple responses.",
    locations = cells_column_labels(columns = Percentage)
  ) 

dt_mgr9


```


```{r MHGroup9Diagn, warning=FALSE, echo=FALSE, message=FALSE}
#	Tonsils removed (tonsillectomy)
tonsil_a_sg=boxp_funct(D_675055475_D_623218391,"Age at Tonisllectomy Surgery","Age") 
tonsil_y_sg=boxp_funct(D_675055475_D_802622485,"Year of Tonisllectomy Surgery","Year")
grid.arrange(tonsil_a_sg, tonsil_y_sg, nrow=2)


#	Gallbladder removed (cholecystectomy)
gall_a_sg=boxp_funct(D_250003172_D_623218391,"Age at Cholecystectomy Surgery","Age") 
gall_y_sg=boxp_funct(D_250003172_D_802622485,"Year of Cholecystectomy Surgery","Year")
grid.arrange(gall_a_sg, gall_y_sg, nrow=2)


#	Appendix removed (appendectomy)
apdx_a_sg=boxp_funct(D_341080024_D_623218391,"Age at Appendectomy Surgery","Age") 
apdx_y_sg=boxp_funct(D_341080024_D_802622485,"Year of Appendectomy Surgery","Year")
grid.arrange(apdx_a_sg, apdx_y_sg, nrow=2)

#	Spleen removed (Splenectomy)
spln_a_sg=boxp_funct(D_841573821_D_623218391,"Age at Splenectomy Surgery","Age") 
spln_y_sg=boxp_funct(D_841573821_D_802622485,"Year of Splenectomy Surgery","Year")
grid.arrange(spln_a_sg, spln_y_sg, nrow=2)

#	Throid removed (Thyroidectomy)
thyr_a_sg=boxp_funct(D_976626196_D_623218391,"Age at Thyroidectomy Surgery","Age") 
thyr_y_sg=boxp_funct(D_976626196_D_802622485,"Year of Thyroidectomy Surgery","Year")
grid.arrange(thyr_a_sg, thyr_y_sg, nrow=2)
```
\FloatBarrier
\newpage
```{r MHGroup9Diagn2, warning=FALSE, echo=FALSE, message=FALSE}
#	Kidney(s) removed (nephrectomy)
neph_a_sg=boxp_funct(D_998519118_D_623218391,"Age at Nephrectomy Surgery","Age") 
neph_y_sg=boxp_funct(D_998519118_D_802622485,"Year of Nephrectomy Surgery","Year")
one_logic_funct(D_951847507, D_729984625_D_215525943, 1, "Type of Kidney Removal Surgery")
grid.arrange(neph_a_sg, neph_y_sg, nrow=2)


#	Liposuction
lipo_a_sg=boxp_funct(D_645149364_D_623218391,"Age at Liposuction Surgery","Age") 
lipo_y_sg=boxp_funct(D_645149364_D_802622485,"Year of Liposuction Surgery","Year")
grid.arrange(lipo_a_sg, lipo_y_sg, nrow=2)


#	Bariatric surgery (lap band, gastric bypass)
bar_sg_a_sg=boxp_funct(D_839555631_D_623218391,"Age at Gastric Bypass Surgery","Age")
bar_sg_y_sg=boxp_funct(D_839555631_D_802622485,"Year of Gastric Bypass Surgery","Year")
grid.arrange(bar_sg_a_sg, bar_sg_y_sg, nrow=2)

```

\newpage

```{r BreastSurgery, warning=FALSE, echo=FALSE, message=FALSE}

  #type of breast surgery
br_surg= screen  %>% filter(D_729984625_D_533491176==1) %>%  
  mutate(
    `Breast Implants` = if_else(D_506456253_D_506456253_D_752953170 == 1, 1, 0),
    `Mastopexy` = if_else(D_506456253_D_506456253_D_325506683 == 1, 1, 0),
    `Breast Reconstruction` = if_else(D_506456253_D_506456253_D_335563082 == 1, 1, 0),
    `Breast Reduction` = if_else(D_506456253_D_506456253_D_955881350 == 1, 1, 0),
    `Partial Mastectomy` = if_else(D_506456253_D_506456253_D_492902023 == 1, 1, 0),
    `Mastectomy` = if_else(D_506456253_D_506456253_D_256196714 == 1, 1, 0),
    `Double Mastectomy` = if_else(D_506456253_D_506456253_D_802859122 == 1, 1, 0),
    Abscess = if_else(D_506456253_D_506456253_D_520432394 == 1, 1, 0),
    `Removal of Lactiferous` = if_else(D_506456253_D_506456253_D_667901971 == 1, 1, 0),
    Other = if_else(D_506456253_D_506456253_D_807835037 == 1 | !is.na(D_506456253_D_942347130), 1, 0),
    None = if_else(D_506456253_D_506456253_D_535003378 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_506456253_D_506456253_")) == 0 | is.na(select(., starts_with("D_506456253_D_506456253_")))) == ncol(select(., starts_with("D_506456253_D_506456253_"))), 1, 0)
  )


pivot_breast <- br_surg %>%
  select(`Breast Implants`:Skipped) %>%
  pivot_longer(cols = everything(), names_to = "Surgery", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  group_by(Surgery) %>%
  summarise(Frequency = n()) %>%
  ungroup() %>%
  mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

dt_breast <- pivot_breast %>%
  gt() %>%
  fmt_number(columns = "Percentage", decimals = 2) %>% 
  fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
  tab_header(title = md("Breast Surgeries")) %>%
  cols_label(Frequency = md("**N**"), 
             Percentage = md("**%**"), 
             Surgery = md("**Answer**")) %>%
  tab_options(stub.font.weight = "bold") %>%
  tab_style(
    style = list(cell_text(weight = "bold")),
    locations = cells_body(columns = Surgery)
  ) %>%
  tab_footnote(
    footnote = "As this is a select all question, participants may select multiple responses.",
    locations = cells_column_labels(columns = Percentage)
  ) 

dt_breast

```


```{r BreastSurgYear, warning=FALSE, echo=FALSE, message=FALSE}
#cat("Breast Implants")
implant_a_sg=boxp_funct(D_439760665_D_623218391,"Age at Breats Implants Surgery","Age")
implant_y_sg=boxp_funct(D_439760665_D_802622485,"Year of Breats Implants Surgery","Year")
grid.arrange(implant_a_sg, implant_y_sg, nrow=2)


#cat("Mastopexy")
mastop_a_sg=boxp_funct(D_950690103_D_623218391,"Age at Mastopexy Surgery","Age")
mastop_y_sg=boxp_funct(D_950690103_D_802622485,"Year of Mastopexy Surgery","Year")
grid.arrange(mastop_a_sg, mastop_y_sg, nrow=2)


#cat("Breast Reconstruction")
recon_a_sg=boxp_funct(D_975268706_D_623218391,"Age at Breast Reconstruction Surgery","Age")
recon_y_sg=boxp_funct(D_975268706_D_802622485,"Year of Breast Reconstruction Surgery","Year") 
grid.arrange(recon_a_sg, recon_y_sg, nrow=2)

#cat("Breast Reduction")
reduct_a_sg=boxp_funct(D_277890744_D_623218391,"Age at Breast Reduction Surgery","Age")
reduct_y_sg=boxp_funct(D_277890744_D_802622485,"Year of Breast Reduction Surgery","Year")
grid.arrange(reduct_a_sg, reduct_y_sg, nrow=2)

#cat("Partial Mastectomy")
prtms_a_sg=boxp_funct(D_936444833_D_623218391,"Age at Partial Mastectomy Surgery","Age")
prtms_y_sg=boxp_funct(D_936444833_D_802622485,"Year of Partial Mastectomy Surgery","Year")
grid.arrange(prtms_a_sg, prtms_y_sg, nrow=2)

#cat("Mastectomy")
mastec_a_sg=boxp_funct(D_758881441_D_623218391,"Age at Mastectomy Surgery","Age") 
mastec_y_sg=boxp_funct(D_758881441_D_802622485,"Year of Mastectomy Surgery","Year") 
grid.arrange(mastec_a_sg, mastec_y_sg, nrow=2)
```
\FloatBarrier
\newpage
```{r BreastSurgYear2, warning=FALSE, echo=FALSE, message=FALSE}
#BREASTSUR6A
screen$D_765772509 <- factor(screen$D_765772509, levels = c(308633554, 967156738, 535003378))
one_logic_funct(D_765772509, D_506456253_D_506456253_D_802859122, 1, "Type of Breast Removal Surgery")


#cat("Double Mastectomy")
dbmas_a_sg=boxp_funct(D_250353250_D_623218391,"Age at Double Mastectomy Surgery","Age")
dbmas_y_sg=boxp_funct(D_250353250_D_802622485,"Year of Double Mastectomy Surgery","Year")
grid.arrange(dbmas_a_sg, dbmas_y_sg, nrow=2)

#cat("Breast Abscess")
abscess_a_sg=boxp_funct(D_166524009_D_623218391,"Age at Breast Abscess Surgery","Age") 
abscess_y_sg=boxp_funct(D_166524009_D_802622485,"Year of Breast Abscess Surgery","Year") 
grid.arrange(abscess_a_sg, abscess_y_sg, nrow=2)

#cat("Lactiferous Surgery")
lact_a_sg=boxp_funct(D_367942006_D_623218391,"Age at Removal of Lactiferous Surgery","Age")
lact_y_sg=boxp_funct(D_367942006_D_802622485,"Year of Removal of Lactiferous Surgery","Year")
grid.arrange(lact_a_sg, lact_y_sg, nrow=2)

#cat("Other Breast Surgery")
othb_a_sg=boxp_funct(D_907385951_D_623218391,"Age at Other Breast Surgery","Age")
othb_y_sg=boxp_funct(D_907385951_D_802622485,"Year of Other Breast Surgery","Year")
grid.arrange(othb_a_sg, othb_y_sg, nrow=2)


```


```{r MHGroup9Diagn_Cont, warning=FALSE, echo=FALSE, message=FALSE}

#cat("Hysterectomy") 
hyst_a_sg=boxp_funct(D_350184001_D_623218391,"Age at Hysterectomy","Age") 
hyst_y_sg=boxp_funct(D_350184001_D_802622485,"Year of Hysterectomy","Year")
grid.arrange(hyst_a_sg, hyst_y_sg, nrow=2)


#cat("Tubal Ligation")  
tublig_a_sg=boxp_funct(D_522645663_D_623218391,"Age at Tubal Ligation Surgery","Age") 
tublig_y_sg=boxp_funct(D_522645663_D_802622485,"Year of Tubal Ligation Surgery","Year")
grid.arrange(tublig_a_sg, tublig_y_sg, nrow=2)
```
\FloatBarrier
\newpage
```{r MHGroup9Diagn_Cont2, warning=FALSE, echo=FALSE, message=FALSE}

#cat("Oophorectomy")
  #type
#screen$D_590067228 <- factor(screen$D_590067228, levels = c(333647143, 109972911, 535003378))
one_logic_funct(D_590067228, D_729984625_D_630100221, 1, "Type of Oophorectomy")

  #age/year of surgery
ooph_a_sg=boxp_funct(D_787505819_D_623218391,"Age at Tubal Oophorectomy","Age") 
ooph_y_sg=boxp_funct(D_787505819_D_802622485,"Year of Tubal Oophorectomy","Year")
grid.arrange(ooph_a_sg, ooph_y_sg, nrow=2)
```
\FloatBarrier
\newpage
```{r MHGroup9Diagn_Cont3, warning=FALSE, echo=FALSE, message=FALSE}

#cat("Salpingectomy") 
  #type
screen$D_860839849 <- factor(screen$D_860839849, levels = c(448068764, 537173119, 535003378))
one_logic_funct(D_860839849, D_729984625_D_692881833, 1, "Type of Salpingectomy")

  #age/year
salp_a_sg=boxp_funct(D_949587133_D_623218391,"Age at Tubal Salpingectomy","Age") 
salp_y_sg=boxp_funct(D_949587133_D_802622485,"Year of Tubal Salpingectomy","Year")
grid.arrange(salp_a_sg, salp_y_sg, nrow=2)


#	Vasectomy 
vasec_a_sg=boxp_funct(D_671670265_D_623218391,"Age at Tubal Vasectomy","Age") 
vasec_y_sg=boxp_funct(D_671670265_D_802622485,"Year of Tubal Vasectomy","Year")
grid.arrange(vasec_a_sg, vasec_y_sg, nrow=2)

```
\FloatBarrier
\newpage
```{r MHGroup9Diagn_Cont4, warning=FALSE, echo=FALSE, message=FALSE}
#cat("Orchiectomy or Ochidectomy") 
  #type
screen$D_429157727 <- factor(screen$D_429157727, levels = c(770550588, 970716952, 535003378))
one_logic_funct(D_429157727, D_729984625_D_532603425, 1, "Type of Orchiectomy or Ochidectomy")

  #age/year
orch_a_sg=boxp_funct(D_314345103_D_623218391,"Age at Orchiectomy Surgery","Age") 
orch_y_sg=boxp_funct(D_314345103_D_802622485,"Year of Orchiectomy Surgery","Year")
grid.arrange(orch_a_sg, orch_y_sg, nrow=2)

```
\FloatBarrier
\newpage
```{r MHGroup9Diagn_Cont5, warning=FALSE, echo=FALSE, message=FALSE}
#cat("Prostatectomy") 
  #type
screen$D_292314539 <- factor(screen$D_292314539, levels = c(524029283, 500023550, 535003378))
one_logic_funct(D_292314539, D_729984625_D_733236542, 1, "Type of Prostatectomy")

  #age/year
prost_a_sg=boxp_funct(D_343990595_D_623218391,"Age at Prostatectomy Surgery","Age") 
prost_y_sg=boxp_funct(D_343990595_D_802622485,"Year of Tubal Prostatectomy Surgery","Year") 
grid.arrange(prost_a_sg, prost_y_sg, nrow=2)


#	Penis removed (penectomy) 
penis_a_sg=boxp_funct(D_203366781_D_623218391,"Age at Tubal Penectomy Surgery","Age") 
penis_y_sg=boxp_funct(D_203366781_D_802622485,"Year of Tubal Penectomy Surgery","Year")
grid.arrange(penis_a_sg, penis_y_sg, nrow=2)


```


\newpage
# Oral Cancer Screening

```{r ORSCREEN, warning=FALSE, echo=FALSE, message=FALSE}


#ORSCREEN
screen$D_802157786 <- factor(screen$D_802157786, levels=c(353358909, 104430631, 178420302, "Skipped this Question"))
simple_funct(D_802157786, "Ever Screened for Oral Cancer")

#ORSCREEN1
screen$D_852697610 <- factor(screen$D_852697610, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_852697610, D_802157786, "353358909", "Timeframe of First Oral Cancer Screening")

#ORSCREEN2
screen$D_860253133 <- factor(screen$D_860253133, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_860253133, D_802157786, "353358909", "Number of Oral Cancer Screenings")

#ORSCREEN3
screen$D_682440005 <- factor(screen$D_682440005, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_682440005, D_860253133, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Oral Cancer Screening")

#ORSCREEN4
screen$D_339142996 <- factor(screen$D_339142996, levels=c(353358909, 104430631, 178420302, "Skipped this Question"))
one_logic_funct(D_339142996, D_802157786, "353358909", "Oral Biospy Completed")

#ORSCREEN5
screen$D_375662706 <- factor(screen$D_375662706, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_375662706, D_339142996, "353358909", "Timeframe of First Oral Cancer Biospy")

#ORSCREEN6
screen$D_859197222 <- factor(screen$D_859197222, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_859197222, D_339142996, "353358909", "Number of Oral Cancer Biospies")

#ORSCREEN7
screen$D_529358901 <- factor(screen$D_529358901, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_529358901, D_859197222, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Oral Cancer Biopsy")

```


\newpage
# Colon and Rectal Cancer Screening

```{r COLREC, warning=FALSE, echo=FALSE, message=FALSE}

#COLSCREEN
col_grid= screen  %>% 
  mutate(
    `Colonoscopy` = if_else(D_365148290_D_203210013 == 1, 1, 0),
    `CT Colonoscopy` = if_else(D_365148290_D_219088015 == 1, 1, 0),
    `Sigmoidoscopy` = if_else(D_365148290_D_283265038 == 1, 1, 0),
    `Proctoscopy` = if_else(D_365148290_D_691148901 == 1, 1, 0),
    `Stool (Fecal) Test` = if_else(D_365148290_D_928432579 == 1, 1, 0),
    None = if_else(D_365148290_D_535003378 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_365148290_")) == 0 | is.na(select(., starts_with("D_365148290_")))) == ncol(select(., starts_with("D_365148290_"))), 1, 0)
  )


pivot_col <- col_grid %>%
  select(`Colonoscopy`:Skipped) %>%
  pivot_longer(cols = everything(), names_to = "Procedures", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  group_by(Procedures) %>%
  summarise(Frequency = n()) %>%
  ungroup() %>%
  mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

pivot_col %>%
  gt() %>%
  fmt_number(columns = "Percentage", decimals = 2) %>% 
  fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
  tab_header(title = md("Tests or Procedures for Colorectal Cancer")) %>%
  cols_label(Frequency = md("**N**"), 
             Percentage = md("**%**"), 
             Procedures = md("**Answer**")) %>%
  tab_options(stub.font.weight = "bold") %>%
  tab_style(
    style = list(cell_text(weight = "bold")),
    locations = cells_body(columns = Procedures)
  ) 


### Colonoscopy

#COL1
screen$D_988661374 <- factor(screen$D_988661374, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_988661374, D_365148290_D_203210013, "1", "Timeframe of First Colonoscopy")

#COL2
screen$D_619830872 <- factor(screen$D_619830872, levels=c(236949684, 506053626, 462661976, 178420302, "Skipped this Question"))
one_logic_funct(D_619830872, D_365148290_D_203210013, "1", "Number of Colonoscopies")

#COL3
screen$D_226488112 <- factor(screen$D_226488112, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
three_logic_funct(D_226488112, D_619830872, "506053626","462661976","178420302", "Timeframe of Last Colonoscopy")



### CT Colonoscopy

#CTCOL1
screen$D_884856351 <- factor(screen$D_884856351, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_884856351, D_365148290_D_219088015, "1", "Timeframe of First CT Colonoscopy")

#CTCOL2
screen$D_900561740 <- factor(screen$D_900561740, levels=c(236949684, 506053626, 462661976, 178420302, "Skipped this Question"))
one_logic_funct(D_900561740, D_365148290_D_219088015, "1", "Number of CT Colonoscopies")

#CTCOL3
screen$D_729390410 <- factor(screen$D_729390410, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
three_logic_funct(D_729390410, D_900561740, "506053626","462661976","178420302", "Timeframe of Last CT Colonoscopy")




### Sigmoidoscopy

#SIG1
screen$D_869938650 <- factor(screen$D_869938650, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_869938650, D_365148290_D_283265038, "1", "Timeframe of First Sigmoidoscopy")

#SIG2
screen$D_541338917 <- factor(screen$D_541338917, levels=c(236949684, 506053626, 462661976, 178420302, "Skipped this Question"))
one_logic_funct(D_541338917, D_365148290_D_283265038, "1", "Number of Sigmoidoscopies")

#SIG3
screen$D_833553697 <- factor(screen$D_833553697, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
three_logic_funct(D_833553697, D_541338917, "506053626","462661976","178420302", "Timeframe of Last Sigmoidoscopy")




### Proctoscopy

#PROCT1
screen$D_689280509 <- factor(screen$D_689280509, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_689280509, D_365148290_D_691148901, "1", "Timeframe of First Proctoscopy")

#PROCT2
screen$D_108417657 <- factor(screen$D_108417657, levels=c(236949684, 506053626, 462661976, 178420302, "Skipped this Question"))
one_logic_funct(D_108417657, D_365148290_D_691148901, "1", "Number of Proctoscopies")

#PROCT3
screen$D_822995885 <- factor(screen$D_822995885, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
three_logic_funct(D_822995885, D_108417657, "506053626","462661976","178420302", "Timeframe of Last Proctoscopy")




### Stool (fecal) test

#STOOL1
screen$D_677043723 <- factor(screen$D_677043723, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_677043723, D_365148290_D_928432579, "1", "Timeframe of First Fecal Test")

#STOOL2
screen$D_960218176 <- factor(screen$D_960218176, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_960218176, D_365148290_D_928432579, "1", "Number of Fecal Tests")

#STOOL3
screen$D_806961194 <- factor(screen$D_806961194, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_806961194, D_960218176, "506053626","119809731"," 282580702", "934779560","178420302", "Timeframe of Last Fecal Test")

```



\newpage
# Anal Cancer Screening

```{r ANALSCREEN, warning=FALSE, echo=FALSE, message=FALSE}


#ANALSCREEN
screen$D_129025755 <- factor(screen$D_129025755, levels=c(353358909, 104430631, 178420302, "Skipped this Question"))
simple_funct(D_129025755, "Ever Screened for Anal Cancer")

#ANALSCREEN1
screen$D_702922820 <- factor(screen$D_702922820, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_702922820, D_129025755, "353358909", "Timeframe of First Anal Cancer Screening")

#ANALSCREEN2
screen$D_236655642 <- factor(screen$D_236655642, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_236655642, D_129025755, "353358909", "Number of Anal Cancer Screenings")

#ANALSCREEN3
screen$D_581174597 <- factor(screen$D_581174597, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_581174597, D_236655642, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Anal Cancer Screening")

```



\newpage
# Lung Cancer Screening

```{r LUNGCT, warning=FALSE, echo=FALSE, message=FALSE}


#LUNGCT
screen$D_524918714 <- factor(screen$D_524918714, levels=c(353358909, 104430631, 178420302, "Skipped this Question"))
simple_funct(D_524918714, "Ever Screened for Lung Cancer")

#LUNGCT1
screen$D_584375130 <- factor(screen$D_584375130, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_584375130, D_524918714, "353358909", "Timeframe of First Lung Cancer Screening")

#LUNGCT2
screen$D_221189280 <- factor(screen$D_221189280, levels=c(236949684, 506053626, 462661976,  178420302, "Skipped this Question"))
one_logic_funct(D_221189280, D_524918714, "353358909", "Number of Lung Cancer Screenings")

#LUNGCT3
screen$D_737402324 <- factor(screen$D_737402324, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
three_logic_funct(D_737402324, D_221189280, "506053626","462661976","178420302", "Timeframe of Last Lung Cancer Screening")

```



\newpage
# Skin Cancer Screening

```{r SkinSCREEN, warning=FALSE, echo=FALSE, message=FALSE}


#SkinSCREEN
screen$D_552399966 <- factor(screen$D_552399966, levels=c(353358909, 104430631, 178420302, "Skipped this Question"))
simple_funct(D_552399966, "Ever Screened for Skin Cancer")

#SkinSCREEN1
skscr1= screen  %>% filter(D_552399966==353358909) %>%  
  mutate(
    `Spot Screen` = if_else(D_124071431_D_160709137 == 1, 1, 0),
    `Part Screen` = if_else(D_124071431_D_547567441 == 1, 1, 0),
    `Full Screen` = if_else(D_124071431_D_956827502 == 1, 1, 0),
    Unknown = if_else(D_124071431_D_178420302 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_124071431_")) == 0 ) == ncol(select(., starts_with("D_124071431_"))), 1, 0)
  )


pivot_skin <- skscr1 %>%
  select(`Spot Screen`:Skipped) %>%
  pivot_longer(cols = everything(), names_to = "Surgery", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  group_by(Surgery) %>%
  summarise(Frequency = n()) %>%
  ungroup() %>%
  mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

pivot_skin %>%
  gt() %>%
  fmt_number(columns = "Percentage", decimals = 2) %>% 
  fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
  tab_header(title = md("Portion of Skin Screened")) %>%
  cols_label(Frequency = md("**N**"), 
             Percentage = md("**%**"), 
             Surgery = md("**Answer**")) %>%
  tab_options(stub.font.weight = "bold") %>%
  tab_style(
    style = list(cell_text(weight = "bold")),
    locations = cells_body(columns = Surgery)
  )



#SkinSCREEN2
screen$D_113343940 <- factor(screen$D_113343940, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_113343940, D_124071431_D_956827502, "1", "Timeframe of Full Body Skin Examination")

#SkinSCREEN3
screen$D_925516907 <- factor(screen$D_925516907, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_925516907, D_124071431_D_956827502, "1", "Number of Full Body Skin Examinations")

#SkinSCREEN4
screen$D_506482920 <- factor(screen$D_506482920, levels=c(506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
five_logic_funct(D_506482920, D_925516907, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Skin Cancer Screening")

```



\newpage
# Upper Endoscopy Screening

```{r UPENDO, warning=FALSE, echo=FALSE, message=FALSE}


#UPENDO
screen$D_991871399 <- factor(screen$D_991871399, levels=c(353358909, 104430631, 178420302, "Skipped this Question"))
simple_funct(D_991871399, "Ever Had an Upper Endoscopy")

#UPENDO1
screen$D_761831751 <- factor(screen$D_761831751, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_761831751, D_991871399, "353358909", "Timeframe of First Upper Endoscopy")

#UPENDO2
screen$D_588828383 <- factor(screen$D_588828383, levels=c(236949684, 506053626, 462661976, 178420302, "Skipped this Question"))
one_logic_funct(D_588828383, D_991871399, "353358909", "Number of Upper Endoscopies")

#UPENDO3
screen$D_485867936 <- factor(screen$D_485867936, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
three_logic_funct(D_485867936, D_588828383, "506053626","462661976","178420302", "Timeframe of Last Upper Endoscopy")

```



\newpage
# Prostate Cancer Screening

```{r PROSCREEN, warning=FALSE, echo=FALSE, message=FALSE}

##PROSCREEN
prost_grid= screen  %>% filter(D_890391968_D_700100953 == 1) %>% 
mutate(
    `Rectal Exam` = if_else(D_465056475_D_312250694 == 1, 1, 0),
    `PSA Blood Test` = if_else(D_465056475_D_255054078 == 1, 1, 0),
    `Prostate Biopsy` = if_else(D_465056475_D_492921091 == 1, 1, 0),
    None = if_else(D_465056475_D_535003378 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_465056475_")) == 0 | is.na(select(., starts_with("D_465056475_")))) == ncol(select(., starts_with("D_465056475_"))), 1, 0)
)


pivot_prost <- prost_grid %>%
    select(`Rectal Exam`:Skipped) %>%
    pivot_longer(cols = everything(), names_to = "Procedures", values_to = "Selected") %>%
    filter(Selected == 1) %>%
    group_by(Procedures) %>%
    summarise(Frequency = n()) %>%
    ungroup() %>%
    mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

pivot_prost %>%
    gt() %>%
    fmt_number(columns = "Percentage", decimals = 2) %>% 
    fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
    tab_header(title = md("Tests or Procedures for Prostate Cancer")) %>%
    cols_label(Frequency = md("**N**"), 
               Percentage = md("**%**"), 
               Procedures = md("**Answer**")) %>%
    tab_options(stub.font.weight = "bold") %>%
    tab_style(
        style = list(cell_text(weight = "bold")),
        locations = cells_body(columns = Procedures)
    ) 


### Rectal Exam

#RECTEX1
screen$D_718137053 <- factor(screen$D_718137053, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_718137053, D_465056475_D_312250694, "1", "Timeframe of First Rectal Exam of Prostate")

#RECTEX2
screen$D_199704727 <- factor(screen$D_199704727, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_199704727, D_465056475_D_312250694, "1", "Number of Rectal Exams")

#RECTEX3
screen$D_621714179 <- factor(screen$D_621714179, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_621714179, D_199704727, "506053626","119809731", "282580702", "934779560","178420302", "Timeframe of Last Rectal Exam of Prostate")



### PSA Blood Test

#PSA1
screen$D_772645761 <- factor(screen$D_772645761, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_772645761, D_465056475_D_255054078, "1", "Timeframe of First PSA Blood Test")

#PSA2
screen$D_650508014 <- factor(screen$D_650508014, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_650508014, D_465056475_D_255054078, "1", "Number of PSA Blood Tests")

#PSA3
screen$D_903059223 <- factor(screen$D_903059223, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_903059223, D_650508014, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last PSA Blood Test")




### Sigmoidoscopy

#PROBIOP1
screen$D_214352460 <- factor(screen$D_214352460, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_214352460, D_465056475_D_492921091, "1", "Timeframe of First Sigmoidoscopy")

#PROBIOP2
screen$D_770939852 <- factor(screen$D_770939852, levels=c(236949684, 506053626, 462661976, 178420302, "Skipped this Question"))
one_logic_funct(D_770939852, D_465056475_D_492921091, "1", "Number of Sigmoidoscopies")

#PROBIOP3
screen$D_423202492 <- factor(screen$D_423202492, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
three_logic_funct(D_423202492, D_770939852, "506053626","462661976","178420302", "Timeframe of Last Sigmoidoscopy")



```




\newpage
# Breast Cancer Screening

```{r BRSTSCREEN, warning=FALSE, echo=FALSE, message=FALSE}

##BRSTSCREEN
br_scr_grid= screen  %>% filter(D_413039729==145235510 | D_413039729==801218076) %>% 
mutate(
    `Mammogram` = if_else(D_961267001_D_577887061 == 1, 1, 0),
    `Breast MRI` = if_else(D_961267001_D_419571068 == 1, 1, 0),
    `Breast Ultrasound` = if_else(D_961267001_D_726183532 == 1, 1, 0),
    `Breast Biopsy` = if_else(D_961267001_D_898042848 == 1, 1, 0),
    None = if_else(D_961267001_D_535003378 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_961267001_")) == 0 | is.na(select(., starts_with("D_961267001_")))) == ncol(select(., starts_with("D_961267001_"))), 1, 0)
)


pivot_br_scr <- br_scr_grid %>%
    select(`Mammogram`:Skipped) %>%
    pivot_longer(cols = everything(), names_to = "Procedures", values_to = "Selected") %>%
    filter(Selected == 1) %>%
    group_by(Procedures) %>%
    summarise(Frequency = n()) %>%
    ungroup() %>%
    mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

pivot_br_scr %>%
    gt() %>%
    fmt_number(columns = "Percentage", decimals = 2) %>% 
    fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
    tab_header(title = md("Tests or Procedures for Breast Cancer")) %>%
    cols_label(Frequency = md("**N**"), 
               Percentage = md("**%**"), 
               Procedures = md("**Answer**")) %>%
    tab_options(stub.font.weight = "bold") %>%
    tab_style(
        style = list(cell_text(weight = "bold")),
        locations = cells_body(columns = Procedures)
    ) 


### Mammogram

#MAMMO1
screen$D_745742553 <- factor(screen$D_745742553, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_745742553, D_961267001_D_577887061, "1", "Timeframe of First Mammogram")

#MAMMO2
screen$D_111580947 <- factor(screen$D_111580947, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_111580947, D_961267001_D_577887061, "1", "Number of Mammograms")

#MAMMO3
screen$D_709088568 <- factor(screen$D_709088568, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_709088568, D_111580947, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Mammogram")

#MAMMO4
five_logic_funct(D_372457715, D_111580947, "506053626","119809731","282580702","934779560","178420302", "Type at Last Mammogram")



### Breast MRI

#BRSTMRI1
screen$D_315184598 <- factor(screen$D_315184598, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_315184598, D_961267001_D_419571068, "1", "Timeframe of First Breast MRI")

#BRSTMRI2
screen$D_560107274 <- factor(screen$D_560107274, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_560107274, D_961267001_D_419571068, "1", "Number of Breast MRIs")

#BRSTMRI3
screen$D_569358384 <- factor(screen$D_569358384, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_569358384, D_560107274, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Breast MRI")



### Breast Ultrasound

#BRSTULTRA1
screen$D_305769587 <- factor(screen$D_305769587, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_305769587, D_961267001_D_726183532, "1", "Timeframe of First Breast Ultrasound")

#BRSTULTRA2
screen$D_434993234 <- factor(screen$D_434993234, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_434993234, D_961267001_D_726183532, "1", "Number of Breast Ultrasounds")

#BRSTULTRA3
screen$D_846067697 <- factor(screen$D_846067697, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_846067697, D_434993234, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Breast Ultrasound")





### Breast Biopsy

#BRSTBIOP1
screen$D_861488320 <- factor(screen$D_861488320, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_861488320, D_961267001_D_898042848, "1", "Timeframe of First Breast Biopsy")

#BRSTBIOP2
screen$D_891793989 <- factor(screen$D_891793989, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_891793989, D_961267001_D_898042848, "1", "Number of Breast Biopsies")

#BRSTBIOP3
screen$D_811848389 <- factor(screen$D_811848389, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_811848389, D_891793989, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Breast Biopsy")



```




\newpage
# Ovarian Cancer Screening

```{r OVSCREEN, warning=FALSE, echo=FALSE, message=FALSE}

##OVSCREEN
OV_grid= screen  %>% filter(D_890391968_D_434651539==1) %>% 
mutate(
    `Blood Test` = if_else(D_957875649_D_903156464 == 1, 1, 0),
    `Transvaginal Ultrasound` = if_else(D_957875649_D_474921307 == 1, 1, 0),
    None = if_else(D_957875649_D_535003378 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_957875649_")) == 0 | is.na(select(., starts_with("D_957875649_")))) == ncol(select(., starts_with("D_957875649_"))), 1, 0)
)


pivot_OV <- OV_grid %>%
    select(`Blood Test`:Skipped) %>%
    pivot_longer(cols = everything(), names_to = "Procedures", values_to = "Selected") %>%
    filter(Selected == 1) %>%
    group_by(Procedures) %>%
    summarise(Frequency = n()) %>%
    ungroup() %>%
    mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

pivot_OV %>%
    gt() %>%
    fmt_number(columns = "Percentage", decimals = 2) %>% 
    fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
    tab_header(title = md("Tests or Procedures for Ovarian Cancer")) %>%
    cols_label(Frequency = md("**N**"), 
               Percentage = md("**%**"), 
               Procedures = md("**Answer**")) %>%
    tab_options(stub.font.weight = "bold") %>%
    tab_style(
        style = list(cell_text(weight = "bold")),
        locations = cells_body(columns = Procedures)
    ) 


### Blood Test

#BLDOV1
screen$D_406370140 <- factor(screen$D_406370140, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_406370140, D_957875649_D_903156464, "1", "Timeframe of First Blood Test")

#BLDOV2
screen$D_951078002 <- factor(screen$D_951078002, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_951078002, D_957875649_D_903156464, "1", "Number of Blood Tests")

#BLDOV3
screen$D_631089527 <- factor(screen$D_631089527, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_631089527, D_951078002, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Blood Test")




### Transvaginal Ultrasound

#OTVULTRA1
screen$D_475018570 <- factor(screen$D_475018570, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_475018570, D_957875649_D_474921307, "1", "Timeframe of First Transvaginal Ultrasound")

#OTVULTRA2
screen$D_227617345 <- factor(screen$D_227617345, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_227617345, D_957875649_D_474921307, "1", "Number of Transvaginal Ultrasounds")

#OTVULTRA3
screen$D_274709835 <- factor(screen$D_274709835, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_274709835, D_227617345, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Transvaginal Ultrasound")



```






\newpage
# Cervical Cancer Screening

```{r CERVSCREEN, warning=FALSE, echo=FALSE, message=FALSE}

##CERVSCREEN
CERV_grid= screen  %>% filter(D_890391968_D_505282171==1) %>%
mutate(
    `HrHPV Test` = if_else(D_229764995_D_405616098 == 1, 1, 0),
    `Pap Test` = if_else(D_229764995_D_646114392 == 1, 1, 0),
    `Unknown Test` = if_else(D_229764995_D_673135412 == 1, 1, 0),
    None = if_else(D_229764995_D_535003378 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_229764995_")) == 0 | is.na(select(., starts_with("D_229764995_")))) == ncol(select(., starts_with("D_229764995_"))), 1, 0)
)


pivot_CERV <- CERV_grid %>%
    select(`HrHPV Test`:Skipped) %>%
    pivot_longer(cols = everything(), names_to = "Procedures", values_to = "Selected") %>%
    filter(Selected == 1) %>%
    group_by(Procedures) %>%
    summarise(Frequency = n()) %>%
    ungroup() %>%
    mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

pivot_CERV %>%
    gt() %>%
    fmt_number(columns = "Percentage", decimals = 2) %>% 
    fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
    tab_header(title = md("Tests or Procedures for Ovarian Cancer")) %>%
    cols_label(Frequency = md("**N**"), 
               Percentage = md("**%**"), 
               Procedures = md("**Answer**")) %>%
    tab_options(stub.font.weight = "bold") %>%
    tab_style(
        style = list(cell_text(weight = "bold")),
        locations = cells_body(columns = Procedures)
    ) 


### HrHPV Test

#CHRHPV1
screen$D_934385625 <- factor(screen$D_934385625, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_934385625, D_229764995_D_405616098, "1", "Timeframe of First HrHPV Test")

#CHRHPV2
screen$D_393386163 <- factor(screen$D_393386163, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_393386163, D_229764995_D_405616098, "1", "Number of HrHPV Tests")

#CHRHPV3
screen$D_856699079 <- factor(screen$D_856699079, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_856699079, D_393386163, "506053626","119809731", "282580702", "934779560","178420302", "Timeframe of Last HrHPV Test")




### Pap Test

#CPAP1
screen$D_723960145 <- factor(screen$D_723960145, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_723960145, D_229764995_D_646114392, "1", "Timeframe of First Pap Test")

#CPAP2
screen$D_353889236 <- factor(screen$D_353889236, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_353889236, D_229764995_D_646114392, "1", "Number of Pap Tests")

#CPAP3
screen$D_242001363 <- factor(screen$D_242001363, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_242001363, D_353889236, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Pap Test")




### Unknown Test

#CERVIDK1
screen$D_623413449 <- factor(screen$D_623413449, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_623413449, D_229764995_D_673135412, "1", "Timeframe of First Unknown Test")

#CERVIDK2
screen$D_153215425 <- factor(screen$D_153215425, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_153215425, D_229764995_D_673135412, "1", "Number of Unknown Tests")

#CERVIDK3
screen$D_115504049 <- factor(screen$D_115504049, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_115504049, D_153215425, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Unknown Test")



```





\newpage
# Endometrial Cancer Screening

```{r ENDOSCREEN, warning=FALSE, echo=FALSE, message=FALSE}

##ENDOSCREEN
ENDO_grid= screen  %>% filter(D_890391968_D_578416151==1) %>%
mutate(
    `Transvaginal Ultrasound` = if_else(D_356470898_D_687879041 == 1, 1, 0),
    `Hysteroscopy` = if_else(D_356470898_D_531274737 == 1, 1, 0),
    `Endometrial Biopsy` = if_else(D_356470898_D_650022485 == 1, 1, 0),
    `Dilation and Curettage` = if_else(D_356470898_D_891052313 == 1, 1, 0),
    None = if_else(D_356470898_D_535003378 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_356470898_")) == 0 | is.na(select(., starts_with("D_356470898_")))) == ncol(select(., starts_with("D_356470898_"))), 1, 0)
)


pivot_ENDO <- ENDO_grid %>%
    select(`Transvaginal Ultrasound`:Skipped) %>%
    pivot_longer(cols = everything(), names_to = "Procedures", values_to = "Selected") %>%
    filter(Selected == 1) %>%
    group_by(Procedures) %>%
    summarise(Frequency = n()) %>%
    ungroup() %>%
    mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

pivot_ENDO %>%
    gt() %>%
    fmt_number(columns = "Percentage", decimals = 2) %>% 
    fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
    tab_header(title = md("Tests or Procedures for Endometrial Cancer")) %>%
    cols_label(Frequency = md("**N**"), 
               Percentage = md("**%**"), 
               Procedures = md("**Answer**")) %>%
    tab_options(stub.font.weight = "bold") %>%
    tab_style(
        style = list(cell_text(weight = "bold")),
        locations = cells_body(columns = Procedures)
    ) 


### Transvaginal Ultrasound

#ETVULTRA1
screen$D_947994136 <- factor(screen$D_947994136, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_947994136, D_356470898_D_687879041, "1", "Timeframe of First Transvaginal Ultrasound")

#ETVULTRA2
screen$D_898341670 <- factor(screen$D_898341670, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_898341670, D_356470898_D_687879041, "1", "Number of Transvaginal Ultrasounds")

#ETVULTRA3
screen$D_913107034 <- factor(screen$D_913107034, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_913107034, D_898341670, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Transvaginal Ultrasound")




### Hysteroscopy

#HYSTERO1
screen$D_655198446 <- factor(screen$D_655198446, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_655198446, D_356470898_D_531274737, "1", "Timeframe of First Hysteroscopy")

#HYSTERO2
screen$D_809308794 <- factor(screen$D_809308794, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_809308794, D_356470898_D_531274737, "1", "Number of Hysteroscopies")

#HYSTERO3
screen$D_766549014 <- factor(screen$D_766549014, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_766549014, D_809308794, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Hysteroscopy")




### Endometrial Biopsy

#ENDOBIOP1
screen$D_496588916 <- factor(screen$D_496588916, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_496588916, D_356470898_D_650022485, "1", "Timeframe of First Endometrial Biopsy")

#ENDOBIOP2
screen$D_104842019 <- factor(screen$D_104842019, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_104842019, D_356470898_D_650022485, "1", "Number of Endometrial Biopsies")

#ENDOBIOP3
screen$D_315199788 <- factor(screen$D_315199788, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_315199788, D_104842019, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Endometrial Biopsy")




### Dilation and Curettage

#DILCUR1
screen$D_249853484 <- factor(screen$D_249853484, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_249853484, D_356470898_D_891052313, "1", "Timeframe of First Dilation and Curettage")

#DILCUR2
screen$D_391300412 <- factor(screen$D_391300412, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_391300412, D_356470898_D_891052313, "1", "Number of Dilation and Curettages")

#DILCUR3
screen$D_808990505 <- factor(screen$D_808990505, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_808990505, D_391300412, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Dilation and Curettage")




```







\newpage
# Multi-Cancer Screening

```{r MULTISCREEN, warning=FALSE, echo=FALSE, message=FALSE}

##ENDOSCREEN
MULTI_grid= screen  %>% 
mutate(
    `MCED Test` = if_else(D_219076879_D_875157431 == 1, 1, 0),
    `Full body MRI or CT` = if_else(D_219076879_D_309925717 == 1, 1, 0),
    None = if_else(D_219076879_D_535003378 == 1, 1, 0),
    Skipped = if_else(rowSums(select(., starts_with("D_219076879_")) == 0 | is.na(select(., starts_with("D_219076879_")))) == ncol(select(., starts_with("D_219076879_"))), 1, 0)
)


pivot_MULTI <- MULTI_grid %>%
    select(`MCED Test`:Skipped) %>%
    pivot_longer(cols = everything(), names_to = "Procedures", values_to = "Selected") %>%
    filter(Selected == 1) %>%
    group_by(Procedures) %>%
    summarise(Frequency = n()) %>%
    ungroup() %>%
    mutate(Percentage = 100 * Frequency / sum(Frequency)) %>% 
  arrange(desc(Frequency))

pivot_MULTI %>%
    gt() %>%
    fmt_number(columns = "Percentage", decimals = 2) %>% 
    fmt_number(column = "Frequency", decimals=0, use_seps = TRUE) %>%
    tab_header(title = md("Tests or Procedures for Multiple Cancer Types")) %>%
    cols_label(Frequency = md("**N**"), 
               Percentage = md("**%**"), 
               Procedures = md("**Answer**")) %>%
    tab_options(stub.font.weight = "bold") %>%
    tab_style(
        style = list(cell_text(weight = "bold")),
        locations = cells_body(columns = Procedures)
    ) 


### MCED Test

#MCED1
screen$D_822790675 <- factor(screen$D_822790675, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_822790675, D_219076879_D_875157431, "1", "Timeframe of First MCED Test")

#MCED2
screen$D_459223565 <- factor(screen$D_459223565, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_459223565, D_219076879_D_875157431, "1", "Number of MCED Tests")

#MCED3
screen$D_397748152 <- factor(screen$D_397748152, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_397748152, D_459223565, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last MCED Test")




### Full body MRI or CT

#FBODMRI1
screen$D_553034408 <- factor(screen$D_553034408, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
one_logic_funct(D_553034408, D_219076879_D_309925717, "1", "Timeframe of First Full body MRI or CT")

#FBODMRI2
screen$D_698242759 <- factor(screen$D_698242759, levels=c(236949684, 506053626, 119809731, 282580702, 934779560, 178420302, "Skipped this Question"))
one_logic_funct(D_698242759, D_219076879_D_309925717, "1", "Number of Full body MRI or CT Scans")

#FBODMRI3
screen$D_695772621 <- factor(screen$D_695772621, levels=c(461386928, 729845236, 669023414, 786431761, 640520411, 178420302, "Skipped this Question"))
five_logic_funct(D_695772621, D_698242759, "506053626","119809731","282580702","934779560","178420302", "Timeframe of Last Full body MRI or CT")



```


