---
title: "Connect Weekly Survey Module Metrics"
author: "Kelsey Sanchez"
date: 'Data Extracted and Report Ran: `r Sys.Date()`'
header-includes: 
  \usepackage[labelformat=empty]{caption} 
  \usepackage{placeins} 
  \usepackage{booktabs}
  \usepackage{pdflscape}
  
output:
  pdf_document:
    latex_engine: xelatex
    extra_dependencies: ["float"]
    toc: yes
    keep_tex: yes
    fig_width: 7
    fig_height: 5
    fig_caption: yes
    df_print: paged
---








This Weekly Survey Module report contains metrics related to Connect survey completion including baseline surveys and follow up surveys. Additional metrics will be added as new surveys are released. Metrics related to the baseline biospecimen surveys, menstrual cycle survey, and COVID survey can be found in the Weekly Biospecimen Metrics reports. Metrics related to overall baseline study activity completion, including baseline survey completion, can be found in the Weekly Operations Report. The Survey Module report is run on a weekly basis and encompasses data through today at 9:30 am. This data is extracted from the flattened participants table.


```{r libraries, include=FALSE, warning=FALSE}

 # \usepackage{caption}
 # \captionsetup[figure]{labelformat=empty}


#old.packages()
#update.packages("tinytex")


library(bigrquery)
library(dplyr)
library(gmodels)
library(epiDisplay)
library(lubridate)
library(tidyverse)
library(knitr)
#install_tinytex()
library(tinytex)
#library(vtable)
library(kableExtra)
library(gtsummary)
library(data.table)


library(arsenal)
library(rio)
library(scales)
library(gt)
library(stringr) 


bq_auth()

```



```{r BQPull, include=FALSE}
knitr::opts_chunk$set(dev = "png", fig.path = "", comment = NA)

#knitr::opts_chunk$set(comment = NA)

project = "nih-nci-dceg-connect-prod-6d04"
queryreccc <- "SELECT  Connect_ID, d_512820379, d_821247024, d_914594314, d_832139544, d_949302066 , d_205553981, 
d_536735468 , d_976570371, d_663265240, d_265193023, d_222161762,d_770257102, d_264644252, d_265193023, d_541836531, 
d_386488297, d_452942800, d_517311251 , d_822499427, d_126331570, d_914639140, d_311580100, d_827220437, d_100767870, 
d_831041022, d_255077064, d_320303124, d_684635302, d_843688458, d_870643066, d_878865966, d_167958071, token,
state_d_934298480, state_d_706256705, state_d_435027713, d_199471989, d_956490759, d_263355177,
state_d_684926335, state_d_849518448, state_d_119643471, state_d_253532712, d_764863765, d_195145666, d_784810139
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` where Connect_ID IS NOT NULL  and (d_512820379='486306141' OR d_512820379='854703046') " 

#and d_831041022='104430631'-- not needed, according to 3/12/24 decisions we'll be keeping participant journeys in overall counts

rec_table_cc <- bq_project_query(project, queryreccc)
data_c <- bq_table_download(rec_table_cc, bigint = "integer64")


#need this separate filter to look at participants unable to be verified
data_ccc <- data_c %>%  filter(d_821247024==197316935) 


data_tib= as_tibble(data_ccc) 


modules <- data_tib[,c("Connect_ID","d_512820379","d_949302066","d_536735468","d_976570371","d_663265240", "d_914594314")] 
mods <- c("d_949302066","d_536735468","d_976570371","d_663265240")
modules$modules <- 0
modules$none <-0
for(i in 1:length(mods)){
  module <- modules[,mods[i]]
  count <- ifelse((!is.na(module) & module ==231311385), 1, 0)
  modules$modules <- count+modules$modules
  count1 <- ifelse((!is.na(module) & module==972455046), 1, 0)
  modules$none <- count1+modules$none
}



length(modules[which(modules$modules==3 & modules$d_663265240==231311385 & modules$d_536735468==231311385),])

modules1 <- modules %>% mutate(process = case_when(as.character(modules) =='0' ~ "None",
                                                   d_949302066 == '231311385' & as.character(modules) == '1' ~ "BOH Section only",
                                                   as.character(modules) == '2' & d_949302066 == '231311385' & d_536735468 == '231311385' ~ "BOH and MRE Sections" ,
                                                   as.character(modules) =='2' & d_949302066 == '231311385' & d_976570371 == '231311385' ~ "BOH and SAS Sections" , 
                                                   as.character(modules) =='2' & d_949302066 == '231311385' & d_663265240 == '231311385' ~ "BOH and LAW Sections" ,  
                                                   as.character(modules) =='3' & d_949302066 == '231311385' & d_536735468 == '231311385' & d_976570371 == '231311385' ~ "BOH, MRE, and SAS Sections" ,  
                                                   as.character(modules) =='3' & d_949302066 == '231311385' & d_976570371 == '231311385' & d_663265240 == '231311385'~ "BOH, SAS, and LAW Sections" , 
                                                   as.character(modules) =='3' & d_949302066 == '231311385' & d_536735468 == '231311385' & d_663265240 == '231311385' ~ "BOH, MRE, and LAW Sections",   
                                                   as.character(modules) =='4' ~ "All")) 

tab1(modules1$process, decimal=2,sort.group = "decreasing", cum.percent = TRUE)$output.table


#completion <- modules1 %>% select(Connect_ID, process) #have no idea why this isn't working
completion <- modules1[, c(1,10)]
all_data <- left_join(data_tib, completion, by="Connect_ID")


all_data <- all_data %>%  mutate(Site = case_when(d_827220437==472940358 ~ "Baylor Scott and White Health",
                                                  d_827220437==125001209 ~ "KP Colorado",
                                                  d_827220437==327912200 ~ "KP Georgia",
                                                  d_827220437==300267574 ~ "KP Hawaii",
                                                  d_827220437==452412599 ~ "KP Northwest",
                                                  d_827220437==548392715 ~ "Henry Ford",
                                                  d_827220437==531629870 ~ "HealthPartners",
                                                  d_827220437==303349821 ~ "Marshfield",
                                                  d_827220437==657167265 ~ "Sanford",
                                                  d_827220437==809703864 ~ "UChicago"),
                                 BL_comp = case_when(d_100767870==353358909 ~ "All",
                                                     process=="None" ~ "None",
                                                     process=="BOH Section only" ~ "BOH Only",
                                                     TRUE ~ "2 or 3 Sections"),
                                 age = case_when(state_d_934298480 == "713781738"~ "30-34",
                                                 state_d_934298480 == '631272782' ~ "35-39",
                                                 state_d_934298480 == '124276120' ~ "40-45",
                                                 state_d_934298480 == '450985724' ~ "46-50",
                                                 state_d_934298480 == '363147933' ~ "51-55",
                                                 state_d_934298480 == '636706443' ~ "56-60",
                                                 state_d_934298480 == '771230670' ~ "61-65",
                                                 state_d_934298480 == '722846087' ~ "66-70"),
                                 race = case_when(state_d_684926335 == '635279662' |state_d_849518448 == '768826601' | state_d_119643471 == '635279662' | state_d_253532712=='723775357' ~ "White, Non-Hispanic" , 
                                                  state_d_684926335 %in% c('232334767', '401335456') |
                                                    state_d_849518448 == '181769837' |
                                                    state_d_253532712 %in% c('153444133','572474909','308427446','211228524','277568192','611398522','181769837') |
                                                    state_d_119643471 %in% c( '232334767','211228524','308427446','432722256','232663805','785578696','200929978','490725843','965998904') ~ "Other",
                                                  state_d_684926335 == '178420302'  | 
                                                    state_d_849518448 == '178420302' | 
                                                    state_d_253532712 == '178420302' |
                                                    state_d_119643471  %in% c( '986445321','746038746','178420302') |
                                                    (is.na(state_d_119643471) & d_827220437 == '657167265') ~ "Unknown"),
                                 sex = case_when(state_d_706256705 == '536341288' | state_d_435027713 == '536341288' ~ "Female",
                                                 state_d_706256705 == '654207589' | state_d_435027713 == '654207589' ~ "Male",
                                                 #state_d_706256705 == '830573274' ~ "Intersex or Other", # too small of a count for now, need to combine with unknown 
                                                 state_d_706256705 == '830573274' | state_d_706256705 == '178420302' | state_d_435027713 == '178420302' ~ "Unknown"),
                                 BSL_compl = case_when(d_100767870==353358909 ~ "All Baseline Modules Completed",
                                                       TRUE ~ "One or More Baseline Modules Not Completed"),
                                 Pref_lang=case_when(d_255077064 == 773342525 ~ "Spanish",
                                                     TRUE ~ "English"),
                                 Recruit_Type= case_when(d_512820379==486306141 ~ "Active",
                                                  d_512820379==854703046 ~ "Passive"),
                                 qolcomplt = ifelse(d_320303124 == 231311385 ,"Submitted",
                                                    ifelse(d_320303124 == 615768760, "Started",
                                                           ifelse(as.numeric(difftime(Sys.Date(), as.POSIXct(ymd_hms(d_914594314)),
                                                                                      units="days")) < 90, "Not Eligible",
                                                                  ifelse(d_320303124 == 972455046, "Not Started", "Error")))),
                                 completion = case_when(d_100767870=="353358909" & 
                                                          (d_878865966=="353358909" | d_684635302=="353358909" | d_167958071=="353358909") ~ "Completed both survey and sample(s)",
                                                        d_100767870=="353358909" ~ "Completed all baseline survey modules 1-4, no baseline samples",
                                                        (d_878865966=="353358909" | d_684635302=="353358909" | 
                                                           d_167958071=="353358909") ~ "Completed any baseline sample, did not complete baseline survey",
                                                        TRUE ~ "Completed neither survey or sample(s)"),
                                 provided4 =case_when(d_311580100==353358909 ~ "Full SSN",
                                                     d_914639140==353358909 ~ "Partial SSN",
                                                     TRUE ~ "No SSN"),
                                 ssn_started=case_when(d_126331570==615768760 ~ "Started",
                                                       d_126331570==231311385 ~ "Submitted",
                                                       TRUE ~ "Not Started"),
                                 CES_status = case_when(d_956490759==972455046	~ "Not Started",
                                                        d_956490759==615768760	~ "Started",
                                                        d_956490759==231311385	~ "Submitted",
                                                        TRUE ~ "Not Eligible"),
                                 m1_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_517311251)), as.POSIXct(ymd_hms(d_205553981)), units="hours"))*60,
                                 m2_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_832139544)), as.POSIXct(ymd_hms(d_541836531)), units="hours"))*60,
                                 m3_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_770257102)), as.POSIXct(ymd_hms(d_386488297)), units="hours"))*60,
                                 m4_comp_mins = as.numeric(difftime(as.POSIXct(ymd_hms(d_264644252)), as.POSIXct(ymd_hms(d_452942800)), units="hours"))*60)

all_data$Site <- factor(all_data$Site, levels=c("Baylor Scott and White Health","HealthPartners", "Henry Ford","Marshfield","Sanford","UChicago","KP Colorado","KP Georgia", "KP Hawaii","KP Northwest"))
all_data$BL_comp <- factor(all_data$BL_comp, levels=c("All", "2 or 3 Sections", "BOH Only", "None"))
all_data$completion <- factor(all_data$completion, levels=c("Completed both survey and sample(s)", "Completed all baseline survey modules 1-4, no baseline samples", 
                                                  "Completed any baseline sample, did not complete baseline survey","Completed neither survey or sample(s)"))
all_data$process <- factor(all_data$process, levels=c("None", "BOH Section only", "BOH and MRE Sections", "BOH and SAS Sections",  "BOH and LAW Sections", 
                                                      "BOH, MRE, and SAS Sections", "BOH, SAS, and LAW Sections", "BOH, MRE, and LAW Sections"))
all_data$provided4<- factor(all_data$provided4,levels=c("Full SSN", "Partial SSN", "No SSN"))

```


```{r Functions, include=FALSE}

create_tbl_cross1 <- function(data,row_var, colm_var, row_or_col_pct, row_name, column_name){
cross__table <- data %>%  
  tbl_cross(
    row = !!sym(row_var),
    col = !!sym(colm_var),
    digits=c(0,2),
    percent = row_or_col_pct,
    label=list(!!sym(row_var) ~ row_name,
               !!sym(colm_var) ~ column_name),
    missing="ifany",
    margin_text="Total") 

#Ops doesn't like the grouped by variables on a different line the column labels
cross_table_df <- as.data.frame(cross__table)[-1, ]
  
}



create_tbl_cross2 <- function(data, row_var, colm_var, row_or_col_pct, row_name, column_name, margin_text) {
  cross__table <- data %>%
    tbl_cross(
      row = !!sym(row_var),
      col = !!sym(colm_var),
      label = list(!!sym(row_var) ~ row_name,
                   !!sym(colm_var) ~ column_name),
      percent = row_or_col_pct,
      digits = c(0, 2),
      margin_text = margin_text
    )
  
  # Check if table_body exists and has data
  if (!is.null(cross__table[["table_body"]]) && nrow(cross__table[["table_body"]]) > 0) {
    # Need only the total column to be a column percentage
    cross__table[["table_body"]]$stat_0 <- sapply(strsplit(cross__table[["table_body"]]$stat_0, " "), "[", 1)
    
    cross__table_df <- as.data.frame(cross__table)[2:nrow(as.data.frame(cross__table)), ]
    colnames(cross__table_df)[1] <- row_name
    
    # Ensure 'Total Verified Participants' exists before modifying
    if ("Total Verified Participants" %in% colnames(cross__table_df)) {
      cross__table_df$`Total Verified Participants` <- as.numeric(gsub(",", "", cross__table_df$`Total Verified Participants`))
      
      total_participants <- cross__table_df$`Total Verified Participants`
      percentages <- round((total_participants / total_participants[length(total_participants)]) * 100, digits = 2)
      
      cross__table_df$`Total Verified Participants` <- paste0(format(total_participants, big.mark = ","), " (", percentages, "%)")
    }
    
    colnames(cross__table_df)[ncol(cross__table_df)] <- "Total Verified \n Participants"
    return(cross__table_df)
  } else {
    warning("The cross table is empty or missing table_body.")
    return(data.frame()) # Return an empty data frame if table_body is missing
  }
}


```



\newpage
# Baseline Survey

Starting July 5th, 2022, all four Initial Survey Modules were in MyConnect. In order of how the sections appear on MyConnect, the Initial Survey Sections are:  

BOH= Background and Overall Health (Module 1)  

LAW= Where you Live and Work (Module 4)

MRE= Medications, Reproductive Health, Exercise, and Sleep (Module 2)

SAS= Smoking, Alcohol, and Sun Exposure (Module 3)
```{r newTable1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

comp_by_site_totals <- create_tbl_cross1(all_data,"Site", "BSL_compl", "row", "Site", " ")

total_rows <- nrow(comp_by_site_totals)
knitr::kable(comp_by_site_totals , 
             caption='Table 1. Completion of Initial Surveys by Site', 
             row.names=FALSE,align=c("l","c","c","c"),
             col.names=c("Site", "All Completed", "One or More Not Completed", "Total"),
             booktabs = TRUE) %>%  
  add_indent(seq(1, total_rows - 1))  %>% 
  kable_styling(latex_options = c("scale_down","hold_position")) # %>%  column_spec(3:4, width = "4cm")


```


 
 \newpage
 
```{r Table2, echo=FALSE, warning=FALSE, message=FALSE}

all_srvy_comp_totals <- create_tbl_cross1(all_data,"process", "Recruit_Type", "column", "Sections Submitted", " ")


overall_surveys <- knitr::kable(all_srvy_comp_totals ,
                                col.names=c("Sections Submitted", "Active Verified","Passive Verified", "Total Verified"), 
                                caption='Table 1.2. Initial Survey Submission Among Verified Participants \n Stratified by Active and Passive Recruits', 
                                row.names=FALSE,align=c("l","c","c","c"), booktabs = TRUE) %>%  
  add_indent(seq(1, nrow(all_srvy_comp_totals) - 1))  %>%
  kable_styling(latex_options = c("scale_down","hold_position"))

add_footnote(overall_surveys, "Note: All sections were in MyConnect on July 5,2022. There were 766 verified participants beore that date.", notation = "none")

```


```{r Table3, echo=FALSE, warning=FALSE, message=FALSE}

calculate_counts <- function(df, column_name, row_label) {
  total_rows <- dim(df)[[1]]
  value_counts <- sapply(c(972455046, 615768760, 231311385), function(value) {
    count <- sum(df[[column_name]] == value)
    formatted_count <- formatC(count, format = "f", big.mark = ",", digits = 0)
    percentage <- round(100 * count / total_rows, 1)
    paste0(formatted_count, " (", percentage, "%)")
  })
  total_label <- paste(formatC(total_rows, format = "f", big.mark = ",", digits = 0), "(100%)")
  c(row_label, value_counts, total_label)
}


section_comp <- data.frame(matrix(ncol =5, nrow = 4))


section_comp[1, ] <- calculate_counts(all_data, "d_949302066", "BOH")
section_comp[2, ] <- calculate_counts(all_data, "d_536735468", "MRE")
section_comp[3, ] <- calculate_counts(all_data, "d_976570371", "SAS")
section_comp[4, ] <- calculate_counts(all_data, "d_663265240", "LAW")


colnames(section_comp) <- c("Section", "Not Started", "Started", "Submitted", "Total Verified Participants")


knitr::kable(section_comp, 
             caption='Table 1.3: Initial Survey Section Submission Status Among Verified Participants', 
             col.names=c("Section", "Not Started", "Started", "Submitted", "Total Verified Participants"), 
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>% 
  kable_styling(latex_options = c("scale_down","hold_position"))


```






\newpage
\FloatBarrier


```{r Table4.1, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, results='asis'}


all_data <- all_data %>% group_by(Connect_ID) %>% mutate(last_mod_ts = max(d_832139544, d_770257102, d_264644252)) %>% ungroup()

all_data <- all_data %>% mutate(ver_M1 = as.numeric(difftime(as.POSIXct(ymd_hms(d_517311251)), as.POSIXct(ymd_hms(d_914594314)), units="hours")),
                                ver_M2 = as.numeric(difftime(as.POSIXct(ymd_hms(d_832139544)), as.POSIXct(ymd_hms(d_914594314)), units="hours")),
                                ver_M3 = as.numeric(difftime(as.POSIXct(ymd_hms(d_770257102)), as.POSIXct(ymd_hms(d_914594314)), units="hours")),
                                ver_M4 = as.numeric(difftime(as.POSIXct(ymd_hms(d_264644252)), as.POSIXct(ymd_hms(d_914594314)), units="hours")),
                                ver_last = as.numeric(difftime(as.POSIXct(ymd_hms(last_mod_ts)), as.POSIXct(ymd_hms(d_914594314)), units="hours")),
                                ver_M1_mins=ver_M1*60,
                                ver_M2_mins=ver_M2*60,
                                ver_M3_mins=ver_M3*60,
                                ver_M4_mins=ver_M4*60)


Table4a = all_data %>% group_by(Recruit_Type) %>% filter(d_949302066==231311385) %>% 
  dplyr::summarize('N'=n(),
                   Min = min(ver_M1, na.rm = TRUE),
                   Q1 = quantile(ver_M1, 0.25, na.rm = TRUE),
                   Median = median(ver_M1, na.rm = TRUE),
                   Mean = mean(ver_M1, na.rm = TRUE), 
                   SD= sd(ver_M1, na.rm = TRUE),
                   Q3 = quantile(ver_M1, 0.75, na.rm = TRUE),
                   'Perc.85' = quantile(ver_M1, 0.85, na.rm = TRUE),
                   'Perc.90' = quantile(ver_M1, 0.90, na.rm = TRUE),
                   'Perc.95' = quantile(ver_M1, 0.95, na.rm = TRUE),
                   Max = max(ver_M1, na.rm = TRUE)) 


Table4a2 = all_data %>% filter(d_949302066==231311385) %>% 
  dplyr::summarize('N'=n(),
                   Min = min(ver_M1, na.rm = TRUE),
                   Q1 = quantile(ver_M1, 0.25, na.rm = TRUE),
                   Median = median(ver_M1, na.rm = TRUE),
                   Mean = mean(ver_M1, na.rm = TRUE), 
                   SD= sd(ver_M1, na.rm = TRUE),
                   Q3 = quantile(ver_M1, 0.75, na.rm = TRUE),
                   'Perc.85' = quantile(ver_M1, 0.85, na.rm = TRUE),
                   'Perc.90' = quantile(ver_M1, 0.90, na.rm = TRUE),
                   'Perc.95' = quantile(ver_M1, 0.95, na.rm = TRUE),
                   Max = max(ver_M1, na.rm = TRUE)) 


Table4a1 <- Table4a #need to keep Table4a's first column name consistent to bind it later in the code
names(Table4a1)[1] <- "Recruit Type"





knitr::kable(Table4a1,format.args = list(big.mark = ","),
             caption='Table 1.4.a. Time (in hours) from Verification to BOH Submission \n Stratified by Active and Passive Recruits', 
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c"),digits=2, booktabs = TRUE)%>% 
  kable_styling(latex_options = "scale_down", full_width = FALSE, font_size=8) 


knitr::kable(Table4a2,format.args = list(big.mark = ","),
             caption='Table 1.4.b. Time (in hours) from Verification to BOH Submission for All Participants',
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c"),digits=2, booktabs = TRUE)%>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 
```


```{r Table5, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE}




summarize_data <- function(data, filter_column, filter_value, target_column) {
  data %>% 
    filter(!!sym(filter_column) == filter_value) %>% 
    summarize('N' = n(),
              Min = min(!!sym(target_column), na.rm = TRUE),
              Q1 = quantile(!!sym(target_column), 0.25, na.rm = TRUE),
              Median = median(!!sym(target_column), na.rm = TRUE),
              Mean = mean(!!sym(target_column), na.rm = TRUE), 
              SD = sd(!!sym(target_column), na.rm = TRUE),
              Q3 = quantile(!!sym(target_column), 0.75, na.rm = TRUE),
              'Perc.85' = quantile(!!sym(target_column), 0.85, na.rm = TRUE),
              'Perc.90' = quantile(!!sym(target_column), 0.90, na.rm = TRUE),
              'Perc.95' = quantile(!!sym(target_column), 0.95, na.rm = TRUE),
              Max = max(!!sym(target_column), na.rm = TRUE))
}


Table4b <- summarize_data(all_data, "d_536735468", 231311385, "ver_M2")
Table4c <- summarize_data(all_data, "d_976570371", 231311385, "ver_M3")
Table4d <- summarize_data(all_data, "d_663265240", 231311385, "ver_M4")
Table4e <- summarize_data(all_data, "d_100767870", 353358909, "ver_last")



### Table4a2 in previous chunk
tb5boh <- as.data.frame(Table4a2)
table4 <- rbind(tb5boh, Table4b, Table4c, Table4d, Table4e)



table4<- table4[, c(1:7, 9, 11)]
table4[,10] <- c("BOH", "MRE", "SAS", "LAW", "All")
table4<- table4[, c(10,1:9)]
colnames(table4)[1] <- "Section"


knitr::kable(table4,format.args = list(big.mark = ","),
             caption='Table 1.5. Time (in hours) from Verification to Initial Survey Module Submission',
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c"),digits=2, booktabs = TRUE)%>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 

```



\FloatBarrier





\newpage



```{r Submission_Minutes,include=FALSE}



process_module <- function(data, start_time, end_time, completion_flag, completion_status, module_name) {
  
  
  data <- data %>%
    filter(!!sym(completion_flag) == completion_status)
  
  
  comp_tm <- as.numeric(difftime(as.POSIXct(ymd_hms(data[[start_time]])), 
                                 as.POSIXct(ymd_hms(data[[end_time]])), 
                                 units = "hours"))
  
  
  data <- data %>%
    mutate(comp_mins = comp_tm * 60,
           time_frame = case_when(
             comp_mins < 5 ~ "Under 5 minutes",
             comp_mins < 10 ~ "5 to 10 minutes",
             comp_mins < 15 ~ "10 to 15 minutes",
             comp_mins < 20 ~ "15 to 20 minutes",
             comp_mins < 30 ~ "20 to 30 minutes",
             comp_mins < 45 ~ "30 to 45 minutes",
             comp_mins < 60 ~ "45 to 60 minutes",
             comp_mins >= 60 ~ "60 minutes+",
             is.na(data[[start_time]]) | is.na(data[[end_time]]) ~ "Missing Time Stamp(s)"
           ))
  
  data$time_frame <- factor(data$time_frame, levels = c(
    "Under 5 minutes", "5 to 10 minutes", "10 to 15 minutes",
    "15 to 20 minutes", "20 to 30 minutes", "30 to 45 minutes",
    "45 to 60 minutes", "60 minutes+", "Missing Time Stamp(s)"
  ))
  
  summary_data <- data %>%
    group_by(time_frame) %>%
    summarize(n = n(), percentage = 100 * n / nrow(data)) %>%
    ungroup() %>%
    mutate(cumulative_percentage = cumsum(percentage)) %>%
    select(time_frame, n, percentage, cumulative_percentage)
  
  summary_row <- summary_data %>%
    summarize(n = sum(n), percentage = 100, 
              cumulative_percentage = 100,
              time_frame = "Total")
  
  summary_data <- bind_rows(summary_data, summary_row)
  
  table_summary <- summary_data %>%
    mutate(np = paste0(n, " (", round(percentage, digits = 2), "%)"),
           cumulative_percentage = paste0(round(cumulative_percentage, digits = 2), "%")) %>%
    select(time_frame, np, cumulative_percentage)
  
  knitr::kable(table_summary, 
               caption = paste0('Table ', module_name, ' Section Initial Survey Submission Time \n from Start to Submit for Verified Participants'), 
               col.names = c("Submission Time", "Total Participants", "Cumulative Percentage"), 
               row.names = FALSE, align = c("l", "c"), digits = 1, booktabs = TRUE) %>%  
    add_indent(seq(1, nrow(table_summary) - 1)) %>% 
    kable_styling(latex_options = "scale_down") #c("scale_down","hold_position"))
}


table6.1_sum <- process_module(all_data, "d_517311251", "d_205553981", "d_949302066", 231311385, "1.6.a. BOH")
table6.2_sum <- process_module(all_data, "d_832139544", "d_541836531", "d_536735468", 231311385, "1.6.b. MRE")
table6.3_sum <- process_module(all_data, "d_770257102", "d_386488297", "d_976570371", 231311385, "1.6.c. SAS")
table6.4_sum <- process_module(all_data, "d_264644252", "d_452942800", "d_663265240", 231311385, "1.6.d. LAW")


```


```{r BL_comp_time,echo=FALSE,error=FALSE,message=FALSE,warning=FALSE,results='asis'}
table6.1_sum
table6.2_sum
table6.3_sum
```

\newpage
```{r LAW_comp_time,echo=FALSE,error=FALSE,message=FALSE,warning=FALSE,results='asis'}
table6.4_sum
```



\FloatBarrier

```{r Table7,echo=FALSE,error=FALSE,message=FALSE,warning=FALSE,results='asis'}



summarize_data <- function(data, filter_column, filter_value, target_column) {
  data %>% 
    filter(!!sym(filter_column) == filter_value) %>% 
    summarize('N' = n(),
              Min = min(!!sym(target_column), na.rm = TRUE),
              Q1 = quantile(!!sym(target_column), 0.25, na.rm = TRUE),
              Median = median(!!sym(target_column), na.rm = TRUE),
              Mean = mean(!!sym(target_column), na.rm = TRUE), 
              SD = sd(!!sym(target_column), na.rm = TRUE),
              Q3 = quantile(!!sym(target_column), 0.75, na.rm = TRUE),
              'Perc.85' = quantile(!!sym(target_column), 0.85, na.rm = TRUE),
              'Perc.90' = quantile(!!sym(target_column), 0.90, na.rm = TRUE),
              'Perc.95' = quantile(!!sym(target_column), 0.95, na.rm = TRUE),
              Max = max(!!sym(target_column), na.rm = TRUE))
}

Table7a <- summarize_data(all_data, "d_949302066", 231311385, "m1_comp_mins")
Table7b <- summarize_data(all_data, "d_536735468", 231311385, "m2_comp_mins")
Table7c <- summarize_data(all_data, "d_976570371", 231311385, "m3_comp_mins")
Table7d <- summarize_data(all_data, "d_663265240", 231311385, "m4_comp_mins")


Table7 <- rbind(Table7a, Table7b, Table7c, Table7d)


Table7<- Table7[, c(1:7, 9, 11)]
Table7[,10] <- c("BOH", "MRE", "SAS", "LAW")
Table7<- Table7[, c(10,1:9)]
colnames(Table7)[1] <- "Section"


knitr::kable(Table7,format.args = list(big.mark = ","),
             caption='Table 1.7. Time (in minutes) from Start to Submit of Initial Survey Modules',
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c"),digits=2, booktabs = TRUE)%>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 


```








```{r Section8, echo=FALSE, warning = FALSE}



cannot_ver <- data_c %>%  filter(d_821247024==219863910 & d_512820379==486306141) %>%  
  mutate(sect_comp= case_when((d_949302066==231311385 | d_536735468==231311385 | d_976570371==231311385 | d_663265240==231311385) ~ "At Least One",
                              TRUE ~ "None"))

Numb5 <- cannot_ver %>% group_by(sect_comp) %>%    dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(sect_comp, n, percentage)

Numb5_table <- Numb5 %>% mutate(np = paste0(n, " (", round(percentage, digits=2), "%)")) %>% select(sect_comp, np)

Numb5_table[dim(Numb5_table)[[1]]+1 , ] <- list("Total", paste(sum(Numb5$n), " (100%)"))


knitr::kable(Numb5_table, 
             caption='Table 1.8. Inital Survey Submission Status among Active Recruits who Could Not be Verified', 
             col.names=c("Sections Submitted", "Active recruits"), 
             row.names=FALSE, align=c("l","c"),digits=1, booktabs = TRUE) %>%  
  add_indent(c(1:2)) %>% 
  kable_styling(latex_options = "scale_down")


```



```{r, echo=FALSE, warning=FALSE, message=FALSE, results='eval'}


CES_by_Sex_df <- create_tbl_cross2(all_data, "sex", "BL_comp", "row", "Sex", "Baseline Survey \n Completion", "Total Verified Participants")

knitr::kable(CES_by_Sex_df, 
             caption='Table 1.9. Initial Survey Completion Rate by Site Defined Sex \n Among Verified Participants',
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(CES_by_Sex_df) - 1)) %>%  landscape() %>% 
  footnote(general="Note: Sex defined as the de-identified sex data reported by sites at time of invitation.",
           general_title = "")





CES_by_Age_df <- create_tbl_cross2(all_data, "age", "BL_comp", "row", "Age", "Baseline Survey \n Completion", "Total Verified Participants")

knitr::kable(CES_by_Age_df, 
             caption="Table 1.10. Initial Survey Completion Rate by Site Defined Age \n Among Verified Participants",
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(CES_by_Age_df) - 1)) %>%  landscape() %>% 
  footnote(general="Note: Age defined as the de-identified age data reported by sites at time of invitation, not current age at time of survey completion.",
           general_title = "")





CES_by_Race_df <- create_tbl_cross2(all_data, "race", "BL_comp", "row", "Race", "Baseline Survey \n Completion", "Total Verified Participants")

knitr::kable(CES_by_Race_df, 
             caption="Table 1.11. Initial Survey Completion Rate by Site Defined Race \n Among Verified Participants",
             row.names=FALSE, align=c("l","c","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(CES_by_Race_df) - 1)) %>%  landscape() %>%
    footnote(general = "Note: Race defined as the de-identified race data reported by sites at time of invitation.",
             general_title = "")



```




\newpage
# SSN Survey
\FloatBarrier
```{r SSN, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


ssn_surv_table <- create_tbl_cross2(all_data, "ssn_started", "provided4", "row", "Submission Status", "Portion of SSN Given", "Total Verified Participants")

knitr::kable(ssn_surv_table, 
             caption='Table 2.1 Portion of SSN Given by Submission Status of SSN Survey Among Verified Participants',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(ssn_surv_table) - 1)) #%>%  landscape()

```

\newpage
\FloatBarrier
# Quality of Life Survey
```{r Table11s, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}



####### ALL 
QOL_comp_elg <- all_data %>% filter(qolcomplt!="Not Eligible") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(Site, qolcomplt) %>% dplyr::arrange(Site,qolcomplt) %>% 
  tbl_cross(
  row = Site,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",Site~"Site"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 

QOL_comp_elg[["table_body"]]$stat_0 <- sapply(strsplit(QOL_comp_elg[["table_body"]]$stat_0," "),"[",1)

QOL_comp_elg <- QOL_comp_elg %>%
  #bold_labels() %>%
  #italicize_levels() %>% 
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 3.1. Completion of 3-Month Quality of Life Survey Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

 
QOL_comp_elg %>% kable_styling(latex_options = c("scale_down","hold_position"))




##### verified on or after 12/1/23

QOL_comp_elg_after <- all_data %>% filter(qolcomplt!="Not Eligible" & as.Date(d_914594314) >= "2023-12-01") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(Site, qolcomplt) %>% dplyr::arrange(Site,qolcomplt) %>% 
  tbl_cross(
  row = Site,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",Site~"Site"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 

QOL_comp_elg_after[["table_body"]]$stat_0 <- sapply(strsplit(QOL_comp_elg_after[["table_body"]]$stat_0," "),"[",1)

 QOL_comp_elg_after <- QOL_comp_elg_after %>%
  #bold_labels() %>%
  #italicize_levels() %>% 
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 3.1.a. Completion of 3-Month Quality of Life Survey among Eligible participants Verified on or after December 1, 2023") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

QOL_comp_elg_after %>% kable_styling(latex_options = c("scale_down","hold_position")) 





###### verified before 12/1/23
QOL_comp_elg_before <- all_data %>% filter(qolcomplt!="Not Eligible" & as.Date(d_914594314) < "2023-12-01") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(Site, qolcomplt) %>% dplyr::arrange(Site,qolcomplt) %>% 
  tbl_cross(
  row = Site,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",Site~"Site"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 

QOL_comp_elg_before[["table_body"]]$stat_0 <- sapply(strsplit(QOL_comp_elg_before[["table_body"]]$stat_0," "),"[",1)

QOL_comp_elg_before <- QOL_comp_elg_before %>%
  #bold_labels() %>%
  #italicize_levels() %>% 
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 3.1.b. Completion of 3-Month Quality of Life Survey among Eligible Participants Verified prior to December 1, 2023") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)


QOL_comp_elg_before %>% kable_styling(latex_options = c("scale_down","hold_position")) %>% 
  footnote(general = 'The QOL "PROMIS" or "QOL" survey was released to all those verified prior to December 1, 2023 on August 30, 2024.',general_title = "Note: ", footnote_as_chunk = T)

```


\newpage
\FloatBarrier

```{r Table12s, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

###### ALL ########
QOL_comp_BL_all <- all_data %>%  filter(qolcomplt!="Not Eligible") 

QOL_comp_BL <- create_tbl_cross2(QOL_comp_BL_all, "completion", "qolcomplt", "row", "Completion", "QOL Completion", "Total QOL Eligible Participants")
colnames(QOL_comp_BL)[5] <- "Total QOL Eligible \n Participants"


knitr::kable(QOL_comp_BL, 
             caption='Table 3.2. Completion of 3-Month Quality of Life Survey by Baseline Data Completeness',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(QOL_comp_BL) - 1)) %>%  landscape()




###### On or After 12/1/23 ########

QOL_comp_after <- all_data %>% filter(as.Date(d_914594314) >= "2023-12-01" & qolcomplt!="Not Eligible")  

QOL_comp_BL_after <- create_tbl_cross2(QOL_comp_after, "completion", "qolcomplt", "row", "Completion", "QOL Completion", "Total QOL Eligible Participants")

colnames(QOL_comp_BL_after)[5] <- "Total QOL Eligible \n Participants"

knitr::kable(QOL_comp_BL_after, 
             caption='Table 3.2.a. Completion of 3-Month Quality of Life Survey by Baseline Data Completeness among Eligible Participants Verified on or after December 1, 2023',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(QOL_comp_BL_after) - 1)) %>%  landscape()



###### Before 12/1/23 ########

QOL_comp_after <- all_data %>% filter(as.Date(d_914594314) < "2023-12-01" & qolcomplt!="Not Eligible")  

QOL_comp_BL_before <- create_tbl_cross2(QOL_comp_after, "completion", "qolcomplt", "row", "Completion", "QOL Completion", "Total QOL Eligible Participants")

colnames(QOL_comp_BL_before)[5] <- "Total QOL Eligible \n Participants"
knitr::kable(QOL_comp_BL_before, 
             caption='Table 3.2.b. Completion of 3-Month Quality of Life Survey by Baseline Data Completeness among Eligible Participants Verified on before December 1, 2023',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(QOL_comp_BL_before) - 1)) %>%  landscape()


```





```{r Overall_BySex_ByAge, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


Comp_by_Sex <- all_data %>% filter(qolcomplt!="Not Eligible") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(sex, qolcomplt) %>% dplyr::arrange(sex,qolcomplt) %>% 
  tbl_cross(
  row = sex,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",sex~"Sex"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 


Comp_by_Sex_table <- Comp_by_Sex %>%
  #bold_labels() %>%
  #italicize_levels() %>% 
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 3.3. 3-Month Quality of Life Survey Completion Rate by Site Defined Sex \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>% kable_styling(latex_options = c("scale_down","hold_position"))  

add_footnote(Comp_by_Sex_table, "Note: Sex defined as the de-identified sex data reported by sites at time of invitation.", 
             notation = "none")





Comp_by_Age <- all_data %>% filter(qolcomplt!="Not Eligible") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(age, qolcomplt) %>% dplyr::arrange(age,qolcomplt) %>% 
  tbl_cross(
  row = age,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",age~"Age"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 

#Comp_by_Age[["table_body"]]$stat_0 <- sapply(strsplit(Comp_by_Age[["table_body"]]$stat_0," "),"[",1)

Comp_by_Age <- Comp_by_Age %>%
  #bold_labels() %>%
  #italicize_levels() %>% 
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 3.4. 3-Month Quality of Life Survey Completion Rate by Age \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)  %>% kable_styling(latex_options = c("scale_down","hold_position")) 

add_footnote(Comp_by_Age, "Note: Age defined as the de-identified age data reported by sites at time of invitation, not current age at time of survey completion.", 
             notation="none")


```



```{r merge1, include=FALSE, warning=FALSE}

dictionary <- rio::import("https://episphere.github.io/conceptGithubActions/aggregate.json",format = "json")
dd <- dplyr::bind_rows(dictionary,.id="CID")
dd <-rbindlist(dictionary,fill=TRUE,use.names=TRUE,idcol="CID")
dd$`Variable Label`[is.na(dd$`Variable Label`)] <- replace_na(dd$'Variable Name')

dd <- as.data.frame.matrix(do.call("rbind",dictionary)) 
dd$CID <- rownames(dd)
#https://shaivyakodan.medium.com/7-useful-r-packages-for-analysis-7f60d28dca98
#devtools::install_github("tidyverse/reprex")


recr_M1 <- bq_project_query(project, query="SELECT token,Connect_ID, d_821247024, d_914594314,  d_827220437,d_512820379,
                            d_949302066 , d_517311251  FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` WHERE  d_821247024='197316935'")
recr_m1 <- bq_table_download(recr_M1,bigint = "integer64",n_max = Inf, page_size = 10000)
cnames <- names(recr_m1)
# Check that it doesn't match any non-number
numbers_only <- function(x) !grepl("\\D", x)
# to check variables in recr_noinact_wl1
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(recr_m1,varname)
  recr_m1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}


#### Handling participants that somehow completed both Mod1 version 1 and Mod1 version 2
sql_M1_1 <- bq_project_query(project, query="SELECT Connect_ID, D_384191091_D_384191091_D_583826374, D_384191091_D_384191091_D_636411467, D_384191091_D_384191091_D_458435048, D_384191091_D_384191091_D_706998638, D_384191091_D_384191091_D_973565052, D_384191091_D_384191091_D_586825330, D_384191091_D_384191091_D_412790539, D_384191091_D_384191091_D_807835037,D_384191091_D_747350323,D_384191091_D_384191091_D_746038746 FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v1_JP` where Connect_ID is not null")
sql_M1_2 <- bq_project_query(project, query="SELECT Connect_ID, D_384191091_D_384191091_D_583826374 ,D_384191091_D_384191091_D_636411467, D_384191091_D_384191091_D_458435048, D_384191091_D_384191091_D_706998638, D_384191091_D_384191091_D_973565052, D_384191091_D_384191091_D_586825330,D_384191091_D_384191091_D_412790539,D_384191091_D_384191091_D_807835037,D_384191091_D_747350323,D_384191091_D_384191091_D_746038746 FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2_JP` where Connect_ID is not null")


M1_V1 <- bq_table_download(sql_M1_1, bigint = "integer64")
M1_V2 <- bq_table_download(sql_M1_2, bigint = "integer64")

# Select matching column names
M1_V1_vars <- colnames(M1_V1)
M1_V2_vars <- colnames(M1_V2)
common_vars <- intersect(M1_V1_vars, M1_V2_vars)

# Subset to common columns
M1_V1_common <- M1_V1[, common_vars]
M1_V2_common <- M1_V2[, common_vars]

# Add version indicator
M1_V1_common$version <- 1
M1_V2_common$version <- 2

# Identify columns with mismatched types
mismatched_cols <- names(M1_V1_common)[sapply(names(M1_V1_common), function(col) {
  class(M1_V1_common[[col]]) != class(M1_V2_common[[col]])
})]

# Convert mismatched columns to character for consistency
M1_V1_common <- M1_V1_common %>%
  mutate(across(all_of(mismatched_cols), as.character))
M1_V2_common <- M1_V2_common %>%
  mutate(across(all_of(mismatched_cols), as.character))

# Combine both versions for participants who completed both
M1_common <- bind_rows(M1_V1_common, M1_V2_common) %>%
  arrange(Connect_ID, desc(version))

# For columns unique to each version
V1_only_vars <- setdiff(M1_V1_vars, common_vars)
V2_only_vars <- setdiff(M1_V2_vars, common_vars)

# Subset each version for unique columns and add version indicator
m1_v1_only <- M1_V1[, c("Connect_ID", V1_only_vars)] %>%
  mutate(version = 1)
m1_v2_only <- M1_V2[, c("Connect_ID", V2_only_vars)] %>%
  mutate(version = 2)

# Combine the unique and common data
m1_common_v1 <- left_join(M1_common, m1_v1_only, by = c("Connect_ID", "version"))
m1_combined_v1v2 <- left_join(m1_common_v1, m1_v2_only, by = c("Connect_ID", "version"))

# Filter for complete cases where specific completion criteria are met
m1_complete <- m1_combined_v1v2 %>%
  filter(Connect_ID %in% recr_m1$Connect_ID[recr_m1$d_949302066 == 231311385]) %>%
  arrange(desc(version))

# Remove duplicates, keeping only the most recent version for each Connect_ID
m1_complete_nodup <- m1_complete[!duplicated(m1_complete$Connect_ID),]

m1_complete_nodup$Connect_ID <- as.numeric(m1_complete_nodup$Connect_ID)



all_data$Connect_ID <- as.numeric(all_data$Connect_ID)


promis_df= left_join(m1_complete_nodup, all_data, by="Connect_ID")
dim(promis_df)


promis <- as_tibble(promis_df)


knitr::opts_chunk$set(comment = NA)

```



```{r Race, warning=FALSE, echo=FALSE, message=FALSE}


## Multi-racial

multi_race=0    
for (i in 1:length(promis$Connect_ID)){
  AI=ifelse((promis$D_384191091_D_384191091_D_583826374[[i]]==1 & (promis$D_384191091_D_384191091_D_636411467[[i]]==1 | promis$D_384191091_D_384191091_D_458435048[[i]]==1|
                                               promis$D_384191091_D_384191091_D_706998638[[i]]==1 | promis$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                               promis$D_384191091_D_384191091_D_586825330[[i]]==1 | promis$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                               promis$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  As=ifelse((promis$D_384191091_D_384191091_D_636411467[[i]]==1 & (promis$D_384191091_D_384191091_D_583826374[[i]]==1 | promis$D_384191091_D_384191091_D_458435048[[i]]==1|
                                                        promis$D_384191091_D_384191091_D_706998638[[i]]==1 | promis$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_586825330[[i]]==1 | promis$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Bl=ifelse((promis$D_384191091_D_384191091_D_458435048[[i]]==1 & (promis$D_384191091_D_384191091_D_583826374[[i]]==1 | promis$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        promis$D_384191091_D_384191091_D_706998638[[i]]==1 | promis$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_586825330[[i]]==1 | promis$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Hs=ifelse((promis$D_384191091_D_384191091_D_706998638[[i]]==1 & (promis$D_384191091_D_384191091_D_583826374[[i]]==1 | promis$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        promis$D_384191091_D_384191091_D_458435048[[i]]==1 | promis$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_586825330[[i]]==1 | promis$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Me=ifelse((promis$D_384191091_D_384191091_D_973565052[[i]]==1 & (promis$D_384191091_D_384191091_D_583826374[[i]]==1 | promis$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        promis$D_384191091_D_384191091_D_458435048[[i]]==1 | promis$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_586825330[[i]]==1 | promis$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Hw=ifelse((promis$D_384191091_D_384191091_D_586825330[[i]]==1 & (promis$D_384191091_D_384191091_D_583826374[[i]]==1 | promis$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        promis$D_384191091_D_384191091_D_458435048[[i]]==1 | promis$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_973565052[[i]]==1 | promis$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Wh=ifelse((promis$D_384191091_D_384191091_D_412790539[[i]]==1 & (promis$D_384191091_D_384191091_D_583826374[[i]]==1 | promis$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        promis$D_384191091_D_384191091_D_458435048[[i]]==1 | promis$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_586825330[[i]]==1 | promis$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Ot=ifelse((promis$D_384191091_D_384191091_D_807835037[[i]]==1 & (promis$D_384191091_D_384191091_D_583826374[[i]]==1 | promis$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        promis$D_384191091_D_384191091_D_458435048[[i]]==1 | promis$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_586825330[[i]]==1 | promis$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        promis$D_384191091_D_384191091_D_412790539[[i]]==1)), 1, 0)
  multi_race= multi_race + sum(AI+As+Bl+Hs+Me+Hw+Wh+Ot, na.rm=T)

}

#cat("Percentage of multirace participants:", (multi_race/(dim(promis)[1]))*100)
   
   

promis$multi_racial <- c(rep(1, times=multi_race), rep(0, times=(dim(promis)[1]- multi_race)))



## RACE

promis = promis %>%  mutate(race= case_when(multi_racial==1 ~ "Multi-Racial",
                                                     D_384191091_D_384191091_D_583826374==1 ~ "American Indian or Native American",
                                                     D_384191091_D_384191091_D_636411467==1 ~ "Asian/Asian American",
                                                     D_384191091_D_384191091_D_458435048==1 ~ "Black, African American, or African",
                                                     D_384191091_D_384191091_D_706998638==1 ~ "Hispanic, Latino, or Spanish",
                                                     D_384191091_D_384191091_D_973565052==1 ~ "Middle Eastern or North African",
                                                     D_384191091_D_384191091_D_586825330==1 ~ "Hawaiian or Pacific Islander",
                                                     D_384191091_D_384191091_D_412790539==1 ~ "White",
                                                     (D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Other",
                                                     D_384191091_D_384191091_D_746038746==1 ~ "Prefer Not to Answer",
                                                     TRUE  ~ "Skipped this question"))

```




```{r By_Race, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


Comp_by_race <- promis %>% filter(qolcomplt!="Not Eligible") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(race, qolcomplt) %>% dplyr::arrange(race,qolcomplt) %>% 
  tbl_cross(
  row = race,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",race~"Race"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 


Comp_by_race <- Comp_by_race %>%
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 3.5. 3-Month Quality of Life Survey Completion Rate by Race \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>% kable_styling(latex_options = c("scale_down","hold_position"))

reduced <- all_data %>% filter(d_949302066 != 231311385 & qolcomplt!="Not Eligible") # Those who are eligible for PROMIS but didn't complete mod1 yet

add_footnote(Comp_by_race, paste0('Note: In order to determine race, Module 1 must first be completed. There are ', dim(reduced)[[1]] , ' QOL eligible participants that have either not started or not finished Module 1.'),
             notation="none")


```


```{r By_Race_And_Sex, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

promis = promis %>%  mutate(sex_race= case_when(sex=="Female" & multi_racial==1 ~ "Female: Multi-Racial",
                                            sex=="Female" & D_384191091_D_384191091_D_583826374==1 ~ "Female: American Indian or Native American",
                                            sex=="Female" & D_384191091_D_384191091_D_636411467==1 ~ "Female: Asian/Asian American",
                                            sex=="Female" & D_384191091_D_384191091_D_458435048==1 ~ "Female: Black, African American, or African",
                                            sex=="Female" & D_384191091_D_384191091_D_706998638==1 ~ "Female: Hispanic, Latino, or Spanish",
                                            sex=="Female" & D_384191091_D_384191091_D_973565052==1 ~ "Female: Middle Eastern or North African",
                                            sex=="Female" & D_384191091_D_384191091_D_586825330==1 ~ "Female: Hawaiian or Pacific Islander",
                                            sex=="Female" & D_384191091_D_384191091_D_412790539==1 ~ "Female: White",
                                            sex=="Female" & (D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Female: Other",
                                            sex=="Female" & D_384191091_D_384191091_D_746038746==1 ~ "Female: Prefer Not to Answer",
                                            
                                            sex=="Male" & multi_racial==1 ~ "Male: Multi-Racial",
                                            sex=="Male" & D_384191091_D_384191091_D_583826374==1 ~ "Male: American Indian or Native American",
                                            sex=="Male" & D_384191091_D_384191091_D_636411467==1 ~ "Male: Asian/Asian American",
                                            sex=="Male" & D_384191091_D_384191091_D_458435048==1 ~ "Male: Black, African American, or African",
                                            sex=="Male" & D_384191091_D_384191091_D_706998638==1 ~ "Male: Hispanic, Latino, or Spanish",
                                            sex=="Male" & D_384191091_D_384191091_D_973565052==1 ~ "Male: Middle Eastern or North African",
                                            sex=="Male" & D_384191091_D_384191091_D_586825330==1 ~ "Male: Hawaiian or Pacific Islander",
                                            sex=="Male" & D_384191091_D_384191091_D_412790539==1 ~ "Male: White",
                                            sex=="Male" & (D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Male: Other",
                                            sex=="Male" & D_384191091_D_384191091_D_746038746==1 ~ "Male: Prefer Not to Answer",
                                            
                                            sex=="Unknown" & multi_racial==1 ~ "Unknown: Multi-Racial",
                                            sex=="Unknown" & D_384191091_D_384191091_D_583826374==1 ~ "Unknown: American Indian or Native American",
                                            sex=="Unknown" & D_384191091_D_384191091_D_636411467==1 ~ "Unknown: Asian/Asian American",
                                            sex=="Unknown" & D_384191091_D_384191091_D_458435048==1 ~ "Unknown: Black, African American, or African",
                                            sex=="Unknown" & D_384191091_D_384191091_D_706998638==1 ~ "Unknown: Hispanic, Latino, or Spanish",
                                            sex=="Unknown" & D_384191091_D_384191091_D_973565052==1 ~ "Unknown: Middle Eastern or North African",
                                            sex=="Unknown" & D_384191091_D_384191091_D_586825330==1 ~ "Unknown: Hawaiian or Pacific Islander",
                                            sex=="Unknown" & D_384191091_D_384191091_D_412790539==1 ~ "Unknown: White",
                                            sex=="Unknown" & (D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Unknown: Other",
                                            sex=="Unknown" & D_384191091_D_384191091_D_746038746==1 ~ "Unknown: Prefer Not to Answer",
                                                     TRUE  ~ "Skipped this question"))

Comp_by_sex_race <- promis %>% filter(qolcomplt!="Not Eligible") %>% 
  mutate(qolcomplt = factor(qolcomplt, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(sex_race, qolcomplt) %>% dplyr::arrange(sex_race,qolcomplt) %>% 
  tbl_cross(
  row = sex_race,
  col = qolcomplt,
  label = list(qolcomplt ~ "Survey Completion",sex_race~"Sex and Race"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total QOL Eligible Participants") 


Comp_by_sex_race <- Comp_by_sex_race %>%
  modify_header(stat_0 = "Total QOL Eligible \n Participants") %>%
  modify_caption("Table 3.6. 3-Month Quality of Life Survey Completion Rate by Sex and Race \n Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

reduced <- all_data %>% filter(d_949302066 != 231311385 & qolcomplt!="Not Eligible") # Those who are eligible for PROMIS but didn't complete mod1 yet

Comp_by_sex_race %>% kable_styling(latex_options = c("scale_down","hold_position")) %>% 
  footnote(general = paste0('In order to determine race, Module 1 must first be completed. There are ', dim(reduced)[[1]] , ' QOL eligible participants that have either not started or not finished Module 1.'),general_title = "Note: ", footnote_as_chunk = T)


```


```{r By_Demographic, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

promis <- promis %>%
  mutate(
    "White Women" = if_else(race == "White" & sex == "Female", 1, 0),
    "Black Men" = if_else(race == "Black, African American, or African" & sex == "Male", 1, 0),
    "Women Under 45" = if_else((age == "35-39" | age == "40-45") & sex == "Female", 1, 0),
    "Women Over 45" = if_else((age == "46-50" | age == "51-55" | age == "56-60" | age == "61-65" | age == "66-70") & sex == "Female", 1, 0),
    "Men Under 45" = if_else((age == "35-39" | age == "40-45") & sex == "Male", 1, 0),
    "Men Over 45" = if_else((age == "46-50" | age == "51-55" | age == "56-60" | age == "61-65" | age == "66-70") & sex == "Male", 1, 0)
  )

# Can be in more then one category
all_data_long <- promis %>%
  pivot_longer(cols = c("White Women", "Black Men", "Women Under 45", "Women Over 45", "Men Under 45", "Men Over 45"),
               names_to = "Demographic_Group", values_to = "Flag") %>%
  filter(Flag == 1)  # Keep only rows where participants are in one or more of these demographics


Comp_by_Demographic <- all_data_long %>% 
  filter(qolcomplt != "Not Eligible") %>%
  mutate(qolcomplt = factor(qolcomplt, levels = c("Not Started", "Started", "Submitted")),
         Demographic_Group = factor(Demographic_Group, levels=c("White Women","Black Men","Women Under 45","Women Over 45","Men Under 45","Men Over 45"))) %>%
  select(Demographic_Group, qolcomplt) %>%
  tbl_cross(
    row = Demographic_Group,
    col = qolcomplt,
    label = list(qolcomplt ~ "Survey Completion", Demographic_Group ~ "Demographic"),
    percent = "row",
    digits = c(0, 2),
    margin_text = "Total"
  )


Comp_by_Demographic <- Comp_by_Demographic %>%
  modify_header(stat_0 = "Total") %>%
  modify_caption("Table 3.7. 3-Month Quality of Life Survey Completion Rate \n by Demographic Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

# Style the table output
Comp_by_Demographic %>% kable_styling(latex_options = c("scale_down", "hold_position"))  %>% 
  footnote(general = "Participants may be counted more then once in these categories.",general_title = "Note: ", footnote_as_chunk = T)


```

\FloatBarrier
```{r QOL_start_stop, echo=FALSE, warning=FALSE, message=FALSE}




QOL_time <- all_data %>% 
  filter(qolcomplt=="Submitted") %>%
  mutate(compTM_qol = as.numeric(difftime(as.POSIXct(ymd_hms(d_843688458)), as.POSIXct(ymd_hms(d_870643066)), units="mins")),
         permission = case_when(compTM_qol<5 ~ "Under 5 Minutes",
                                compTM_qol<10 ~ "5-10 Minutes",
                                compTM_qol<15 ~ "10-15 Minutes",
                                compTM_qol<20 ~ "15-20 Minutes",
                                compTM_qol<30 ~ "20-30 Minutes",
                                compTM_qol>=30 ~ "30+ Minutes"),
         permission = factor(permission, levels=c("Under 5 Minutes", "5-10 Minutes", "10-15 Minutes", 
                                                   "15-20 Minutes", "20-30 Minutes", "30+ Minutes")))  %>% 
    group_by(permission) %>% tally() %>% 
  mutate(Percentage = (n / sum(n)) * 100)



summary_row <- data.frame(permission = "Total Submitted QOL Survey",
                          n = sum(QOL_time$n),
                          Percentage = 100)


QOL_TM <- rbind(QOL_time, summary_row) %>%
  mutate(N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                            " (", round(Percentage, digits = 1), "%)"),
         Cumulative_Percentage = round(cumsum(Percentage), digits=2))
QOL_TM$Cumulative_Percentage[nrow(QOL_TM)] <- 100

QOL_TM <- QOL_TM %>% 
  select(permission, N_percent, Cumulative_Percentage) %>%
  rename(`Completion Time` = permission, `N%` = N_percent,
         'Cumulative Percentage' = Cumulative_Percentage)


knitr::kable(QOL_TM, #format.args = list(big.mark = ","),
             caption = 'Table 3.8. 3-Month Quality of Life Survey Completion Time from Start to Submit \n Among Eligible Participants That Submitted the Survey', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c", "c")) %>% 
  add_indent(c(1:(nrow(QOL_TM)-1))) %>%  
  kable_styling(latex_options = "scale_down") #c("scale_down","hold_position"))

```


```{r Table14, echo=FALSE, warning=FALSE, message=FALSE}




## Time from QOL trigger to submission of QOL survey
# category= 3mo QOL Survey Reminders attempt=1st contact notification_time will be used in place of FIRST_QOL_REMINDER

trig_qol <- bq_project_query(project,
query="SELECT distinct(token), notification_time FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.notifications_JP`
where category='3mo QOL Survey Reminders' and attempt='1st contact'")
trigger <- bigrquery::bq_table_download(trig_qol,bigint = "integer64")


trigger_time <- left_join(all_data, trigger, by="token")


## Those verified after 12/1/2024 were notified
trigger_time$trig <- ifelse(as.Date(trigger_time$d_914594314)> "2024-12-01", trigger_time$notification_time,
                            as.Date(as.Date(trigger_time$d_914594314) + 90))

trig_time<- trigger_time %>%  filter(qolcomplt=="Submitted") %>%
  mutate(trigTM_qol = as.numeric(difftime(as.POSIXct(ymd_hms(d_843688458)), as.POSIXct(ymd_hms(notification_time)), units="days")))

Trig_table = trig_time %>%
  dplyr::summarize('N'=n(),
                   Min = round(min(trigTM_qol, na.rm = TRUE), digits=2),
                   Q1 = round(quantile(trigTM_qol, 0.25, na.rm = TRUE), digits=2),
                   Median = round(median(trigTM_qol, na.rm = TRUE), digits=2),
                   Mean = round(mean(trigTM_qol, na.rm = TRUE),  digits=2),
                   SD= round(sd(trigTM_qol, na.rm = TRUE), digits=2),
                   Q3 = round(quantile(trigTM_qol, 0.75, na.rm = TRUE), digits=2),
                   'Perc.90' = round(quantile(trigTM_qol, 0.90, na.rm = TRUE), digits=2),
                   Max = round(max(trigTM_qol, na.rm = TRUE), digits=2))

knitr::kable(Trig_table, 
             caption = 'Table 3.9. 3-Month Quality of Life Survey Completion from Trigger to Submit for \n Verified Participants, in Days', 
             row.names=FALSE, format.args = list(big.mark = ","), linesep = "", 
             booktabs = T, align=c("l", "c", "c", "c", "c", "c", "c", "c", "c")) %>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 

```


```{r QOL_ver_time, echo=FALSE, warning=FALSE, message=FALSE}

qol_ver<- all_data %>%  filter(qolcomplt != "Not Eligible") %>% 
  mutate(ver_surv = case_when(as.Date(d_914594314) < "2023-01-01" ~ "More than 1 Year",
                              as.Date(d_914594314) < "2023-07-01" ~ "6 Months - 1 Year",
                              as.Date(d_914594314) < "2024-01-01" ~ "3 Months - 6 Months",
                              as.Date(d_914594314) >= "2023-01-01" ~ "At 3 Months"),
         ver_surv = factor(ver_surv, levels=c("More than 1 Year","6 Months - 1 Year","3 Months - 6 Months","At 3 Months")))


qol_ver_df <- create_tbl_cross2(qol_ver, "ver_surv", "qolcomplt", "row", "Time from Verification to QOL Survey Release", "Survey Completion", "Total QOL Eligible Participants")

colnames(qol_ver_df)[5] <- "Total QOL Eligible \n Participants"
knitr::kable(qol_ver_df, 
             caption='Table 3.10. QOL Survey Completion By Time from Verification to QOL Survey Release',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(qol_ver_df) - 1)) %>%  landscape()
  


```



```{r BL_After_PROMIS, echo=FALSE, warning=FALSE, message=FALSE}


BL_QOL <- all_data %>%  filter(qolcomplt=="Submitted") %>%
  mutate(after_qol = case_when(as.Date(d_843688458) <= as.Date(d_517311251) ~ "BOH",
                               as.Date(d_843688458) <= as.Date(d_832139544) ~ "MRE",
                               as.Date(d_843688458) <= as.Date(d_770257102) ~ "SAS",
                               as.Date(d_843688458) <= as.Date(d_264644252) ~ "LAW",
                               as.Date(d_843688458) <= as.Date(d_222161762) ~ "BUM",
                               as.Date(d_843688458) <= as.Date(d_764863765) ~ "BU",
                               as.Date(d_843688458) <= as.Date(d_195145666) ~ "MW",
                               as.Date(d_843688458) <= as.Date(d_784810139) ~ "COVID",
                               TRUE ~ "No Survey Submitted After QOL"),
         after_qol = factor(after_qol, levels=c("BOH","MRE","SAS", 
                                        "LAW", "BUM", "BU", 
                                        "MW", "COVID", "No Survey Submitted After QOL"))) %>% 
  group_by(after_qol) %>% tally() %>% 
  mutate(Percentage = (n / sum(n)) * 100)

summary_row <- data.frame(after_qol = "Total Submitted QOL Survey",
                          n = sum(QOL_time$n),
                          Percentage = 100)


BL_QOL_table <- rbind(BL_QOL, summary_row) %>%
  mutate(N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                            " (", round(Percentage, digits = 1), "%)"))

BL_QOL_table <- BL_QOL_table %>% 
  select(after_qol, N_percent) %>%
  rename(`Survey Completed After QOL` = after_qol, `N%` = N_percent)


knitr::kable(BL_QOL_table,
             caption = 'Table 3.11. Baseline Survey Completion On Day of or After QOL Survey Completion', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c")) %>% 
  add_indent(c(1:(nrow(BL_QOL_table)-1))) %>%  
  kable_styling(latex_options = "scale_down") #c("scale_down","hold_position"))



```




\newpage
\FloatBarrier
# Connect Experience Survey
```{r CES, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}



CES_comp <- all_data %>% filter(CES_status!="Not Eligible") %>% 
  mutate(CES_status = factor(CES_status, levels=c("Not Started", "Started", "Submitted"))) %>% 
  select(Site, CES_status) %>% dplyr::arrange(Site,CES_status) %>% 
  tbl_cross(
  row = Site,
  col = CES_status,
  label = list(CES_status ~ "Survey Completion",Site~"Site"),
  percent = "row",
  digits=c(0,2),
  margin_text="Total CES Eligible Participants") 

CES_comp[["table_body"]]$stat_0 <- sapply(strsplit(CES_comp[["table_body"]]$stat_0," "),"[",1)

CES_comp <- CES_comp %>%
  #bold_labels() %>%
  #italicize_levels() %>% 
  modify_header(stat_0 = "Total CES Eligible \n Participants") %>%
  modify_caption("Table 4.1. Completion of Connect Experience Survey Among Eligible Participants") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE)

 
CES_comp %>% kable_styling(latex_options = c("scale_down","hold_position"))

```



```{r CES_BL, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


CES_comp_BL <- all_data %>%  filter(CES_status!="Not Eligible") %>%  
  mutate(CES_status = factor(CES_status, levels=c("Not Started", "Started", "Submitted")),
         completion = factor(completion, levels=c("Completed both survey and sample(s)","Completed all baseline survey modules 1-4, no baseline samples", 
                                                  "Completed any baseline sample, did not complete baseline survey","Completed neither survey or sample(s)")))


CES_com_df <- create_tbl_cross2(CES_comp_BL, "completion", "CES_status", "row", "Completion", "Survey Completion", "Total CES Eligible Participants")

colnames(CES_com_df)[5] <- "Total CES Eligible \n Participants"

knitr::kable(CES_com_df, 
             caption='Table 4.2. Completion of Connect Experience Survey by Baseline Data Completeness',
             row.names=FALSE, align=c("l","c","c","c","c"), booktabs = TRUE) %>%
    kable_styling(latex_options = "scale_down") %>%  
    add_indent(seq(1, nrow(CES_com_df) - 1)) %>%  landscape()

```



\FloatBarrier
```{r CES_Start_Stop, echo=FALSE, warning=FALSE, message=FALSE}


CES_time <- all_data %>% filter(d_956490759 == 231311385) %>%
  mutate(comp_tm_CES = as.numeric(difftime(as.POSIXct(ymd_hms(d_199471989)), as.POSIXct(ymd_hms(d_263355177)), units="mins")),
         start_stop_time = case_when(comp_tm_CES<5 ~ "Under 5 Minutes",
                                comp_tm_CES<10 ~ "5-10 Minutes",
                                comp_tm_CES<15 ~ "10-15 Minutes",
                                comp_tm_CES<20 ~ "15-20 Minutes",
                                comp_tm_CES<30 ~ "20-30 Minutes",
                                comp_tm_CES>=30 ~ "30+ Minutes",
                                is.na(d_199471989) | is.na(d_263355177) ~ "Missing Stop or Start Timestamp"),
         start_stop_time = factor(start_stop_time, levels=c("Under 5 Minutes", "5-10 Minutes", "10-15 Minutes", 
                                                   "15-20 Minutes", "20-30 Minutes", "30+ Minutes", "Missing Stop or Start Timestamp")))  %>% 
    group_by(start_stop_time) %>% tally()

CES_time$Percentage <- (CES_time$n / sum(CES_time$n)) * 100
#CES_time <- CES_time[c(1:6),]

summary_row <- data.frame(start_stop_time = "Total CES Eligible Participants",
                          n = sum(CES_time$n),
                          Percentage = 100)


CES_TM <- rbind(CES_time, summary_row)

CES_TM[1, 4] <- paste0(formatC(CES_TM[1, 2], big.mark = ",", format = "d"), " (", round(CES_TM[1, 3], digits = 1), "%)")
CES_TM[2, 4] <- paste0(formatC(CES_TM[2, 2], big.mark = ",", format = "d"), " (", round(CES_TM[2, 3], digits = 1), "%)")
CES_TM[3, 4] <- paste0(formatC(CES_TM[3, 2], big.mark = ",", format = "d"), " (", round(CES_TM[3, 3], digits = 1), "%)")
CES_TM[4, 4] <- paste0(formatC(CES_TM[4, 2], big.mark = ",", format = "d"), " (", round(CES_TM[4, 3], digits = 1), "%)")
CES_TM[5, 4] <- paste0(formatC(CES_TM[5, 2], big.mark = ",", format = "d"), " (", round(CES_TM[5, 3], digits = 1), "%)")
CES_TM[6, 4] <- paste0(formatC(CES_TM[6, 2], big.mark = ",", format = "d"), " (", round(CES_TM[6, 3], digits = 1), "%)")
CES_TM[7, 4] <- paste0(formatC(CES_TM[7, 2], big.mark = ",", format = "d"), " (", round(CES_TM[7, 3], digits = 1), "%)")


CES_TM_table <- CES_TM[, c(1,4)]

colnames(CES_TM_table) <- c("Completion Time", "N%")

knitr::kable(CES_TM_table, 
             caption = 'Table 4.3. Connect Experience Survey Completion Time from Start to Submit \n Among Eligible Participants', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c")) %>% 
  add_indent(c(1:(nrow(CES_TM_table)-1))) %>%  
  kable_styling(latex_options = "scale_down") #c("scale_down","hold_position"))

```


```{r CES_trig_stop, echo=FALSE, warning=FALSE, message=FALSE}


ces_notif_time<- all_data %>%  
  filter(d_956490759 == 231311385) %>%
  mutate(notification_time = "2024-09-30",
         time = as.numeric(difftime(as.Date(d_199471989), as.Date(notification_time), units="days")))

ces_notif_table = ces_notif_time %>%
  dplyr::summarize('N'=n(),
                   Min = round(min(time, na.rm = TRUE), digits=2),
                   Q1 = round(quantile(time, 0.25, na.rm = TRUE), digits=2),
                   Median = round(median(time, na.rm = TRUE), digits=2),
                   Mean = round(mean(time, na.rm = TRUE),  digits=2),
                   SD= round(sd(time, na.rm = TRUE), digits=2),
                   Q3 = round(quantile(time, 0.75, na.rm = TRUE), digits=2),
                   'Perc.90' = round(quantile(time, 0.90, na.rm = TRUE), digits=2),
                   Max = round(max(time, na.rm = TRUE), digits=2))



knitr::kable(ces_notif_table, 
             caption = 'Table 4.4. Connect Experience Survey Completion from Trigger to Submit for \n Verified Participants, in Days', 
             row.names=FALSE, format.args = list(big.mark = ","), linesep = "", 
             booktabs = T, align=c("l", "c", "c", "c", "c", "c", "c", "c", "c")) %>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 

```



\newpage
\FloatBarrier
```{r BL_After_CES, echo=FALSE, warning=FALSE, message=FALSE}


BL_CES <- all_data %>%  filter(CES_status=="Submitted") %>%
  mutate(after_CES = case_when(as.Date(d_199471989) <= as.Date(d_517311251) ~ "BOH",
                               as.Date(d_199471989) <= as.Date(d_832139544) ~ "MRE",
                               as.Date(d_199471989) <= as.Date(d_770257102) ~ "SAS",
                               as.Date(d_199471989) <= as.Date(d_264644252) ~ "LAW",
                               as.Date(d_199471989) <= as.Date(d_222161762) ~ "BUM",
                               as.Date(d_199471989) <= as.Date(d_764863765) ~ "BU",
                               as.Date(d_199471989) <= as.Date(d_195145666) ~ "MW",
                               as.Date(d_199471989) <= as.Date(d_784810139) ~ "COVID",
                               TRUE ~ "No Survey Submitted After CES"),
         after_CES = factor(after_CES, levels=c("BOH","MRE","SAS", 
                                        "LAW", "BUM", "BU", 
                                        "MW", "COVID", "No Survey Submitted After CES"))) %>% 
  group_by(after_CES) %>% tally() %>% 
  mutate(Percentage = (n / sum(n)) * 100)

summary_row <- data.frame(after_CES = "Total Submitted CES Survey",
                          n = sum(BL_CES$n),
                          Percentage = 100)


BL_CES_table <- rbind(BL_CES, summary_row) %>%
  mutate(N_percent = paste0(formatC(n, big.mark = ",", format = "d"), 
                            " (", round(Percentage, digits = 1), "%)"))

BL_CES_table <- BL_CES_table %>% 
  select(after_CES, N_percent) %>%
  rename(`Survey Completed After QOL` = after_CES, `N%` = N_percent)


knitr::kable(BL_CES_table,
             caption = 'Table 4.5. Baseline Survey Completion On Day of or After CES Survey Completion', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c")) %>% 
  add_indent(c(1:(nrow(BL_CES_table)-1))) %>%  
  kable_styling(latex_options = "scale_down") #c("scale_down","hold_position"))



```



\newpage                   
\FloatBarrier
# Survey Metrics by Language Completed
Note: Spanish was made available in MyConnect beginning August 1, 2024.
```{r Pref_Lang_Time_All, echo=FALSE, warning=FALSE, message=FALSE}


pref_lang_site <- all_data %>% 
  tbl_cross(
    col = Pref_lang,
    row = Site,
    digits=c(0,1),
    percent = "column",
    label=list(Pref_lang="Preferred Language",
                Site = "Site"),
    missing="ifany",
    margin_text="Total") %>% 
  modify_header(stat_0 = "Total") %>%
  modify_caption("Table 5.1. Preferred Language by Site") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>%  
  kable_styling(latex_options = "scale_down") 

add_footnote(pref_lang_site, "Note: Preferred language is based on language of signed consent form and current user profile language status",
             notation="none")

```






```{r Survey_Flag_Setup, echo=FALSE, warning = FALSE, include=FALSE}


## SSN survey is not viewable in BQ so we will not have the language flag for that survey



queries <- list(
  m1_lang_c = "SELECT pts.Connect_ID, m1.d_784119588, d_255077064
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2_JP` m1
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on m1.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_949302066='231311385'",
  m2_lang_c = "SELECT pts.Connect_ID, m2.d_784119588, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module2_v2_JP` m2
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on m2.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_536735468='231311385'",
  m3_lang_c = "SELECT pts.Connect_ID, m3.d_784119588, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module3_v1_JP` m3
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on m3.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_976570371='231311385'",
  m4_lang_c = "SELECT pts.Connect_ID, m4.d_784119588, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module4_v1_JP` m4
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on m4.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and pts.d_663265240='231311385'",
  BUM_lang_c = "SELECT pts.Connect_ID, bum.d_784119588, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.bioSurvey_v1_JP` bum
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on bum.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_265193023='231311385'",
  BU_lang_c = "SELECT pts.Connect_ID, bu.d_784119588, d_255077064
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.clinicalBioSurvey_v1_JP` bu 
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on bu.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_253883960='231311385'",
  CV_lang_c = "SELECT pts.Connect_ID, cv.d_784119588, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.covid19Survey_v1_JP` cv
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on cv.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_220186468='231311385'",
  Mens_lang_c = "SELECT pts.Connect_ID, mns.d_784119588, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.menstrualSurvey_v1_JP` mns
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on mns.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_459098666='231311385'",
  MW_lang_c = "SELECT pts.Connect_ID, mw.d_784119588, d_255077064 
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.mouthwash_v1_JP` mw
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on mw.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_547363263='231311385'",
  QOL_lang_c = "SELECT pts.Connect_ID, qol.d_784119588, d_255077064
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.promis_v1_JP` qol
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on qol.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_320303124='231311385'",
  CES_lang_c = "SELECT pts.Connect_ID, ces.d_784119588, d_255077064
                FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.experience2024_JP` ces
                left join `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` pts
                on ces.Connect_ID=pts.Connect_ID
                WHERE pts.Connect_ID IS NOT NULL and d_956490759='231311385'"
)


results_list <- list()


for (name in names(queries)) {
  query <- queries[[name]]
  query_result <- bq_project_query(project, query)
  data <- bq_table_download(query_result, bigint = "integer64")
  results_list[[name]] <- data
}


m1_lang <- results_list$m1_lang_c
m2_lang <- results_list$m2_lang_c
m3_lang <- results_list$m3_lang_c
m4_lang <- results_list$m4_lang_c
BUM_lang <- results_list$BUM_lang_c
BU_lang <- results_list$BU_lang_c
CV_lang <- results_list$CV_lang_c
Mens_lang <- results_list$Mens_lang_c
MW_lang <- results_list$MW_lang_c
QOL_lang <- results_list$QOL_lang_c
CES_lang <- results_list$CES_lang_c




```


\FloatBarrier
```{r Svy_Lang_Diff, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


# Define the list of survey data frames
survey_dfs <- list(m1_lang, m2_lang, m3_lang, m4_lang, BUM_lang, BU_lang, CV_lang, Mens_lang, MW_lang, QOL_lang, CES_lang)

# Initialize an empty data frame to store results for all participants
all_scenarios <- data.frame(Connect_ID = character(), Flag = character(), Pref_lang = character(), stringsAsFactors = FALSE)

# Loop through each survey data frame
for (current_df in survey_dfs) {
  current_df <- current_df %>%
    mutate(
      Flag = ifelse(is.na(d_784119588), NA, ifelse(d_784119588 == 773342525, "Spanish", "English")),
      Pref_lang = case_when(d_255077064 == 773342525 ~ "Spanish", TRUE ~ "English")
    )
  
  # Extract relevant columns and add to the scenario tracking data frame
  participant_scenarios <- current_df %>%
    select(Connect_ID, Flag, Pref_lang)
  
  all_scenarios <- bind_rows(all_scenarios, participant_scenarios)
}

# Summarize the scenario for each participant
final_scenarios <- all_scenarios %>%
  group_by(Connect_ID) %>%
  summarize(
    Flag_set = unique(na.omit(Flag)), # Remove NAs from Flags
    Pref_lang_set = unique(Pref_lang),
    scenario = case_when(
      length(Flag_set) == 0 ~ "No survey language preference has been made", # No Flag values
      all(Flag_set == Pref_lang_set) ~ "Survey Flags and Preferred Language Consistent", # All Flags match Pref_lang
      any(Flag_set != Pref_lang_set) ~ "Any Survey Flag Inconsistent with Preferred Language" # Any inconsistency
    )
  ) %>%
  ungroup()

# Summarize the counts for each scenario
scenario_counts <- final_scenarios %>%
  count(scenario) %>%
  dplyr::rename(Scenario = scenario, 'Total Participants' = n)

consist <- knitr::kable(scenario_counts,
                        caption = "Table 5.2. Consistency of Language Choice in Survey Completion",
                        row.names = FALSE, align = c("l", "c"), digits = 2, booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down") # c("scale_down","hold_position")) 

add_footnote(consist, "Note: Those who do not start any surveys will not have survey flags, and thus not be counted in this table. Those that start but do not complete a survey will still choose a survey language.", notation = "none")



```

\newpage                        
\FloatBarrier
```{r Svy_Lang_Compare, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


survey_acronyms <- c("BOH", "MRE", "SAS", "LAW", "BUM", "BU", "COVID", "MENS", "MW", "QOL", "CES")


create_table <- function(current_df, current_acronym) {
  if (nrow(current_df) == 0) {
    return(data.frame(Survey = current_acronym, English = 0, Spanish = 0, Total = 0))
  }
  
  all_svry_flags <- current_df %>%
    mutate(Survey = case_when(!is.na(Connect_ID) ~ current_acronym,
                              TRUE ~ "NA"),
           Flag = case_when(d_784119588 == 773342525 ~ "Spanish",
                            TRUE ~ "English")) %>%
    tbl_cross(
      col =Flag,
      row = Survey,
      digits = c(0, 1),
      percent = "row",
      label = list(Flag = "Survey Flag",
                   Site = "Survey"),
      missing = "ifany",
      margin_text = "Total") %>%
    modify_header(stat_0 = "Total")
  
  df_all_svry_flags <- as.data.frame(all_svry_flags)
  colnames(df_all_svry_flags)[1] <- "Survey"
  df_all_svry_flags <- df_all_svry_flags[2,]
  
  # Ensure the data frame has consistent columns by adding missing ones with zeros
  expected_columns <- c("Survey", "English", "Spanish", "Total")
  missing_columns <- setdiff(expected_columns, names(df_all_svry_flags))
  
  if (length(missing_columns) > 0) {
    for (col in missing_columns) {
      df_all_svry_flags[[col]] <- 0
    }
  }
  
  df_all_svry_flags <- df_all_svry_flags[expected_columns]
  
  return(df_all_svry_flags)
}

# Initialize empty lists to store the results for each condition
all_flags_list_overall <- list()
all_flags_list_condition1 <- list()
all_flags_list_condition2 <- list()

# Loop through each survey data frame and acronym
for (i in seq_along(survey_dfs)) {
  # Get the current data frame and acronym
  current_df <- survey_dfs[[i]]
  current_acronym <- survey_acronyms[i]
  
  # Overall table
  df_overall <- create_table(current_df, current_acronym)
  all_flags_list_overall[[current_acronym]] <- df_overall
  
  # Spanish
  current_df_cond1 <- current_df %>% filter(d_255077064 == 773342525)
  df_condition1 <- create_table(current_df_cond1, current_acronym)
  all_flags_list_condition1[[current_acronym]] <- df_condition1
  
  # English
  current_df_cond2 <- current_df %>% filter(d_255077064 == 163149180 | is.na(d_255077064))
  df_condition2 <- create_table(current_df_cond2, current_acronym)
  all_flags_list_condition2[[current_acronym]] <- df_condition2
}


final_df_overall <- do.call(rbind, all_flags_list_overall)
final_df_condition1 <- do.call(rbind, all_flags_list_condition1)
final_df_condition2 <- do.call(rbind, all_flags_list_condition2)



knitr::kable(final_df_overall,
               caption = paste0("Table 5.3. Survey Completion by Survey Language \n Among All Participants"),
               row.names = FALSE, align = c("l","c","c","c"), digits = 2, booktabs = TRUE) %>% 
  add_indent(1:11) %>%  
  kable_styling(latex_options = "scale_down")

knitr::kable(final_df_condition1,
               caption = paste0("Table 5.3.a. Survey Completion by Survey Language \n Among Participants with Preferred language of Spanish"),
               row.names = FALSE, align = c("l","c","c","c"), digits = 2, booktabs = TRUE) %>% 
  add_indent(1:11) %>%  
  kable_styling(latex_options = "scale_down")

knitr::kable(final_df_condition2,
               caption = paste0("Table 5.3.b. Survey Completion by Survey Language \n Among Participants with Preferred language of English"),
               row.names = FALSE, align = c("l","c","c","c"), digits = 2, booktabs = TRUE) %>% 
  add_indent(1:11) %>%  
  kable_styling(latex_options = "scale_down")


```


\newpage

\FloatBarrier
```{r BL_start_stop_Lang, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

summarize_data <- function(data, filter_column, filter_value, language_value, target_column) {
    data %>% 
        filter(!!sym(filter_column) == filter_value & Pref_lang == language_value) %>% 
        summarize('N' = n(),
                  Min = min(!!sym(target_column), na.rm = TRUE),
                  Q1 = quantile(!!sym(target_column), 0.25, na.rm = TRUE),
                  Median = median(!!sym(target_column), na.rm = TRUE),
                  Mean = mean(!!sym(target_column), na.rm = TRUE), 
                  SD = sd(!!sym(target_column), na.rm = TRUE),
                  Q3 = quantile(!!sym(target_column), 0.75, na.rm = TRUE),
                  'Perc.90' = quantile(!!sym(target_column), 0.90, na.rm = TRUE),
                  Max = max(!!sym(target_column), na.rm = TRUE))
}

BOH_LangE <- summarize_data(all_data, "d_949302066", 231311385, "English", "m1_comp_mins")
MRE_LangE <- summarize_data(all_data, "d_536735468", 231311385, "English", "m2_comp_mins")
SAS_LangE <- summarize_data(all_data, "d_976570371", 231311385, "English", "m3_comp_mins")
LAW_LangE <- summarize_data(all_data, "d_663265240", 231311385, "English", "m4_comp_mins")

BOH_LangSP <- summarize_data(all_data, "d_949302066", 231311385, "Spanish", "m1_comp_mins")
MRE_LangSP <- summarize_data(all_data, "d_536735468", 231311385, "Spanish", "m2_comp_mins")
SAS_LangSP <- summarize_data(all_data, "d_976570371", 231311385, "Spanish", "m3_comp_mins")
LAW_LangSP <- summarize_data(all_data, "d_663265240", 231311385, "Spanish", "m4_comp_mins")



BL_lang_E <- rbind(BOH_LangE, MRE_LangE, SAS_LangE, LAW_LangE)
BL_lang_SP <- rbind(BOH_LangSP, MRE_LangSP, SAS_LangSP, LAW_LangSP)


BL_lang_E[,10] <- c("BOH", "MRE", "SAS", "LAW")
BL_lang_SP[,10] <- c("BOH", "MRE", "SAS", "LAW")

BL_lang_E<- BL_lang_E[, c(10,1:9)]
BL_lang_SP<- BL_lang_SP[, c(10,1:9)]


colnames(BL_lang_E)[1] <- "Section"
colnames(BL_lang_SP)[1] <- "Section"

knitr::kable(BL_lang_E, format.args = list(big.mark = ","), digits=2, 
             caption='Table 5.4.a Time (in minutes) from Start to Submit of Initial Survey Modules for English',
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c","c"), booktabs = TRUE)%>% 
    kable_styling(latex_options = c("scale_down","hold_position")) 

knitr::kable(BL_lang_SP, format.args = list(big.mark = ","), digits=2, 
             caption='Table 5.5.b Time (in minutes) from Start to Submit of Initial Survey Modules for Spanish',
             row.names=FALSE, align=c("l","c","c","c","c","c","c","c","c"),booktabs = TRUE)%>% 
    kable_styling(latex_options = c("scale_down","hold_position")) 

```

