---
title: "Home Address 1 Missingness Across Sites"
author: "Kelsey Dowling"
date: "`r Sys.Date()`"
output: pdf_document
---


In Module 4, the entire cohort is asked to provide their Home 1 Addresses , meaning their current home address. This is asked in a manner of open text boxes for each of the following home address components:
Street Number, Street Name, City, State, ZIP, Country. While we hope the entirety of the question is answered, a participant does have the ability to skip one or all text boxes and still move on from this question. This report reviews the skipping of Home Address 1 questions across all Connect Sites using the Module 4 skip logic from Qx: https://nih.app.box.com/file/1255293127627 ; only participants that have skipped one or all address 1 components are included in this report. Among those that did skip providing their full current address, the skipping trends are very much aligned across sites, though UChicago does have slightly higher rates overall. Roughly 19-27% chose not to provide their street name, less than 2% of participants from any site skipped their entire address, and the remainder of the address components were skipped at a much lower rate varying between 0-7%.



To avoid confusion, these tables will NOT have sums of missing responses at the bottom. Participants are able to skip one or all components of a question in Module 4.


```{r libraries, include=FALSE}

##  MUST RUN FIRST BEFORE KNITTING


library(bigrquery)
#install_tinytex()
library(tinytex)

library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(reshape)  ###to work on transition from long to wide or wide to long data
library(listr) ###to work on a list of vector, files or..
library(sqldf) ##sql
library(lubridate) ###date time
library(stringr) ###to work on patterns, charaters
library(arsenal)
library(gt)
library(gtsummary)

options(tinytex.verbose = TRUE)

bq_auth()
```


```{r QueryStatus, include=FALSE}

##Make sure SQL queries are properly running


# check_sch_query_status <- 
#   function(project, table_name){
# 
#     ## Set default project for BQ CLI
#     #set_proj_cmd <- paste0("bq ls -j --project_id ", project, " > /dev/null")
#     #system(set_proj_cmd)
#     
#     # Get list of scheduled queries from bq
#     bq_request <- 'bq ls --transfer_config --transfer_location="us" --filter="dataSourceIds:scheduled_query"'
#     response   <- system(bq_request, intern=TRUE)
#     # Remove second line "----" of table and remove white space from each row
#     response   <- lapply(response[-2], function(x) scan(text = x, what = ""))
#     header     <- simplify2array(response[1]) # Array of column names
#     
#     # Bind rows of data into one array
#     for (i in length(header)){
#       x <- c() # Initialize array with first non-header line of data
#       # Loop through remaining data
#       for (line in response[2:length(response)]){
#         x <- rbind(x, line)
#       }
#     }
#     
#     # Format as dataframe
#     df <- data.frame(x, row.names = NULL)
#     colnames(df) <- header
#     
#     # Return sch. query status as "SUCCEEDED", "PENDING", "RUNNING" or "FAILED".
#     df$state[df$displayName==table_name] 
#   }
# 
# 
# table_name <- "FlatConnect.participants_JP"
# project    <- "nih-nci-dceg-connect-prod-6d04"
# 
# # Check status of scheduled query
# query_status <- check_sch_query_status(project, table_name)
# switch(query_status,
#  "FAILED"    = stop(paste0("The sch. query for ", table_name, " failed. Reach out to Jake.")),
#   "PENDING"   = stop(paste0("The query for ", table_name, " is scheduled and waiting to be run.")),
#   "RUNNING"   = stop(paste0("The sch. query for ", table_name, " is still running. Wait until complete.")),
#   "SUCCEEDED" = print(paste0("The most recent scheduled query for ", table_name, " succeeded. The table is up-to-date."))
# )
# 
# 
# table_name <- "FlatConnect.module1_v1_JP"
# project    <- "nih-nci-dceg-connect-prod-6d04"
# 
# # Check status of scheduled query
# query_status <- check_sch_query_status(project, table_name)
# switch(query_status,
#  "FAILED"    = stop(paste0("The sch. query for ", table_name, " failed. Reach out to Jake.")),
#   "PENDING"   = stop(paste0("The query for ", table_name, " is scheduled and waiting to be run.")),
#   "RUNNING"   = stop(paste0("The sch. query for ", table_name, " is still running. Wait until complete.")),
#   "SUCCEEDED" = print(paste0("The most recent scheduled query for ", table_name, " succeeded. The table is up-to-date."))
# )
# 
# 
# table_name <- "FlatConnect.module1_v2_JP"
# project    <- "nih-nci-dceg-connect-prod-6d04"
# 
# # Check status of scheduled query
# query_status <- check_sch_query_status(project, table_name)
# switch(query_status,
#  "FAILED"    = stop(paste0("The sch. query for ", table_name, " failed. Reach out to Jake.")),
#   "PENDING"   = stop(paste0("The query for ", table_name, " is scheduled and waiting to be run.")),
#   "RUNNING"   = stop(paste0("The sch. query for ", table_name, " is still running. Wait until complete.")),
#   "SUCCEEDED" = print(paste0("The most recent scheduled query for ", table_name, " succeeded. The table is up-to-date."))
# )
# 
# 
# table_name <- "FlatConnect.module4_v1_JP"
# project    <- "nih-nci-dceg-connect-prod-6d04"
# 
# # Check status of scheduled query
# query_status <- check_sch_query_status(project, table_name)
# switch(query_status,
#  "FAILED"    = stop(paste0("The sch. query for ", table_name, " failed. Reach out to Jake.")),
#   "PENDING"   = stop(paste0("The query for ", table_name, " is scheduled and waiting to be run.")),
#   "RUNNING"   = stop(paste0("The sch. query for ", table_name, " is still running. Wait until complete.")),
#   "SUCCEEDED" = print(paste0("The most recent scheduled query for ", table_name, " succeeded. The table is up-to-date."))
# )


```


```{r M1Merge, include=FALSE}
project = "nih-nci-dceg-connect-prod-6d04"

dictionary <- rio::import("https://episphere.github.io/conceptGithubActions/aggregate.json",format = "json")
dd <- dplyr::bind_rows(dictionary,.id="CID")
dd <-rbindlist(dictionary,fill=TRUE,use.names=TRUE,idcol="CID")
dd$`Variable Label`[is.na(dd$`Variable Label`)] <- replace_na(dd$'Variable Name')

dd <- as.data.frame.matrix(do.call("rbind",dictionary)) 
dd$CID <- rownames(dd)
#https://shaivyakodan.medium.com/7-useful-r-packages-for-analysis-7f60d28dca98
devtools::install_github("tidyverse/reprex")

project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" ##project and billing should be consistent
##517311251 Date/time Status of Completion of Background and Overall Health                         SrvBOH_TmComplete_v1r0
##949302066 Flag for Baseline Module Background and Overall Health                        SrvBOH_BaseStatus_v1r0
recr_M1 <- bq_project_query(project, query="SELECT token,Connect_ID, d_821247024, d_914594314,  d_827220437,d_512820379,
                            d_949302066 , d_517311251  FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` WHERE  d_821247024='197316935'")
recr_m1 <- bq_table_download(recr_M1,bigint = "integer64")
cnames <- names(recr_m1)
# Check that it doesn't match any non-number
numbers_only <- function(x) !grepl("\\D", x)
# to check variables in recr_noinact_wl1
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(recr_m1,varname)
  recr_m1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}

sql_M1_1 <- bq_project_query(project, query="SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v1_JP` where Connect_ID is not null")
sql_M1_2 <- bq_project_query(project, query="SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2_JP` where Connect_ID is not null")


M1_V1 <- bq_table_download(sql_M1_1,bigint = "integer64") #1436 #1436 vars: 1507 01112023 
M1_V2 <- bq_table_download(sql_M1_2,bigint = "integer64") #2333 #3033 01112023 var:1531 #6339 obs 1893 vars 05022023

mod1_v1 <- M1_V1
cnames <- names(M1_V1)
###to check variables and convert to numeric
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(mod1_v1,varname)
  mod1_v1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}
mod1_v2 <- M1_V2
cnames <- names(M1_V2)
###to check variables and convert to numeric
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(mod1_v2,varname)
  mod1_v2[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}

M1_V1.var <- colnames(M1_V1)
M1_V2.var <- colnames(M1_V2)
var.matched <- M1_V1.var[which(M1_V1.var %in% M1_V2.var)]
length(var.matched)  #1275 #1278 vars 01112023 #1348 vars 05022023

V1_only_vars <- colnames(M1_V1)[colnames(M1_V1) %nin% var.matched] #232 #229 01112023 #159 05022023
V2_only_vars <- colnames(M1_V2)[colnames(M1_V2) %nin% var.matched] #253 #253 01112023 #545 05022023

length(M1_V1$Connect_ID[M1_V1$Connect_ID %in% M1_V2$Connect_ID])
#[1] 59 with the completion of two versions of Module1 
#[1] 62 with completing both versions of M1 ###double checked 03/28/2023
#68 double checked 05/02/2023

common.IDs <- M1_V1$Connect_ID[M1_V1$Connect_ID %in% M1_V2$Connect_ID]
M1_V1_common <- mod1_v1[,var.matched]

M1_V2_common <- mod1_v2[,var.matched]
M1_V1_common$version <- 1
M1_V2_common$version <- 2

##to check the completion of M1 among these duplicates
partM1_dups <- recr_m1[which(recr_m1$Connect_ID %in% common.IDs),]
table(partM1_dups$d_949302066)

M1_common  <- rbind(M1_V1_common, M1_V2_common) #including 136 duplicates (version 1 and version 2) from 68 participants 05022023
#M1_response <- matrix(data=NA, nrow=118, ncol=967)

m1_v1_only <- mod1_v1[,c("Connect_ID", V1_only_vars)] #230 vars 03282023 #160 vars 05/02/2023
m1_v2_only <- mod1_v2[,c("Connect_ID", V2_only_vars)] #255 vars 03282023 #546 vars 05/02/2023
m1_v1_only$version <- 1
m1_v2_only$version <- 2
#for (i in 1:length)
##to check the completion in each version
length(recr_m1$Connect_ID[which(recr_m1$Connect_ID %in% m1_v1_only$Connect_ID & recr_m1$d_949302066 ==231311385)]) #1364 03282023 # 1370 05022023
length(recr_m1$Connect_ID[which(recr_m1$Connect_ID %in% m1_v2_only$Connect_ID & recr_m1$d_949302066 ==231311385)]) #4870 03282023 # 5731 05022023

#library(janitor)

m1_common <- rbind(M1_V1_common,M1_V2_common)
m1_common_v1 <- base::merge(m1_common, m1_v1_only, by=c("Connect_ID","version"),all.x=TRUE)
m1_combined_v1v2 <- base::merge(m1_common_v1,m1_v2_only,by=c("Connect_ID","version"),all.x=TRUE)
m1_complete <- m1_combined_v1v2[which(m1_combined_v1v2$Connect_ID %in% recr_m1$Connect_ID[which(recr_m1$d_949302066 ==231311385 )]),] #7289 including duplicates 05022023

m1_complete <- m1_complete %>% arrange(desc(version)) 


m1_complete_nodup <- m1_complete[!duplicated(m1_complete$Connect_ID),] 
table(m1_complete_nodup$version)


parts <- "SELECT Connect_ID, token, D_512820379, D_471593703, state_d_934298480, D_230663853,
D_335767902, D_982402227, D_919254129, D_699625233, D_564964481, D_795827569, D_544150384,
D_371067537, D_430551721, D_821247024, D_914594314,  state_d_725929722, d_827220437, d_827220437, 
D_949302066 , D_517311251, D_205553981, D_117249500, d_976570371, d_663265240, d_452942800 FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` 
where Connect_ID IS NOT NULL"
querymod4 <- "SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module4_v1_JP` where Connect_ID IS NOT NULL"

parts_table <- bq_project_query(project, parts)
mod4_table <- bq_project_query(project, querymod4)

parts_data <- bq_table_download(parts_table, bigint = "integer64")
mod4_data <- bq_table_download(mod4_table, bigint = "integer64")

parts_data$Connect_ID <- as.numeric(parts_data$Connect_ID) ###need to convert type- m1... is double and parts is character
mod4_data$Connect_ID <- as.numeric(mod4_data$Connect_ID)

mergeall= left_join(m1_complete_nodup, mod4_data, by="Connect_ID") %>%  left_join(parts_data, by="Connect_ID")
dim(mergeall)

knitr::opts_chunk$set(comment = NA)


#Has a recruitment flag
mergeall <- mergeall %>% filter(D_512820379==486306141 | D_512820379==854703046)
dim(mergeall)

active4 <- mergeall %>% filter(D_512820379==486306141)
dim(active4)
passive4 <- mergeall %>% filter(D_512820379==854703046)
dim(passive4)

#User consent submitted
mergeall <- mergeall %>% filter(D_919254129==353358909)
dim(mergeall)

#User profile submitted
mergeall <- mergeall %>% filter(D_699625233==353358909)
dim(mergeall)

#Verified by site
sum(mergeall$d_821247024==197316935, na.rm=TRUE)
#all who have started or completed survey are verified

#Mod1 completed
mergeall <- mergeall %>% filter(D_949302066==231311385)
dim(mergeall)


#Mod4 completed
module4 <- mergeall %>% filter(d_663265240==231311385)
dim(module4)


```

```{r MissingnessLibraries, warning=FALSE, include=FALSE}
#Missingness Analysis Set Up

#install.packages("naniar")
#install.packages("UpSetR")
library(naniar)
library(UpSetR)
library(tidyverse)



Mod4 <- as_tibble(module4)
```

```{r, echo=FALSE, warning=FALSE}
cat("Module 4 Completed by : ", dim(module4)[[1]], " Total Participants")
```


# Home 1 Address

## HealthPartners
```{r HP, warning=FALSE, echo=FALSE, message=FALSE}

HP <- Mod4 %>%  filter(d_827220437=='531629870')
  
HP$Street_Number <- HP$D_121490150_D_255248624
HP$Street_Name <- HP$D_121490150_D_945532934
HP$Apt_Number <- HP$D_121490150_D_469838242
HP$City <- HP$D_121490150_D_303500597
HP$State <- HP$D_121490150_D_195068098
HP$ZIP <- HP$D_121490150_D_202784871
HP$Country <- HP$D_121490150_D_831127170



home1skip <- HP %>% select(Connect_ID, Street_Number, Street_Name, City, State, ZIP, Country)
home1skip= home1skip %>%  mutate(Address1= case_when(is.na(Street_Number) & is.na(Street_Name) & 
                                                       is.na(City) & is.na(State) & is.na(ZIP)& is.na(Country)~"Skipped Entire Home 1 Address "))

dt_home1skip_summary <- home1skip %>% dplyr::group_by(Address1) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(Address1, n, percentage)
dt_home1skip_summary <- dt_home1skip_summary[1,]


dt_home1skip_summary[2,1] <- "Skipped Street Number" 
dt_home1skip_summary[2,2] <- sum(is.na(home1skip$Street_Number))
dt_home1skip_summary[2,3] <- (sum(is.na(home1skip$Street_Number))/dim(home1skip)[[1]])*100

dt_home1skip_summary[3,1] <- "Skipped Street Name" 
dt_home1skip_summary[3,2] <- sum(is.na(home1skip$Street_Name))
dt_home1skip_summary[3,3] <- (sum(is.na(home1skip$Street_Name))/dim(home1skip)[[1]])*100

dt_home1skip_summary[4,1] <- "Skipped City"
dt_home1skip_summary[4,2] <- sum(is.na(home1skip$City))
dt_home1skip_summary[4,3] <- (sum(is.na(home1skip$City))/dim(home1skip)[[1]])*100

dt_home1skip_summary[5,1] <- "Skipped State"
dt_home1skip_summary[5,2] <- sum(is.na(home1skip$State))
dt_home1skip_summary[5,3] <- (sum(is.na(home1skip$State))/dim(home1skip)[[1]])*100

dt_home1skip_summary[6,1] <- "Skipped ZIP"
dt_home1skip_summary[6,2] <- sum(is.na(home1skip$ZIP))
dt_home1skip_summary[6,3] <- (sum(is.na(home1skip$ZIP))/dim(home1skip)[[1]])*100

dt_home1skip_summary[7,1] <- "Skipped Country"
dt_home1skip_summary[7,2] <- sum(is.na(home1skip$Country))
dt_home1skip_summary[7,3] <- (sum(is.na(home1skip$Country))/dim(home1skip)[[1]])*100



dt_home1skip_summary_gtHP <- dt_home1skip_summary %>%  gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Address 1 Components Skipped by HealthPartners")) %>% 
  cols_label(n= md("**Number of Participants**"),Address1 = md("**Question**"), percentage = md("**Percentage of Participants**")) %>% 
  #grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Address1,
    )
  ) 
tab_footnote(
  dt_home1skip_summary_gtHP,
  md("Each row is not mutually exclusive. Those that skip all address 1 components will be counted in each row. Those that skip multiple components will be counted in each of the component rows; for example, if both Street Number and Street Name are skipped by a participant, they are counted in both the 'Skipped Street Number' and 'Skipped Street Name' rows."),
  locations = cells_column_labels(columns = Address1),
  placement = c("left")
)


```



## Henry Ford Health System
```{r HF, warning=FALSE, echo=FALSE, message=FALSE}

HF <- Mod4 %>%  filter(d_827220437=='548392715')
  
HF$Street_Number <- HF$D_121490150_D_255248624
HF$Street_Name <- HF$D_121490150_D_945532934
HF$Apt_Number <- HF$D_121490150_D_469838242
HF$City <- HF$D_121490150_D_303500597
HF$State <- HF$D_121490150_D_195068098
HF$ZIP <- HF$D_121490150_D_202784871
HF$Country <- HF$D_121490150_D_831127170



home1skip <- HF %>% select(Connect_ID, Street_Number, Street_Name, City, State, ZIP, Country)
home1skip= home1skip %>%  mutate(Address1= case_when(is.na(Street_Number) & is.na(Street_Name) & 
                                                       is.na(City) & is.na(State) & is.na(ZIP)& is.na(Country)~"Skipped Entire Home 1 Address "))

dt_home1skip_summary <- home1skip %>% dplyr::group_by(Address1) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(Address1, n, percentage)
dt_home1skip_summary <- dt_home1skip_summary[1,]


dt_home1skip_summary[2,1] <- "Skipped Street Number" 
dt_home1skip_summary[2,2] <- sum(is.na(home1skip$Street_Number))
dt_home1skip_summary[2,3] <- (sum(is.na(home1skip$Street_Number))/dim(home1skip)[[1]])*100

dt_home1skip_summary[3,1] <- "Skipped Street Name" 
dt_home1skip_summary[3,2] <- sum(is.na(home1skip$Street_Name))
dt_home1skip_summary[3,3] <- (sum(is.na(home1skip$Street_Name))/dim(home1skip)[[1]])*100

dt_home1skip_summary[4,1] <- "Skipped City"
dt_home1skip_summary[4,2] <- sum(is.na(home1skip$City))
dt_home1skip_summary[4,3] <- (sum(is.na(home1skip$City))/dim(home1skip)[[1]])*100

dt_home1skip_summary[5,1] <- "Skipped State"
dt_home1skip_summary[5,2] <- sum(is.na(home1skip$State))
dt_home1skip_summary[5,3] <- (sum(is.na(home1skip$State))/dim(home1skip)[[1]])*100

dt_home1skip_summary[6,1] <- "Skipped ZIP"
dt_home1skip_summary[6,2] <- sum(is.na(home1skip$ZIP))
dt_home1skip_summary[6,3] <- (sum(is.na(home1skip$ZIP))/dim(home1skip)[[1]])*100

dt_home1skip_summary[7,1] <- "Skipped Country"
dt_home1skip_summary[7,2] <- sum(is.na(home1skip$Country))
dt_home1skip_summary[7,3] <- (sum(is.na(home1skip$Country))/dim(home1skip)[[1]])*100



dt_home1skip_summary_gtHF <- dt_home1skip_summary %>%  gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Address 1 Components Skipped by Henry Ford Health System")) %>% 
  cols_label(n= md("**Number of Participants**"),Address1 = md("**Question**"), percentage = md("**Percentage of Participants**")) %>% 
  #grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Address1,
    )
  ) 
tab_footnote(
  dt_home1skip_summary_gtHF,
  md("Each row is not mutually exclusive. Those that skip all address 1 components will be counted in each row. Those that skip multiple components will be counted in each of the component rows; for example, if both Street Number and Street Name are skipped by a participant, they are counted in both the 'Skipped Street Number' and 'Skipped Street Name' rows."),
  locations = cells_column_labels(columns = Address1),
  placement = c("left")
)

```


## Kaiser Permanente Colorado
```{r KPCO, warning=FALSE, echo=FALSE, message=FALSE}

KPCO <- Mod4 %>%  filter(d_827220437=='125001209')
  
KPCO$Street_Number <- KPCO$D_121490150_D_255248624
KPCO$Street_Name <- KPCO$D_121490150_D_945532934
KPCO$Apt_Number <- KPCO$D_121490150_D_469838242
KPCO$City <- KPCO$D_121490150_D_303500597
KPCO$State <- KPCO$D_121490150_D_195068098
KPCO$ZIP <- KPCO$D_121490150_D_202784871
KPCO$Country <- KPCO$D_121490150_D_831127170



home1skip <- KPCO %>% select(Connect_ID, Street_Number, Street_Name, City, State, ZIP, Country)
home1skip= home1skip %>%  mutate(Address1= case_when(is.na(Street_Number) & is.na(Street_Name) & 
                                                       is.na(City) & is.na(State) & is.na(ZIP)& is.na(Country)~"Skipped Entire Home 1 Address "))

dt_home1skip_summary <- home1skip %>% dplyr::group_by(Address1) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(Address1, n, percentage)
dt_home1skip_summary <- dt_home1skip_summary[1,]


dt_home1skip_summary[2,1] <- "Skipped Street Number" 
dt_home1skip_summary[2,2] <- sum(is.na(home1skip$Street_Number))
dt_home1skip_summary[2,3] <- (sum(is.na(home1skip$Street_Number))/dim(home1skip)[[1]])*100

dt_home1skip_summary[3,1] <- "Skipped Street Name" 
dt_home1skip_summary[3,2] <- sum(is.na(home1skip$Street_Name))
dt_home1skip_summary[3,3] <- (sum(is.na(home1skip$Street_Name))/dim(home1skip)[[1]])*100

dt_home1skip_summary[4,1] <- "Skipped City"
dt_home1skip_summary[4,2] <- sum(is.na(home1skip$City))
dt_home1skip_summary[4,3] <- (sum(is.na(home1skip$City))/dim(home1skip)[[1]])*100

dt_home1skip_summary[5,1] <- "Skipped State"
dt_home1skip_summary[5,2] <- sum(is.na(home1skip$State))
dt_home1skip_summary[5,3] <- (sum(is.na(home1skip$State))/dim(home1skip)[[1]])*100

dt_home1skip_summary[6,1] <- "Skipped ZIP"
dt_home1skip_summary[6,2] <- sum(is.na(home1skip$ZIP))
dt_home1skip_summary[6,3] <- (sum(is.na(home1skip$ZIP))/dim(home1skip)[[1]])*100

dt_home1skip_summary[7,1] <- "Skipped Country"
dt_home1skip_summary[7,2] <- sum(is.na(home1skip$Country))
dt_home1skip_summary[7,3] <- (sum(is.na(home1skip$Country))/dim(home1skip)[[1]])*100



dt_home1skip_summary_gtKPCO <- dt_home1skip_summary %>%  gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Address 1 Components Skipped by KPCO")) %>% 
  cols_label(n= md("**Number of Participants**"),Address1 = md("**Question**"), percentage = md("**Percentage of Participants**")) %>% 
  #grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Address1,
    )
  ) 
tab_footnote(
  dt_home1skip_summary_gtKPCO,
  md("Each row is not mutually exclusive. Those that skip all address 1 components will be counted in each row. Those that skip multiple components will be counted in each of the component rows; for example, if both Street Number and Street Name are skipped by a participant, they are counted in both the 'Skipped Street Number' and 'Skipped Street Name' rows."),
  locations = cells_column_labels(columns = Address1),
  placement = c("left")
)


```


## Kaiser Permanente Georgia
```{r KPGA, warning=FALSE, echo=FALSE, message=FALSE}

KPGA <- Mod4 %>%  filter(d_827220437=='327912200')
  
KPGA$Street_Number <- KPGA$D_121490150_D_255248624
KPGA$Street_Name <- KPGA$D_121490150_D_945532934
KPGA$Apt_Number <- KPGA$D_121490150_D_469838242
KPGA$City <- KPGA$D_121490150_D_303500597
KPGA$State <- KPGA$D_121490150_D_195068098
KPGA$ZIP <- KPGA$D_121490150_D_202784871
KPGA$Country <- KPGA$D_121490150_D_831127170



home1skip <- KPGA %>% select(Connect_ID, Street_Number, Street_Name, City, State, ZIP, Country)
home1skip= home1skip %>%  mutate(Address1= case_when(is.na(Street_Number) & is.na(Street_Name) & 
                                                       is.na(City) & is.na(State) & is.na(ZIP)& is.na(Country)~"Skipped Entire Home 1 Address "))

dt_home1skip_summary <- home1skip %>% dplyr::group_by(Address1) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(Address1, n, percentage)
dt_home1skip_summary <- dt_home1skip_summary[1,]


dt_home1skip_summary[2,1] <- "Skipped Street Number" 
dt_home1skip_summary[2,2] <- sum(is.na(home1skip$Street_Number))
dt_home1skip_summary[2,3] <- (sum(is.na(home1skip$Street_Number))/dim(home1skip)[[1]])*100

dt_home1skip_summary[3,1] <- "Skipped Street Name" 
dt_home1skip_summary[3,2] <- sum(is.na(home1skip$Street_Name))
dt_home1skip_summary[3,3] <- (sum(is.na(home1skip$Street_Name))/dim(home1skip)[[1]])*100

dt_home1skip_summary[4,1] <- "Skipped City"
dt_home1skip_summary[4,2] <- sum(is.na(home1skip$City))
dt_home1skip_summary[4,3] <- (sum(is.na(home1skip$City))/dim(home1skip)[[1]])*100

dt_home1skip_summary[5,1] <- "Skipped State"
dt_home1skip_summary[5,2] <- sum(is.na(home1skip$State))
dt_home1skip_summary[5,3] <- (sum(is.na(home1skip$State))/dim(home1skip)[[1]])*100

dt_home1skip_summary[6,1] <- "Skipped ZIP"
dt_home1skip_summary[6,2] <- sum(is.na(home1skip$ZIP))
dt_home1skip_summary[6,3] <- (sum(is.na(home1skip$ZIP))/dim(home1skip)[[1]])*100

dt_home1skip_summary[7,1] <- "Skipped Country"
dt_home1skip_summary[7,2] <- sum(is.na(home1skip$Country))
dt_home1skip_summary[7,3] <- (sum(is.na(home1skip$Country))/dim(home1skip)[[1]])*100



dt_home1skip_summary_gtKPGA <- dt_home1skip_summary %>%  gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Address 1 Components Skipped by KPGA")) %>% 
  cols_label(n= md("**Number of Participants**"),Address1 = md("**Question**"), percentage = md("**Percentage of Participants**")) %>% 
  #grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Address1,
    )
  ) 
tab_footnote(
  dt_home1skip_summary_gtKPGA,
  md("Each row is not mutually exclusive. Those that skip all address 1 components will be counted in each row. Those that skip multiple components will be counted in each of the component rows; for example, if both Street Number and Street Name are skipped by a participant, they are counted in both the 'Skipped Street Number' and 'Skipped Street Name' rows."),
  locations = cells_column_labels(columns = Address1),
  placement = c("left")
)



```


## Kaiser Permanente Hawaii
```{r KPHI, warning=FALSE, echo=FALSE, message=FALSE}

KPHI <- Mod4 %>%  filter(d_827220437=='300267574')
  
KPHI$Street_Number <- KPHI$D_121490150_D_255248624
KPHI$Street_Name <- KPHI$D_121490150_D_945532934
KPHI$Apt_Number <- KPHI$D_121490150_D_469838242
KPHI$City <- KPHI$D_121490150_D_303500597
KPHI$State <- KPHI$D_121490150_D_195068098
KPHI$ZIP <- KPHI$D_121490150_D_202784871
KPHI$Country <- KPHI$D_121490150_D_831127170



home1skip <- KPHI %>% select(Connect_ID, Street_Number, Street_Name, City, State, ZIP, Country)
home1skip= home1skip %>%  mutate(Address1= case_when(is.na(Street_Number) & is.na(Street_Name) & 
                                                       is.na(City) & is.na(State) & is.na(ZIP)& is.na(Country)~"Skipped Entire Home 1 Address "))

dt_home1skip_summary <- home1skip %>% dplyr::group_by(Address1) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(Address1, n, percentage)
dt_home1skip_summary <- dt_home1skip_summary[1,]


dt_home1skip_summary[2,1] <- "Skipped Street Number" 
dt_home1skip_summary[2,2] <- sum(is.na(home1skip$Street_Number))
dt_home1skip_summary[2,3] <- (sum(is.na(home1skip$Street_Number))/dim(home1skip)[[1]])*100

dt_home1skip_summary[3,1] <- "Skipped Street Name" 
dt_home1skip_summary[3,2] <- sum(is.na(home1skip$Street_Name))
dt_home1skip_summary[3,3] <- (sum(is.na(home1skip$Street_Name))/dim(home1skip)[[1]])*100

dt_home1skip_summary[4,1] <- "Skipped City"
dt_home1skip_summary[4,2] <- sum(is.na(home1skip$City))
dt_home1skip_summary[4,3] <- (sum(is.na(home1skip$City))/dim(home1skip)[[1]])*100

dt_home1skip_summary[5,1] <- "Skipped State"
dt_home1skip_summary[5,2] <- sum(is.na(home1skip$State))
dt_home1skip_summary[5,3] <- (sum(is.na(home1skip$State))/dim(home1skip)[[1]])*100

dt_home1skip_summary[6,1] <- "Skipped ZIP"
dt_home1skip_summary[6,2] <- sum(is.na(home1skip$ZIP))
dt_home1skip_summary[6,3] <- (sum(is.na(home1skip$ZIP))/dim(home1skip)[[1]])*100

dt_home1skip_summary[7,1] <- "Skipped Country"
dt_home1skip_summary[7,2] <- sum(is.na(home1skip$Country))
dt_home1skip_summary[7,3] <- (sum(is.na(home1skip$Country))/dim(home1skip)[[1]])*100



dt_home1skip_summary_gtKPHI <- dt_home1skip_summary %>%  gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Address 1 Components Skipped by KPHI")) %>% 
  cols_label(n= md("**Number of Participants**"),Address1 = md("**Question**"), percentage = md("**Percentage of Participants**")) %>% 
  #grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Address1,
    )
  ) 
tab_footnote(
  dt_home1skip_summary_gtKPHI,
  md("Each row is not mutually exclusive. Those that skip all address 1 components will be counted in each row. Those that skip multiple components will be counted in each of the component rows; for example, if both Street Number and Street Name are skipped by a participant, they are counted in both the 'Skipped Street Number' and 'Skipped Street Name' rows."),
  locations = cells_column_labels(columns = Address1),
  placement = c("left")
)


```


## Kaiser Permanente Northwest
```{r KPNW, warning=FALSE, echo=FALSE, message=FALSE}

KPNW <- Mod4 %>%  filter(d_827220437=='452412599')
  
KPNW$Street_Number <- KPNW$D_121490150_D_255248624
KPNW$Street_Name <- KPNW$D_121490150_D_945532934
KPNW$Apt_Number <- KPNW$D_121490150_D_469838242
KPNW$City <- KPNW$D_121490150_D_303500597
KPNW$State <- KPNW$D_121490150_D_195068098
KPNW$ZIP <- KPNW$D_121490150_D_202784871
KPNW$Country <- KPNW$D_121490150_D_831127170



home1skip <- KPNW %>% select(Connect_ID, Street_Number, Street_Name, City, State, ZIP, Country)
home1skip= home1skip %>%  mutate(Address1= case_when(is.na(Street_Number) & is.na(Street_Name) & 
                                                       is.na(City) & is.na(State) & is.na(ZIP)& is.na(Country)~"Skipped Entire Home 1 Address "))

dt_home1skip_summary <- home1skip %>% dplyr::group_by(Address1) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(Address1, n, percentage)
dt_home1skip_summary <- dt_home1skip_summary[1,]


dt_home1skip_summary[2,1] <- "Skipped Street Number" 
dt_home1skip_summary[2,2] <- sum(is.na(home1skip$Street_Number))
dt_home1skip_summary[2,3] <- (sum(is.na(home1skip$Street_Number))/dim(home1skip)[[1]])*100

dt_home1skip_summary[3,1] <- "Skipped Street Name" 
dt_home1skip_summary[3,2] <- sum(is.na(home1skip$Street_Name))
dt_home1skip_summary[3,3] <- (sum(is.na(home1skip$Street_Name))/dim(home1skip)[[1]])*100

dt_home1skip_summary[4,1] <- "Skipped City"
dt_home1skip_summary[4,2] <- sum(is.na(home1skip$City))
dt_home1skip_summary[4,3] <- (sum(is.na(home1skip$City))/dim(home1skip)[[1]])*100

dt_home1skip_summary[5,1] <- "Skipped State"
dt_home1skip_summary[5,2] <- sum(is.na(home1skip$State))
dt_home1skip_summary[5,3] <- (sum(is.na(home1skip$State))/dim(home1skip)[[1]])*100

dt_home1skip_summary[6,1] <- "Skipped ZIP"
dt_home1skip_summary[6,2] <- sum(is.na(home1skip$ZIP))
dt_home1skip_summary[6,3] <- (sum(is.na(home1skip$ZIP))/dim(home1skip)[[1]])*100

dt_home1skip_summary[7,1] <- "Skipped Country"
dt_home1skip_summary[7,2] <- sum(is.na(home1skip$Country))
dt_home1skip_summary[7,3] <- (sum(is.na(home1skip$Country))/dim(home1skip)[[1]])*100



dt_home1skip_summary_gtKPHNW <- dt_home1skip_summary %>%  gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Address 1 Components Skipped by KPNW")) %>% 
  cols_label(n= md("**Number of Participants**"),Address1 = md("**Question**"), percentage = md("**Percentage of Participants**")) %>% 
  #grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Address1,
    )
  ) 
tab_footnote(
  dt_home1skip_summary_gtKPHNW,
  md("Each row is not mutually exclusive. Those that skip all address 1 components will be counted in each row. Those that skip multiple components will be counted in each of the component rows; for example, if both Street Number and Street Name are skipped by a participant, they are counted in both the 'Skipped Street Number' and 'Skipped Street Name' rows."),
  locations = cells_column_labels(columns = Address1),
  placement = c("left")
)


```


## Marshfield Clinic Health System
```{r MF, warning=FALSE, echo=FALSE, message=FALSE}

MF <- Mod4 %>%  filter(d_827220437=='303349821')
  
MF$Street_Number <- MF$D_121490150_D_255248624
MF$Street_Name <- MF$D_121490150_D_945532934
MF$Apt_Number <- MF$D_121490150_D_469838242
MF$City <- MF$D_121490150_D_303500597
MF$State <- MF$D_121490150_D_195068098
MF$ZIP <- MF$D_121490150_D_202784871
MF$Country <- MF$D_121490150_D_831127170



home1skip <- MF %>% select(Connect_ID, Street_Number, Street_Name, City, State, ZIP, Country)
home1skip= home1skip %>%  mutate(Address1= case_when(is.na(Street_Number) & is.na(Street_Name) & 
                                                       is.na(City) & is.na(State) & is.na(ZIP)& is.na(Country)~"Skipped Entire Home 1 Address "))

dt_home1skip_summary <- home1skip %>% dplyr::group_by(Address1) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(Address1, n, percentage)
dt_home1skip_summary <- dt_home1skip_summary[1,]


dt_home1skip_summary[2,1] <- "Skipped Street Number" 
dt_home1skip_summary[2,2] <- sum(is.na(home1skip$Street_Number))
dt_home1skip_summary[2,3] <- (sum(is.na(home1skip$Street_Number))/dim(home1skip)[[1]])*100

dt_home1skip_summary[3,1] <- "Skipped Street Name" 
dt_home1skip_summary[3,2] <- sum(is.na(home1skip$Street_Name))
dt_home1skip_summary[3,3] <- (sum(is.na(home1skip$Street_Name))/dim(home1skip)[[1]])*100

dt_home1skip_summary[4,1] <- "Skipped City"
dt_home1skip_summary[4,2] <- sum(is.na(home1skip$City))
dt_home1skip_summary[4,3] <- (sum(is.na(home1skip$City))/dim(home1skip)[[1]])*100

dt_home1skip_summary[5,1] <- "Skipped State"
dt_home1skip_summary[5,2] <- sum(is.na(home1skip$State))
dt_home1skip_summary[5,3] <- (sum(is.na(home1skip$State))/dim(home1skip)[[1]])*100

dt_home1skip_summary[6,1] <- "Skipped ZIP"
dt_home1skip_summary[6,2] <- sum(is.na(home1skip$ZIP))
dt_home1skip_summary[6,3] <- (sum(is.na(home1skip$ZIP))/dim(home1skip)[[1]])*100

dt_home1skip_summary[7,1] <- "Skipped Country"
dt_home1skip_summary[7,2] <- sum(is.na(home1skip$Country))
dt_home1skip_summary[7,3] <- (sum(is.na(home1skip$Country))/dim(home1skip)[[1]])*100



dt_home1skip_summary_gtMF <- dt_home1skip_summary %>%  gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Address 1 Components Skipped by Marshfield")) %>% 
  cols_label(n= md("**Number of Participants**"),Address1 = md("**Question**"), percentage = md("**Percentage of Participants**")) %>% 
  #grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Address1,
    )
  ) 

tab_footnote(
  dt_home1skip_summary_gtMF,
  md("Each row is not mutually exclusive. Those that skip all address 1 components will be counted in each row. Those that skip multiple components will be counted in each of the component rows; for example, if both Street Number and Street Name are skipped by a participant, they are counted in both the 'Skipped Street Number' and 'Skipped Street Name' rows."),
  locations = cells_column_labels(columns = Address1),
  placement = c("left")
)

```


## Sanford Health
```{r SF, warning=FALSE, echo=FALSE, message=FALSE}

SF <- Mod4 %>%  filter(d_827220437=='657167265')
  
SF$Street_Number <- SF$D_121490150_D_255248624
SF$Street_Name <- SF$D_121490150_D_945532934
SF$Apt_Number <- SF$D_121490150_D_469838242
SF$City <- SF$D_121490150_D_303500597
SF$State <- SF$D_121490150_D_195068098
SF$ZIP <- SF$D_121490150_D_202784871
SF$Country <- SF$D_121490150_D_831127170



home1skip <- SF %>% select(Connect_ID, Street_Number, Street_Name, City, State, ZIP, Country)
home1skip= home1skip %>%  mutate(Address1= case_when(is.na(Street_Number) & is.na(Street_Name) & 
                                                       is.na(City) & is.na(State) & is.na(ZIP)& is.na(Country)~"Skipped Entire Home 1 Address "))

dt_home1skip_summary <- home1skip %>% dplyr::group_by(Address1) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(Address1, n, percentage)
dt_home1skip_summary <- dt_home1skip_summary[1,]


dt_home1skip_summary[2,1] <- "Skipped Street Number" 
dt_home1skip_summary[2,2] <- sum(is.na(home1skip$Street_Number))
dt_home1skip_summary[2,3] <- (sum(is.na(home1skip$Street_Number))/dim(home1skip)[[1]])*100

dt_home1skip_summary[3,1] <- "Skipped Street Name" 
dt_home1skip_summary[3,2] <- sum(is.na(home1skip$Street_Name))
dt_home1skip_summary[3,3] <- (sum(is.na(home1skip$Street_Name))/dim(home1skip)[[1]])*100

dt_home1skip_summary[4,1] <- "Skipped City"
dt_home1skip_summary[4,2] <- sum(is.na(home1skip$City))
dt_home1skip_summary[4,3] <- (sum(is.na(home1skip$City))/dim(home1skip)[[1]])*100

dt_home1skip_summary[5,1] <- "Skipped State"
dt_home1skip_summary[5,2] <- sum(is.na(home1skip$State))
dt_home1skip_summary[5,3] <- (sum(is.na(home1skip$State))/dim(home1skip)[[1]])*100

dt_home1skip_summary[6,1] <- "Skipped ZIP"
dt_home1skip_summary[6,2] <- sum(is.na(home1skip$ZIP))
dt_home1skip_summary[6,3] <- (sum(is.na(home1skip$ZIP))/dim(home1skip)[[1]])*100

dt_home1skip_summary[7,1] <- "Skipped Country"
dt_home1skip_summary[7,2] <- sum(is.na(home1skip$Country))
dt_home1skip_summary[7,3] <- (sum(is.na(home1skip$Country))/dim(home1skip)[[1]])*100



dt_home1skip_summary_gtSF <- dt_home1skip_summary %>%  gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Address 1 Components Skipped by Sanford")) %>% 
  cols_label(n= md("**Number of Participants**"),Address1 = md("**Question**"), percentage = md("**Percentage of Participants**")) %>% 
  #grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Address1,
    )
  ) 
tab_footnote(
  dt_home1skip_summary_gtSF,
  md("Each row is not mutually exclusive. Those that skip all address 1 components will be counted in each row. Those that skip multiple components will be counted in each of the component rows; for example, if both Street Number and Street Name are skipped by a participant, they are counted in both the 'Skipped Street Number' and 'Skipped Street Name' rows."),
  locations = cells_column_labels(columns = Address1),
  placement = c("left")
)


```



## University of Chicago Medicine
```{r UC, warning=FALSE, echo=FALSE, message=FALSE}

UC <- Mod4 %>%  filter(d_827220437=='809703864')
  
UC$Street_Number <- UC$D_121490150_D_255248624
UC$Street_Name <- UC$D_121490150_D_945532934
UC$Apt_Number <- UC$D_121490150_D_469838242
UC$City <- UC$D_121490150_D_303500597
UC$State <- UC$D_121490150_D_195068098
UC$ZIP <- UC$D_121490150_D_202784871
UC$Country <- UC$D_121490150_D_831127170



home1skip <- UC %>% select(Connect_ID, Street_Number, Street_Name, City, State, ZIP, Country)
home1skip= home1skip %>%  mutate(Address1= case_when(is.na(Street_Number) & is.na(Street_Name) & 
                                                       is.na(City) & is.na(State) & is.na(ZIP)& is.na(Country)~"Skipped Entire Home 1 Address "))

dt_home1skip_summary <- home1skip %>% dplyr::group_by(Address1) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(Address1, n, percentage)
dt_home1skip_summary <- dt_home1skip_summary[1,]


dt_home1skip_summary[2,1] <- "Skipped Street Number" 
dt_home1skip_summary[2,2] <- sum(is.na(home1skip$Street_Number))
dt_home1skip_summary[2,3] <- (sum(is.na(home1skip$Street_Number))/dim(home1skip)[[1]])*100

dt_home1skip_summary[3,1] <- "Skipped Street Name" 
dt_home1skip_summary[3,2] <- sum(is.na(home1skip$Street_Name))
dt_home1skip_summary[3,3] <- (sum(is.na(home1skip$Street_Name))/dim(home1skip)[[1]])*100

dt_home1skip_summary[4,1] <- "Skipped City"
dt_home1skip_summary[4,2] <- sum(is.na(home1skip$City))
dt_home1skip_summary[4,3] <- (sum(is.na(home1skip$City))/dim(home1skip)[[1]])*100

dt_home1skip_summary[5,1] <- "Skipped State"
dt_home1skip_summary[5,2] <- sum(is.na(home1skip$State))
dt_home1skip_summary[5,3] <- (sum(is.na(home1skip$State))/dim(home1skip)[[1]])*100

dt_home1skip_summary[6,1] <- "Skipped ZIP"
dt_home1skip_summary[6,2] <- sum(is.na(home1skip$ZIP))
dt_home1skip_summary[6,3] <- (sum(is.na(home1skip$ZIP))/dim(home1skip)[[1]])*100

dt_home1skip_summary[7,1] <- "Skipped Country"
dt_home1skip_summary[7,2] <- sum(is.na(home1skip$Country))
dt_home1skip_summary[7,3] <- (sum(is.na(home1skip$Country))/dim(home1skip)[[1]])*100



dt_home1skip_summary_gtUC <- dt_home1skip_summary %>%  gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Address 1 Components Skipped by UChicago")) %>% 
  cols_label(n= md("**Number of Participants**"),Address1 = md("**Question**"), percentage = md("**Percentage of Participants**")) %>% 
  #grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Address1,
    )
  ) 
tab_footnote(
  dt_home1skip_summary_gtUC,
  md("Each row is not mutually exclusive. Those that skip all address 1 components will be counted in each row. Those that skip multiple components will be counted in each of the component rows; for example, if both Street Number and Street Name are skipped by a participant, they are counted in both the 'Skipped Street Number' and 'Skipped Street Name' rows."),
  locations = cells_column_labels(columns = Address1),
  placement = c("left")
)




```

