---
title: "IRB Request"
author: "Kelsey Dowling"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r libraries, include=FALSE}


#  pdf-engine: xelatex
#tinytex::install_tinytex()

library(bigrquery)
library(epiDisplay) ##recommended applied here crosstable, tab1
library(gmodels) ##recommended
library(arsenal)
library(gtsummary)
library(rio)
library(glue)


library(ggplot2)
library(gridExtra)
library(scales)
library(gt)
library(tinytex)
library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(lubridate) ###date time
library(stringr) ###to work on patterns, charaters
library(kableExtra)


options(tinytex.verbose = TRUE)

bq_auth()

project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" 
```




```{r merge1, include=FALSE, warning=FALSE}

## MERGE MOD1V1, MOD1V2


dictionary <- rio::import("https://episphere.github.io/conceptGithubActions/aggregate.json",format = "json")
dd <- dplyr::bind_rows(dictionary,.id="CID")
dd <-rbindlist(dictionary,fill=TRUE,use.names=TRUE,idcol="CID")
dd$`Variable Label`[is.na(dd$`Variable Label`)] <- replace_na(dd$'Variable Name')

dd <- as.data.frame.matrix(do.call("rbind",dictionary)) 
dd$CID <- rownames(dd)
#https://shaivyakodan.medium.com/7-useful-r-packages-for-analysis-7f60d28dca98
#devtools::install_github("tidyverse/reprex")

project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" ##project and billing should be consistent
##517311251 Date/time Status of Completion of Background and Overall Health                         SrvBOH_TmComplete_v1r0
##949302066 Flag for Baseline Module Background and Overall Health                        SrvBOH_BaseStatus_v1r0
recr_M1 <- bq_project_query(project, query="SELECT token,Connect_ID, d_821247024, d_914594314,  d_827220437,d_512820379,
                            d_949302066 , d_517311251  FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` WHERE  d_821247024='197316935'")
recr_m1 <- bq_table_download(recr_M1,bigint = "integer64",n_max = Inf, page_size = 10000)
cnames <- names(recr_m1)
# Check that it doesn't match any non-number
numbers_only <- function(x) !grepl("\\D", x)
# to check variables in recr_noinact_wl1
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(recr_m1,varname)
  recr_m1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}

sql_M1_1 <- bq_project_query(project, query="SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v1_JP` where Connect_ID is not null")
sql_M1_2 <- bq_project_query(project, query="SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2_JP` where Connect_ID is not null")


M1_V1 <- bq_table_download(sql_M1_1,bigint = "integer64") #1436 #1436 vars: 1507 01112023 
M1_V2 <- bq_table_download(sql_M1_2,bigint = "integer64") #2333 #3033 01112023 var:1531 #6339 obs 1893 vars 05022023

mod1_v1 <- M1_V1
cnames <- names(M1_V1)
###to check variables and convert to numeric
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(mod1_v1,varname)
  mod1_v1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}
mod1_v2 <- M1_V2
cnames <- names(M1_V2)
###to check variables and convert to numeric
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(mod1_v2,varname)
  mod1_v2[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}

M1_V1.var <- colnames(M1_V1)
M1_V2.var <- colnames(M1_V2)
var.matched <- M1_V1.var[which(M1_V1.var %in% M1_V2.var)]
length(var.matched)  #1275 #1278 vars 01112023 #1348 vars 05022023

V1_only_vars <- colnames(M1_V1)[colnames(M1_V1) %nin% var.matched] #232 #229 01112023 #159 05022023
V2_only_vars <- colnames(M1_V2)[colnames(M1_V2) %nin% var.matched] #253 #253 01112023 #545 05022023

length(M1_V1$Connect_ID[M1_V1$Connect_ID %in% M1_V2$Connect_ID])
#[1] 59 with the completion of two versions of Module1 
#[1] 62 with completing both versions of M1 ###double checked 03/28/2023
#68 double checked 05/02/2023

common.IDs <- M1_V1$Connect_ID[M1_V1$Connect_ID %in% M1_V2$Connect_ID]
M1_V1_common <- mod1_v1[,var.matched]

M1_V2_common <- mod1_v2[,var.matched]
M1_V1_common$version <- 1
M1_V2_common$version <- 2

##to check the completion of M1 among these duplicates
partM1_dups <- recr_m1[which(recr_m1$Connect_ID %in% common.IDs),]
table(partM1_dups$d_949302066)

M1_common  <- rbind(M1_V1_common, M1_V2_common) #including 136 duplicates (version 1 and version 2) from 68 participants 05022023
#M1_response <- matrix(data=NA, nrow=118, ncol=967)

m1_v1_only <- mod1_v1[,c("Connect_ID", V1_only_vars)] #230 vars 03282023 #160 vars 05/02/2023
m1_v2_only <- mod1_v2[,c("Connect_ID", V2_only_vars)] #255 vars 03282023 #546 vars 05/02/2023
m1_v1_only$version <- 1
m1_v2_only$version <- 2
#for (i in 1:length)
##to check the completion in each version
length(recr_m1$Connect_ID[which(recr_m1$Connect_ID %in% m1_v1_only$Connect_ID & recr_m1$d_949302066 ==231311385)]) #1364 03282023 # 1370 05022023
length(recr_m1$Connect_ID[which(recr_m1$Connect_ID %in% m1_v2_only$Connect_ID & recr_m1$d_949302066 ==231311385)]) #4870 03282023 # 5731 05022023


m1_common <- rbind(M1_V1_common,M1_V2_common)
m1_common_v1 <- base::merge(m1_common, m1_v1_only, by=c("Connect_ID","version"),all.x=TRUE)
m1_combined_v1v2 <- base::merge(m1_common_v1,m1_v2_only,by=c("Connect_ID","version"),all.x=TRUE)
m1_complete <- m1_combined_v1v2[which(m1_combined_v1v2$Connect_ID %in% recr_m1$Connect_ID[which(recr_m1$d_949302066 ==231311385 )]),] #7289 including duplicates 05022023

m1_complete <- m1_complete %>% arrange(desc(version)) 


m1_complete_nodup <- m1_complete[!duplicated(m1_complete$Connect_ID),] 
table(m1_complete_nodup$version)







#dim(base_vars)

knitr::opts_chunk$set(comment = NA)



parts <- "SELECT Connect_ID, d_564964481, d_795827569, d_544150384, d_117249500, d_454445267,d_949302066 FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` where Connect_ID IS NOT NULL and d_821247024='197316935' and d_747006172!='353358909' and d_831041022!='353358909'" 
parts_table <- bq_project_query(project, parts)
parts_data <- bq_table_download(parts_table, bigint = "integer64",n_max = Inf, page_size = 10000)

parts_data$Connect_ID <- as.numeric(parts_data$Connect_ID)


irb= left_join(parts_data,m1_complete_nodup,  by="Connect_ID") 
dim(irb)


```


```{r Race, warning=FALSE, echo=FALSE, message=FALSE}


## Multi-racial

multi_race=0    
for (i in 1:length(irb$Connect_ID)){
  AI=ifelse((irb$D_384191091_D_384191091_D_583826374[[i]]==1 & (irb$D_384191091_D_384191091_D_636411467[[i]]==1 | irb$D_384191091_D_384191091_D_458435048[[i]]==1|
                                               irb$D_384191091_D_384191091_D_706998638[[i]]==1 | irb$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                               irb$D_384191091_D_384191091_D_586825330[[i]]==1 | irb$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                               irb$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  As=ifelse((irb$D_384191091_D_384191091_D_636411467[[i]]==1 & (irb$D_384191091_D_384191091_D_583826374[[i]]==1 | irb$D_384191091_D_384191091_D_458435048[[i]]==1|
                                                        irb$D_384191091_D_384191091_D_706998638[[i]]==1 | irb$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_586825330[[i]]==1 | irb$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Bl=ifelse((irb$D_384191091_D_384191091_D_458435048[[i]]==1 & (irb$D_384191091_D_384191091_D_583826374[[i]]==1 | irb$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        irb$D_384191091_D_384191091_D_706998638[[i]]==1 | irb$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_586825330[[i]]==1 | irb$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Hs=ifelse((irb$D_384191091_D_384191091_D_706998638[[i]]==1 & (irb$D_384191091_D_384191091_D_583826374[[i]]==1 | irb$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        irb$D_384191091_D_384191091_D_458435048[[i]]==1 | irb$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_586825330[[i]]==1 | irb$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Me=ifelse((irb$D_384191091_D_384191091_D_973565052[[i]]==1 & (irb$D_384191091_D_384191091_D_583826374[[i]]==1 | irb$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        irb$D_384191091_D_384191091_D_458435048[[i]]==1 | irb$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_586825330[[i]]==1 | irb$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Hw=ifelse((irb$D_384191091_D_384191091_D_586825330[[i]]==1 & (irb$D_384191091_D_384191091_D_583826374[[i]]==1 | irb$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        irb$D_384191091_D_384191091_D_458435048[[i]]==1 | irb$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_973565052[[i]]==1 | irb$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Wh=ifelse((irb$D_384191091_D_384191091_D_412790539[[i]]==1 & (irb$D_384191091_D_384191091_D_583826374[[i]]==1 | irb$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        irb$D_384191091_D_384191091_D_458435048[[i]]==1 | irb$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_586825330[[i]]==1 | irb$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Ot=ifelse((irb$D_384191091_D_384191091_D_807835037[[i]]==1 & (irb$D_384191091_D_384191091_D_583826374[[i]]==1 | irb$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        irb$D_384191091_D_384191091_D_458435048[[i]]==1 | irb$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_586825330[[i]]==1 | irb$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        irb$D_384191091_D_384191091_D_412790539[[i]]==1)), 1, 0)
  multi_race= multi_race + sum(AI+As+Bl+Hs+Me+Hw+Wh+Ot, na.rm=T)

}

#cat("Percentage of multirace participants:", (multi_race/(dim(irb)[1]))*100)
   
   

irb$multi_racial <- c(rep(1, times=multi_race), rep(0, times=(dim(irb)[1]- multi_race)))




## RACE
currentDate <- Sys.Date()

# Convert to numeric and handle non-numeric values
irb <- irb %>%
  mutate(
    d_544150384 = as.numeric(as.character(d_544150384)),
    d_795827569 = as.numeric(as.character(d_795827569)),
    d_564964481 = as.numeric(as.character(d_564964481))
  )

# Ensure month and day are two digits
irb <- irb %>%
  mutate(
    d_795827569 = ifelse(d_795827569 < 10, paste0("0", d_795827569), as.character(d_795827569)),
    d_564964481 = ifelse(d_564964481 < 10, paste0("0", d_564964481), as.character(d_564964481))
  )

irb = irb %>%  mutate(race= case_when(d_949302066==231311385 & multi_racial==1 ~ "More than One Race",
                                      d_949302066==231311385 &  D_384191091_D_384191091_D_583826374==1 ~ "American Indian/Alaska Native",
                                      d_949302066==231311385 &  D_384191091_D_384191091_D_636411467==1 ~ "Asian",
                                      d_949302066==231311385 &  D_384191091_D_384191091_D_458435048==1 ~ "Black or African American",
                                      #d_949302066==231311385 &  D_384191091_D_384191091_D_706998638==1 ~ "Hispanic, Latino, or Spanish", #category instead
                                      #d_949302066==231311385 &  D_384191091_D_384191091_D_973565052==1 ~ "Middle Eastern or North African", #grouped with White as requested
                                      d_949302066==231311385 &  D_384191091_D_384191091_D_586825330==1 ~ "Native Hawaiian or Other Pacific Islander",
                                      d_949302066==231311385 &  (D_384191091_D_384191091_D_412790539==1 | D_384191091_D_384191091_D_973565052==1) ~ "White",
                                      TRUE  ~ "Unknown or Not Reported"),
                      race_hisp= case_when(d_949302066==231311385 & D_384191091_D_384191091_D_706998638==1 ~ "Hispanic or Latino",
                                           d_949302066==231311385 & (multi_racial==1 | D_384191091_D_384191091_D_583826374==1 | D_384191091_D_384191091_D_636411467==1 |
                                                                       D_384191091_D_384191091_D_458435048==1 |D_384191091_D_384191091_D_973565052==1 | 
                                                                       D_384191091_D_384191091_D_586825330==1 |  D_384191091_D_384191091_D_412790539==1) ~ "Not Hispanic or Latino",
                                           TRUE  ~ "Unknown/Not Reported Ethnicity"),
                     sex_at_birth= case_when(d_949302066==231311385& D_407056417== 536341288 ~ "Female",
                                             d_949302066==231311385 & D_407056417== 654207589 ~ "Male",
                                             TRUE ~"Unknown/Not Reported"),
                     DOB = as.Date(paste(d_544150384, d_564964481, d_795827569, sep = "-")),
                     consent_date = as.Date(d_454445267),
                     rough_age=lubridate::time_length(consent_date-DOB, "year"),
                     age= round(rough_age,digits=0))

                     
```
 
```{r Documenting, echo=FALSE, message=FALSE, warning=FALSE, collapse=TRUE}

wd_ver <- "SELECT Connect_ID,d_821247024,d_747006172  FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` where Connect_ID IS NOT NULL" 
wd_ver_table <- bq_project_query(project, wd_ver)
wd_ver_data <- bq_table_download(wd_ver_table, bigint = "integer64",n_max = Inf, page_size = 10000)


wd <- wd_ver_data %>%  filter(d_747006172=='353358909' & d_821247024=='197316935')
ver <- wd_ver_data %>%  filter(d_821247024=='197316935') #d_747006172!='353358909' & 
finished_m1 <- irb %>% filter(d_949302066=='231311385')
current_date <- Sys.Date()

cat("Run on data extracted: 2024-07-01")

cat("Total number of verified participants= ", nrow(ver))

cat("Total number of verified participants who are withdrawn = ", nrow(wd))

cat("Denominator included in this report = ", nrow(irb))

cat("Of those,", nrow(finished_m1) , " submitted Module 1.")	



```
 
Participants who did not submit Module 1 are counted as race, ethnicity and sex = unknown.

The question RACEETH was used for race and ethnicity.

The question on sex at birth was used for this report. It is a required question on Module 1.

The age listed is the age at consent, calculated by subtracting the DOB from the date the participant consented.

Middle Eastern or North African is an option in our survey but not an option on the Inclusion 
Enrollment Report. Following former census precedent, we classified those participants as White.

Hispanic, Latino, or Spanish is a race option in our survey but not an option on the Inclusion
Enrollment Report. For those that selected Hispanic, Latino, or Spanish as their only race in Module 1,
we classified  as 'Unknown/Not Reported'.

If Hispanic, Latino or Spanish was not selected but RACEETH was answered with at least one response category, 
they are defined as Ethnicity = Not Hispanic or Latino.

If Hispanic, Latino or Spanish was selected and RACEETH was answered with at least one response category, 
they are defined as Ethnicity = Hispanic or Latino.

If RACETH was entirely missing, Ethnicity = Unknown.


 
```{r Table1, warning=FALSE, echo=FALSE, message=FALSE}



count_table <- irb %>%
  group_by(race, race_hisp, sex_at_birth) %>%
  summarize(count = n(), .groups = 'drop') %>%
  arrange(race, race_hisp, sex_at_birth)

colnames(count_table) <- c("Race", "Ethnicity", "Sex", "Total")


count_table %>%  gt::gt(rowname_col = "row_lab")  %>%
  tab_header(title = md("Cumulative Inclusion Enrollment Report")) %>%
  grand_summary_rows(column=Total,fns = ~sum(.,na.rm = T))|>
  tab_options(stub.font.weight = "bold",
              table.font.size = 6) 
    
  
```


```{r Table2, warning=FALSE, echo=FALSE, message=FALSE}
irb$age_unit <- rep("Years", times=nrow(irb))

table2csv <- irb %>%  group_by(Connect_ID) %>%  select(Connect_ID, race,race_hisp, sex_at_birth,age, age_unit) 
table2csv <- table2csv[, c(2:ncol(table2csv))]

write.csv(table2csv,glue("Participant_Age_Data_Table_{currentDate}.csv"),row.names = F,na="")

```

```{r crosswalk, warning=FALSE, echo=FALSE, message=FALSE}



irb= irb %>%  mutate(actual_race= case_when(multi_racial==1 ~ "Multi-Racial",
                                                     D_384191091_D_384191091_D_583826374==1 ~ "American Indian or Native American",
                                                     D_384191091_D_384191091_D_636411467==1 ~ "Asian/Asian American",
                                                     D_384191091_D_384191091_D_458435048==1 ~ "Black, African American, or African",
                                                     D_384191091_D_384191091_D_706998638==1 ~ "Hispanic, Latino, or Spanish",
                                                     D_384191091_D_384191091_D_973565052==1 ~ "Middle Eastern or North African",
                                                     D_384191091_D_384191091_D_586825330==1 ~ "Hawaiian or Pacific Islander",
                                                     D_384191091_D_384191091_D_412790539==1 ~ "White",
                                                     (D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Other",
                                                     D_384191091_D_384191091_D_746038746==1 ~ "Prefer Not to Answer",
                                                     TRUE  ~ "Skipped this question "))

race_crosswalk <- irb %>% dplyr::select(race,actual_race)  %>% 
  tbl_cross(
    row = actual_race,
    col = race,
    digits=c(0,1),
    percent = "col",
    label=list(actual_race="Module 1 Race Answers", race= "CIE Race Options"),
    missing="ifany",
    margin_text="Total")

race_crosswalk_totals <- as.data.frame(race_crosswalk)

race_crosswalk_totals <- race_crosswalk_totals[-1, ]

write.csv(race_crosswalk_totals,glue("RACEETH Options from Module 1 vs Race for the inclusion.csv"),row.names = F,na="")

# cross_race <- knitr::kable(race_crosswalk_totals , caption='RACEETH Options from Module 1 vs Race for the inclusion', row.names=FALSE,align=c("l","c","c","c","c","c","c"), booktabs = TRUE)  %>% kable_styling(latex_options = "scale_down")
# landscape(cross_race)






eth_crosswalk <- irb %>% dplyr::select(race_hisp,actual_race)  %>% 
  tbl_cross(
    row = actual_race,
    col = race_hisp,
    digits=c(0,1),
    percent = "col",
    label=list(actual_race="Module 1 Race Answers", race_hisp= "CIE Ethnicity Options"),
    missing="ifany",
    margin_text="Total")

eth_crosswalk_totals <- as.data.frame(eth_crosswalk)

eth_crosswalk_totals <- eth_crosswalk_totals[-1, ]


cross_eth <- knitr::kable(eth_crosswalk_totals , caption='RACEETH Options from Module 1 vs Ethnicity for the inclusion', row.names=FALSE,align=c("l","c","c","c","c","c","c"), booktabs = TRUE)  %>% kable_styling(latex_options = "scale_down")
landscape(cross_eth)


```

