---
title: "Letter Variant Next Steps"
author: "Kelsey Sanchez"
date: "`r Sys.Date()`"
header-includes:  
    \usepackage{placeins}


output:
  pdf_document:
    extra_dependencies: ["float"]
---

```{r libraries, include=FALSE}


#rm(list = ls())
library(bigrquery)
library(foreach)
library(stringr)
#library(plyr)
#library(expss) ###to add labels
library(epiDisplay) ##recommended applied here crosstable, tab1
library(gmodels) ##recommended
library(magrittr)
library(arsenal)
library(gtsummary)
library(rio)
library(knitr)
library(kableExtra)
library(ggplot2)
library(gridExtra)
library(scales)
#library(gt)
#install(tinytex)
library(tinytex)
library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(reshape)  ###to work on transition from long to wide or wide to long data
library(listr) ###to work on a list of vector, files or..
library(sqldf) ##sql
library(lubridate) ###date time
library(stringr) ###to work on patterns, charaters
library(janitor)


options(tinytex.verbose = TRUE)

bq_auth()


```


```{r BQ_Data_Pull, include=FALSE}

demo <- "SELECT Connect_ID, token,
d_827220437, state_d_253532712, state_d_934298480, state_d_684926335, state_d_849518448, state_d_119643471, 
state_d_706256705, state_d_435027713, d_949302066, d_536735468, d_663265240, d_976570371, d_100767870, 
d_878865966, d_684635302, d_167958071, state_d_811353546, d_230663853, d_558435199, d_919254129, d_699625233,
state_d_158291096
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` 
where state_d_811353546 is not null"
demo_table <- bq_project_query(project, demo)
letter_cont <- bq_table_download(demo_table, bigint = "integer64")


letter_cont <- letter_cont %>% 
  mutate(site = case_when(d_827220437 == '472940358' ~ "Baylor Scott and White Health",
                          d_827220437 == '531629870' ~ "HealthPartners",
                          d_827220437 == '548392715' ~ "Henry Ford Health System",
                          d_827220437 == '303349821' ~ "Marshfield Clinic Health System",
                          d_827220437 == '657167265' ~ "Sanford Health",
                          d_827220437 == '809703864' ~ "University of Chicago Medicine",
                          d_827220437 == '125001209' ~ "Kaiser Permanente Colorado",
                          d_827220437 == '327912200' ~ "Kaiser Permanente Georgia",
                          d_827220437 == '452412599' ~ "Kaiser Permanente Northwest",
                          d_827220437 == '300267574' ~ "Kaiser Permanente Hawaii"),
       age = case_when(state_d_934298480 == "713781738"~ "30-34",
                         state_d_934298480 == '631272782' ~ "35-39",
                         state_d_934298480 == '124276120' ~ "40-45",
                         state_d_934298480 == '450985724' ~ "46-50",
                         state_d_934298480 == '363147933' ~ "51-55",
                         state_d_934298480 == '636706443' ~ "56-60",
                         state_d_934298480 == '771230670' ~ "61-65",
                         state_d_934298480 == '722846087' ~ "66-70"),
       race = case_when(state_d_684926335 == '635279662' |state_d_849518448 == '768826601' | state_d_119643471 == '635279662' | 
                          state_d_253532712=='723775357' ~ "White, Non-Hispanic" , 
                        state_d_684926335 %in% c('232334767', '401335456') |
                          state_d_849518448 == '181769837' |
                          state_d_253532712 %in% c('153444133','572474909','308427446','211228524','277568192','611398522','181769837') |
                          state_d_119643471 %in% c( '232334767','211228524','308427446','432722256','232663805','785578696','200929978','490725843','965998904') ~ "Other",
                        state_d_684926335 == '178420302'  | 
                          state_d_849518448 == '178420302' | 
                          state_d_253532712 == '178420302' |
                          state_d_119643471  %in% c( '986445321','746038746','178420302') |
                          (is.na(state_d_119643471) & d_827220437 == '657167265') ~ "Unknown"),
       sex = case_when(state_d_706256705 == '536341288' | state_d_435027713 == '536341288' ~ "Female",
                       state_d_706256705 == '654207589' | state_d_435027713 == '654207589' ~ "Male",
                       #state_d_706256705 == '830573274' ~ "Intersex or Other", # too small of a count for now, need to combine with unknown 
                       state_d_706256705 == '830573274' | state_d_706256705 == '178420302' | state_d_435027713 == '178420302' ~ "Unknown/Other"),
       basesvcomplt = case_when(d_949302066!= '231311385' ~ "None",
                                d_949302066 == '231311385' & d_536735468 == '231311385' & 
                                  d_663265240 == '231311385' & d_976570371 == '231311385' ~ "All",
                                d_949302066 == '231311385' & d_536735468 != '231311385' & 
                                  d_663265240 != '231311385' & d_976570371 != '231311385' ~ "BOH only",
                                TRUE ~ "2 or 3 Sections"),
       completion = case_when(d_100767870=="353358909" & 
                                (d_878865966=="353358909" | d_684635302=="353358909" | d_167958071=="353358909") ~ "Completed Survey and Sample(s)",
                              d_100767870=="353358909"  ~ "Completed Survey, No Sample(s)",
                              (d_878865966=="353358909" | d_684635302=="353358909" | d_167958071=="353358909") ~ "Completed Sample(s), No Survey",
                              TRUE ~ "Completed Neither"),
       collections = case_when((d_878865966=="353358909" | d_684635302=="353358909" | d_167958071=="353358909") ~ "Collected",
                               TRUE ~ "Not Collected"),
       letter = case_when(state_d_811353546=="711757828" ~ "Join Connect today to help prevent cancer tomorrow",
                          state_d_811353546=="943427992" ~ "Receive a $25 payment for participating",
                          state_d_811353546=="648219696" ~ "Join to honor the memory of those lost to cancer",
                          state_d_811353546=="798915634" ~ "Join others in your community who are changing the future of cancer prevention",
                          state_d_811353546=="896010519" ~ "You can easily do most study tasks on your own"),
       signed_in= case_when(d_230663853=="353358909" ~ "Yes",
                            TRUE ~ "No"),
       hippaa = case_when(d_558435199=="353358909" ~ "Yes",
                          TRUE ~ "No"),
       consent= case_when(d_919254129=="353358909" ~ "Yes",
                          TRUE ~ "No"),
       user_profile = case_when(d_699625233=="353358909" ~ "Yes",
                                TRUE ~ "No"),
       refusal = case_when(state_d_158291096=="353358909" ~ "Active Refusal",
                           state_d_158291096=="104430631" & signed_in=="No" ~ "Passive refusal (no refusal or account creation)",
                           TRUE ~ "No Refusal"))
       
```



```{r newTable1, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

compare_Age <- letter_cont %>%
    tbl_cross(
      row = age,
      col = letter,
      label = list(letter ~ "Letter Variant", age ~ "Age"),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total"
    ) %>% 
  add_p()

compare_Race <- letter_cont %>%
    tbl_cross(
      row = race,
      col = letter,
      label = list(letter ~ "Letter Variant", race ~ "Race"),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total"
    ) %>% 
  add_p()

compare_Sex <- letter_cont %>%
    tbl_cross(
      row = sex,
      col = letter,
      label = list(letter ~ "Letter Variant", sex ~ "Sex"),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total"
    ) %>% 
  add_p()


compare_Site <- letter_cont %>%
    tbl_cross(
      row = site,
      col = letter,
      label = list(letter ~ "Letter Variant", site ~ "Site"),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total"
    ) %>% 
  add_p()




# Convert tbl_cross objects to data frames
df_Age <- as.data.frame(compare_Age)
df_Race <- as.data.frame(compare_Race)
df_Sex <- as.data.frame(compare_Sex)
df_Site <- as.data.frame(compare_Site)

# Rename the blank column to 'Temp_Demographic'
colnames(df_Age)[1] <- "Temp_Demographic"
colnames(df_Race)[1] <- "Temp_Demographic"
colnames(df_Sex)[1] <- "Temp_Demographic"
colnames(df_Site)[1] <- "Temp_Demographic"

# Add a demographic column to each data frame
df_Age <- df_Age %>% mutate(Demographic = "Age") %>% select(Demographic, everything())
df_Race <- df_Race %>% mutate(Demographic = "Race") %>% select(Demographic, everything())
df_Sex <- df_Sex %>% mutate(Demographic = "Sex") %>% select(Demographic, everything())
df_Site <- df_Site %>% mutate(Demographic = "Site") %>% select(Demographic, everything())

# Combine all data frames into one
combined_df <- bind_rows(df_Site, df_Race, df_Sex, df_Age)

# Replace NA values with blank spaces
combined_df[is.na(combined_df)] <- ""

# Check the result
combined_df <- combined_df[, c(2:9)]

colnames(combined_df)[1] <- "Total"



```


# Table 1: Randomization of letter content by demographic factors, Connect for Cancer Prevention Study, eligible individuals invited X/XX/2024 to XXX/XX/2024

```{r knitTable1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
knitr::kable(combined_df , 
             #caption='Table 1: How recruits learned about  the study among participants in the Connect for Cancer Prevention cohort', 
             row.names=FALSE,align=c("l","c","c","c","c","c","c","c"),
             #col.names=c("Demographics", "Digital","Traditional","Both","Total Consented \n Recruits"), #escape=F, #linebreak(
             booktabs = TRUE) %>%  
  landscape() %>% 
  add_indent(c(2:7, 9:12, 14:17, 19:24))  %>% 
  kable_styling(latex_options = "scale_down", full_width= FALSE)
  
```

\FloatBarrier


```{r table2, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#Indiviudal workflows
cumm_counts <- letter_cont %>% 
  mutate('Step 1: MyConnect Account/ Signed In' = d_230663853 == '353358909',
         'Step 2: User Profile' = d_699625233 == '353358909',
         'Step 3: Consent & HIPAA' = (d_919254129 == '353358909' & d_558435199=="353358909") ,
          "Biospecimen Donation" = collections == "Collected", 
         'Some Survey Modules' = (basesvcomplt=="BOH only" | basesvcomplt=="2 or 3 Sections"),
         'All Survey Modules' = basesvcomplt=="All",
         'Biospecimen Donation & All Survey Modules' =  completion=="Completed Survey and Sample(s)")


# Will need to create a separate total column, since total recruits will be much larger then the sums of these columns
total_participants_per_letter <- cumm_counts %>%
  group_by(letter) %>%
  tally()

#total_participants_per_letter[6,] <- c("Total", sum(total_participants_per_letter$n))

# long format to count instances of each independently
long_recr <- cumm_counts %>%
  select(letter, 'Step 1: MyConnect Account/ Signed In', 'Step 2: User Profile', 'Step 3: Consent & HIPAA',"Biospecimen Donation", 
         'Some Survey Modules','All Survey Modules','Biospecimen Donation & All Survey Modules') %>%
  pivot_longer(cols = 'Step 1: MyConnect Account/ Signed In':'Biospecimen Donation & All Survey Modules', names_to = "cumm_workflow", values_to = "in_category") %>%
  filter(in_category) %>%
  select(-in_category)


long_recr$cumm_workflow <- factor(long_recr$cumm_workflow, levels = c('Step 1: MyConnect Account/ Signed In', 'Step 2: User Profile', 
                                                                      'Step 3: Consent & HIPAA',"Biospecimen Donation", 
                                                                      'Some Survey Modules','All Survey Modules','Biospecimen Donation & All Survey Modules'))



workflow2 <- long_recr %>%
  tbl_cross(
    row = letter,
    col = cumm_workflow,
    label = list(cumm_workflow ~ " ", letter ~ " "),
    percent = "row",
    digits = c(0, 2),
    missing = "ifany",
    #missing_text = "Missing",
    margin_text = "Total Invited"
  ) #%>%  add_p()

workflow2[["table_body"]]$stat_1 <- sapply(strsplit(workflow2[["table_body"]]$stat_1," "),"[",1)
workflow2[["table_body"]]$stat_2 <- sapply(strsplit(workflow2[["table_body"]]$stat_2," "),"[",1)
workflow2[["table_body"]]$stat_3 <- sapply(strsplit(workflow2[["table_body"]]$stat_3," "),"[",1)
workflow2[["table_body"]]$stat_4 <- sapply(strsplit(workflow2[["table_body"]]$stat_4," "),"[",1)
workflow2[["table_body"]]$stat_5 <- sapply(strsplit(workflow2[["table_body"]]$stat_5," "),"[",1)
workflow2[["table_body"]]$stat_6 <- sapply(strsplit(workflow2[["table_body"]]$stat_6," "),"[",1)
workflow2[["table_body"]]$stat_7 <- sapply(strsplit(workflow2[["table_body"]]$stat_7," "),"[",1)
workflow2[["table_body"]]$stat_0 <- sapply(strsplit(workflow2[["table_body"]]$stat_0," "),"[",1)



workflow2_df <- as.data.frame(workflow2$table_body)[c(2:7), c(5:12)]

# Add back the total row
workflow2_df <- workflow2_df %>%
  left_join(total_participants_per_letter, by = c("label" = "letter"))

workflow2_df[nrow( workflow2_df), ncol( workflow2_df)] <- sum( workflow2_df$n, na.rm = TRUE)


colnames(workflow2_df) <- c('Letter', 'Step 1: MyConnect Account/ Signed In', 'Step 2: User Profile', 'Step 3: Consent & HIPAA',
                            "Biospecimen Donation",'Some Survey Modules','All Survey Modules','Biospecimen Donation & All Survey Modules', "Total Invited")



```





# Table 2a: Completion of recruitment workflow steps and study activities by letter type, Connect for Cancer Prevention Study, eligible individuals invited X/XX/2024 to XXX/XX/2024

```{r knitTable2, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}


knitr::kable(workflow2 , 
             #caption='Table 1. Completion of Initial Surveys by Site', 
             row.names=FALSE,align=c("l","c","c","c","c","c","c","c","c","c"),
             #col.names=c("Site", "All Completed", "One or More Not Completed", "Total"),
             booktabs = TRUE) %>%  
  add_indent(seq(1, nrow(workflow2) - 1))  %>% 
  kable_styling(latex_options = c("scale_down","hold_position"))

```



\FloatBarrier

# Table 2b: Connect enrollment milestones by message Among those who have Consented

```{r Table2b, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

Refusal_tables <- letter_cont %>%
  filter(refusal!="No Refusal") %>% 
    tbl_cross(
      col = refusal,
      row = letter,
      label = list(letter ~ " ", refusal ~ " "),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total"
    ) %>%  add_p()

Refusal_tables 

## Doing this makes the other lines NA under the one p-value
# knitr::kable(Refusal_tables, 
#              row.names=FALSE,align=c("l","c","c","c","c","c","c","c","c"),
#              booktabs = TRUE) %>%  
#   landscape() %>% 
#   kable_styling(latex_options = "scale_down", full_width= FALSE)
  
```






```{r Table1_Repeated_Consented, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

### This same table as Table 1 needs to be repeated four times
## 1. Of those who consented
## 2. Of those who donated biospecimens
## 3. Of those who completed all surveys
## 4. Of those who completed biospecimens and surveys
## 5. Of those who opted out of Connect


## Can't get the looping right so I'll have to code this5 different times


const <- letter_cont %>%  filter(consent=="Yes")
bio_comp <- letter_cont %>%  filter(collections=="Collected")
survey_comp <- letter_cont %>%  filter(basesvcomplt="All")
both_comp <- letter_cont %>%  filter(completion=="Completed Survey and Sample(s)")
refused <- letter_cont %>%  filter(refusal=="Active Refusal")





#dfs <- c(letter_cont, bio_comp, survey_comp, both_comp, refusal)

#for (df in dfs){

compare_Age <- const %>%
    tbl_cross(
      row = age,
      col = letter,
      label = list(letter ~ "Letter Variant", age ~ "Age"),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total"
    ) %>% 
  add_p()

compare_Race <- const %>%
    tbl_cross(
      row = race,
      col = letter,
      label = list(letter ~ "Letter Variant", race ~ "Race"),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total"
    ) %>% 
  add_p()

compare_Sex <- const %>%
    tbl_cross(
      row = sex,
      col = letter,
      label = list(letter ~ "Letter Variant", sex ~ "Sex"),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total"
    ) %>% 
  add_p()


compare_Site <- const %>%
    tbl_cross(
      row = site,
      col = letter,
      label = list(letter ~ "Letter Variant", site ~ "Site"),
      percent = "row",
      digits = c(0, 2),
      missing = "no",
      margin_text = "Total"
    ) %>% 
  add_p()




# Convert tbl_cross objects to data frames
df_Age <- as.data.frame(compare_Age)
df_Race <- as.data.frame(compare_Race)
df_Sex <- as.data.frame(compare_Sex)
df_Site <- as.data.frame(compare_Site)

# Rename the blank column to 'Temp_Demographic'
colnames(df_Age)[1] <- "Temp_Demographic"
colnames(df_Race)[1] <- "Temp_Demographic"
colnames(df_Sex)[1] <- "Temp_Demographic"
colnames(df_Site)[1] <- "Temp_Demographic"

# Add a demographic column to each data frame
df_Age <- df_Age %>% mutate(Demographic = "Age") %>% select(Demographic, everything())
df_Race <- df_Race %>% mutate(Demographic = "Race") %>% select(Demographic, everything())
df_Sex <- df_Sex %>% mutate(Demographic = "Sex") %>% select(Demographic, everything())
df_Site <- df_Site %>% mutate(Demographic = "Site") %>% select(Demographic, everything())

# Combine all data frames into one
combined_df_consented <- bind_rows(df_Site, df_Race, df_Sex, df_Age)

# Replace NA values with blank spaces
combined_df_consented[is.na(combined_df_consented)] <- ""

# Check the result
combined_df_consented <- combined_df_consented[, c(2:9)]

colnames(combined_df_consented)[1] <- "Total"

#}



```

\FloatBarrier
# Table 3a: Connect enrollment milestones by message Among those who have Consented

```{r knitTable1, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
knitr::kable(combined_df_consented, 
             row.names=FALSE,align=c("l","c","c","c","c","c","c","c"),
             booktabs = TRUE) %>%  
  landscape() %>% 
  add_indent(c(2:7, 9:12, 14:17, 19:24))  %>% ## add indents 
  kable_styling(latex_options = "scale_down", full_width= FALSE, font_size=6)
  
```






