---
title: "Module 1 Custom QC Rule Errors"
author: "Kelsey Dowling"
date: "`r Sys.Date()`"
header-includes:  
    \usepackage{placeins}


output:
  pdf_document:
    extra_dependencies: ["float"]
    toc: false
    keep_tex: yes
    fig_caption: true
---

```{r library, include=FALSE}
#rm(list = ls())


#update.packages("tinytex")
#require(devtools)
#install_version("ggplot2", version = "0.9.1", repos = "http://cran.us.r-project.org")
#tinytex::install_tinytex(version = "2020.10")
#tinytex::reinstall_tinytex(repository = "illinois")



library(bigrquery)
library(foreach)
library(stringr)
#library(plyr)
#library(expss) ###to add labels
library(epiDisplay) ##recommended applied here crosstable, tab1
library(gmodels) ##recommended
library(magrittr)
library(arsenal)
library(gtsummary)
library(rio)


library(ggplot2)
library(gridExtra)
library(scales)
library(gt)
#install(tinytex)
library(tinytex)
library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(reshape)  ###to work on transition from long to wide or wide to long data
library(listr) ###to work on a list of vector, files or..
library(sqldf) ##sql
library(lubridate) ###date time
library(stringr) ###to work on patterns, characters
library(kableExtra)


options(tinytex.verbose = TRUE)

bq_auth()
```



```{r M1merge, include=FALSE}
dictionary <- rio::import("https://episphere.github.io/conceptGithubActions/aggregate.json",format = "json")
dd <- dplyr::bind_rows(dictionary,.id="CID")
dd <-rbindlist(dictionary,fill=TRUE,use.names=TRUE,idcol="CID")
dd$`Variable Label`[is.na(dd$`Variable Label`)] <- replace_na(dd$'Variable Name')

dd <- as.data.frame.matrix(do.call("rbind",dictionary)) 
dd$CID <- rownames(dd)
#https://shaivyakodan.medium.com/7-useful-r-packages-for-analysis-7f60d28dca98
devtools::install_github("tidyverse/reprex")

project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" ##project and billing should be consistent
##517311251 Date/time Status of Completion of Background and Overall Health                         SrvBOH_TmComplete_v1r0
##949302066 Flag for Baseline Module Background and Overall Health                        SrvBOH_BaseStatus_v1r0
recr_M1 <- bq_project_query(project, query="SELECT token,Connect_ID, d_821247024, d_914594314,  d_827220437,d_512820379,
                            d_949302066 , d_517311251  FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` WHERE  d_821247024='197316935' and d_949302066 ='231311385'")
recr_m1 <- bq_table_download(recr_M1,bigint = "integer64")
cnames <- names(recr_m1)
# Check that it doesn't match any non-number
numbers_only <- function(x) !grepl("\\D", x)
# to check variables in recr_noinact_wl1
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(recr_m1,varname)
  recr_m1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}

sql_M1_1 <- bq_project_query(project, query="SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v1_JP` where Connect_ID is not null")
sql_M1_2 <- bq_project_query(project, query="SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2_JP` where Connect_ID is not null")


M1_V1 <- bq_table_download(sql_M1_1,bigint = "integer64") #1436 #1436 vars: 1507 01112023 
M1_V2 <- bq_table_download(sql_M1_2,bigint = "integer64") #2333 #3033 01112023 var:1531 #6339 obs 1893 vars 05022023

mod1_v1 <- M1_V1
cnames <- names(M1_V1)
###to check variables and convert to numeric
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(mod1_v1,varname)
  mod1_v1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}
mod1_v2 <- M1_V2
cnames <- names(M1_V2)
###to check variables and convert to numeric
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(mod1_v2,varname)
  mod1_v2[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}

M1_V1.var <- colnames(M1_V1)
M1_V2.var <- colnames(M1_V2)
var.matched <- M1_V1.var[which(M1_V1.var %in% M1_V2.var)]
length(var.matched)  #1275 #1278 vars 01112023 #1348 vars 05022023

V1_only_vars <- colnames(M1_V1)[colnames(M1_V1) %nin% var.matched] #232 #229 01112023 #159 05022023
V2_only_vars <- colnames(M1_V2)[colnames(M1_V2) %nin% var.matched] #253 #253 01112023 #545 05022023

length(M1_V1$Connect_ID[M1_V1$Connect_ID %in% M1_V2$Connect_ID])
#[1] 59 with the completion of two versions of Module1 
#[1] 62 with completing both versions of M1 ###double checked 03/28/2023
#68 double checked 05/02/2023

common.IDs <- M1_V1$Connect_ID[M1_V1$Connect_ID %in% M1_V2$Connect_ID]
M1_V1_common <- mod1_v1[,var.matched]

M1_V2_common <- mod1_v2[,var.matched]
M1_V1_common$version <- 1
M1_V2_common$version <- 2

##to check the completion of M1 among these duplicates
partM1_dups <- recr_m1[which(recr_m1$Connect_ID %in% common.IDs),]
table(partM1_dups$d_949302066)

M1_common  <- rbind(M1_V1_common, M1_V2_common) #including 136 duplicates (version 1 and version 2) from 68 participants 05022023
#M1_response <- matrix(data=NA, nrow=118, ncol=967)

m1_v1_only <- mod1_v1[,c("Connect_ID", V1_only_vars)] #230 vars 03282023 #160 vars 05/02/2023
m1_v2_only <- mod1_v2[,c("Connect_ID", V2_only_vars)] #255 vars 03282023 #546 vars 05/02/2023
m1_v1_only$version <- 1
m1_v2_only$version <- 2
#for (i in 1:length)
##to check the completion in each version
length(recr_m1$Connect_ID[which(recr_m1$Connect_ID %in% m1_v1_only$Connect_ID & recr_m1$d_949302066 ==231311385)]) #1364 03282023 # 1370 05022023
length(recr_m1$Connect_ID[which(recr_m1$Connect_ID %in% m1_v2_only$Connect_ID & recr_m1$d_949302066 ==231311385)]) #4870 03282023 # 5731 05022023

#library(janitor)

m1_common <- rbind(M1_V1_common,M1_V2_common)
m1_common_v1 <- base::merge(m1_common, m1_v1_only, by=c("Connect_ID","version"),all.x=TRUE)
m1_combined_v1v2 <- base::merge(m1_common_v1,m1_v2_only,by=c("Connect_ID","version"),all.x=TRUE)
m1_complete <- m1_combined_v1v2[which(m1_combined_v1v2$Connect_ID %in% recr_m1$Connect_ID[which(recr_m1$d_949302066 ==231311385 )]),] #7289 including duplicates 05022023

m1_complete <- m1_complete %>% arrange(desc(version)) 


m1_complete_nodup <- m1_complete[!duplicated(m1_complete$Connect_ID),] 
table(m1_complete_nodup$version)



parts <- "SELECT Connect_ID, token, D_512820379, D_471593703, state_d_934298480, D_230663853,
D_335767902, D_982402227, D_919254129, D_699625233, D_564964481, D_795827569, D_544150384,
D_371067537, D_430551721, D_821247024, D_914594314,  state_d_725929722, d_827220437, 
D_949302066 , D_517311251, D_205553981, D_117249500, d_430551721, d_517311251, d_544150384, d_564964481, d_117249500 FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` 
where Connect_ID IS NOT NULL and (d_512820379='486306141' OR d_512820379='854703046') and (D_919254129='353358909') and (D_699625233='353358909') and (d_949302066='231311385')"
parts_table <- bq_project_query(project, parts)
parts_data <- bq_table_download(parts_table, bigint = "integer64")

parts_data$Connect_ID <- as.numeric(parts_data$Connect_ID) ###need to convert type- m1... is double and parts is character

module1= left_join(m1_complete_nodup, parts_data, by="Connect_ID") 
dim(module1)





module1 <-
  module1 %>%  mutate(
    Site = case_when(
      d_827220437 == 125001209 ~ "Kaiser Permanente Colorado",
      d_827220437 == 181769837 ~ "Other",
      d_827220437 == 300267574 ~ "Kaiser Permanente Hawaii",
      d_827220437 == 303349821 ~ "Marshfield Clinic Health System",
      d_827220437 == 327912200 ~ "Kaiser Permanente Georgia",
      d_827220437 == 452412599 ~ "Kaiser Permanente Northwest",
      d_827220437 == 517700004 ~ "National Cancer Institute",
      d_827220437 == 531629870 ~ "HealthPartners",
      d_827220437 == 548392715 ~ "Henry Ford Health System",
      d_827220437 == 657167265 ~ "Sanford Health",
      d_827220437 == 809703864 ~ "University of Chicago Medicine"
    )
  )

```




### 1. If Module 1 isn't completed, no other module can be started or completed. Note this table is very wide, so if there are no errors found all that will be diplayed is "No errors".
```{r Mod1NS, echo=FALSE, warning=FALSE, message=FALSE}


Mod1NS <- module1 %>%  filter(d_949302066!='231311385' & #mod 1 not done
                                 (d_536735468!=972455046 | d_976570371!=972455046 | d_663265240!=972455046 )) %>%  #mod2-4 started or submitted
      select(Site, Connect_ID, d_949302066, d_536735468 ,d_976570371 , d_663265240 ) %>%  sort_by(Site)

colnames(Mod1NS) <- c("Site", "Connect ID", "SrvBOH_BaseStatus_v1r0", "SrvMRE_BaseStatus_v1r0", "SrvSAS_BaseStatus_v1r0", "SrvLAW_BaseStatus_v1r0")


if (nrow(Mod1NS) == 0) {
  cat("No errors\n")
} else {
  knitr::kable(Mod1NS) %>% kable_styling(latex_options = "scale_down")
}
```


\FloatBarrier
### 2. If 'none of the above' is selected for cardiovascular conditions, no other cardiovascular condition can be chosen. Note this table is very wide, so if there are no errors found all that will be diplayed is "No errors".

```{r cardio_none, echo=FALSE, warning=FALSE, message=FALSE}


cardio_none <- module1 %>%  filter(D_167101091_D_535003378 == 1 & rowSums(select(., starts_with("D_167101091_")) == 1) > 1) %>%
      select(Site, Connect_ID, starts_with("D_167101091_") ) %>%  sort_by(Site)


#knitr::kable(cardio_none)  %>% kable_styling(latex_options = "scale_down")

if (nrow(cardio_none) == 0) {
  cat("No errors\n")
} else {
  knitr::kable(cardio_none) %>% kable_styling(latex_options = "scale_down")
}

```


\FloatBarrier
### 3. If 'none of the above' is selected for digestive conditions, no other digestive condition can be chosen. Note this table is very wide, so if there are no errors found all that will be diplayed is "No errors".

```{r digest_none, echo=FALSE, warning=FALSE, message=FALSE}


digest_none <- module1 %>%  filter(D_180961306_D_535003378 == 1 & rowSums(select(., starts_with("D_180961306_")) == 1) > 1) %>%
      select(Site, Connect_ID, starts_with("D_180961306_") ) %>%  sort_by(Site)



if (nrow(digest_none) == 0) {
  cat("No errors\n")
} else {
  knitr::kable(digest_none) %>% kable_styling(latex_options = "scale_down")
}

```


\FloatBarrier
### 4. If 'none of the above' is selected for STDs and Other Infectious conditions, no other STD or condition can be chosen. Note this table is very wide, so if there are no errors found all that will be diplayed is "No errors".

```{r std_none, echo=FALSE, warning=FALSE, message=FALSE}


std_none <- module1 %>%  filter(D_874709643_D_535003378 == 1 & rowSums(select(., starts_with("D_874709643_")) == 1) > 1) %>%
      select(Site, Connect_ID, starts_with("D_874709643_") ) %>%  sort_by(Site)



if (nrow(std_none) == 0) {
  cat("No errors\n")
} else {
  knitr::kable(std_none) %>% kable_styling(latex_options = "scale_down")
}

```


\FloatBarrier
### 5. If 'none of the above' is selected for urinary conditions, no other urinary condition can be chosen. Note this table is very wide, so if there are no errors found all that will be diplayed is "No errors".

```{r urin_none, echo=FALSE, warning=FALSE, message=FALSE}


urin_none <- module1 %>%  filter(D_725626004_D_535003378 == 1 & rowSums(select(., starts_with("D_725626004_")) == 1) > 1) %>%
      select(Site, Connect_ID, starts_with("D_725626004_") ) %>%  sort_by(Site)



if (nrow(urin_none) == 0) {
  cat("No errors\n")
} else {
  knitr::kable(urin_none) %>% kable_styling(latex_options = "scale_down")
}

```


\FloatBarrier
### 6. If 'none of the above' is selected for surgerical prodedures, no other surgeries can be chosen. Note this table is very wide, so if there are no errors found all that will be diplayed is "No errors".

```{r surgery_none, echo=FALSE, warning=FALSE, message=FALSE}


surgery_none <- module1 %>%  filter(D_624179836_D_535003378 == 1 & rowSums(select(., starts_with("D_624179836_")) == 1) > 1) %>%
      select(Site, Connect_ID, starts_with("D_624179836_") ) %>%  sort_by(Site)



if (nrow(surgery_none) == 0) {
  cat("No errors\n")
} else {
  knitr::kable(surgery_none) %>% kable_styling(latex_options = "scale_down")
}

```


\FloatBarrier
### 7. If 'none of the above' is selected for breast surgeries, no other breast surgeries can be chosen. Note this table is very wide, so if there are no errors found all that will be diplayed is "No errors".

```{r brst_surg_none, echo=FALSE, warning=FALSE, message=FALSE}


brst_surg_none <- module1 %>%  filter(D_517307064_D_517307064_D_535003378 == 1 & rowSums(select(., starts_with("D_517307064_D_517307064_")) == 1) > 1) %>%
      select(Site, Connect_ID, starts_with("D_517307064_D_517307064_") ) %>%  sort_by(Site)



if (nrow(brst_surg_none) == 0) {
  cat("No errors\n")
} else {
  knitr::kable(brst_surg_none) %>% kable_styling(latex_options = "scale_down")
}

```

\FloatBarrier
### 8. Alternative contact mobile number (SrvBOH_AltContCell_v1r0) must be numeric and 10 digits
```{r alt_mb_phone, echo=FALSE, warning=FALSE, message=FALSE}

module1 <- module1   %>% mutate(mobile_num= gsub("[^0-9]", "", D_285718391_D_286149234))

alt_mobile <- module1 %>%  mutate(mobile= ifelse(nchar(module1$mobile_num)==11 & str_sub(module1$mobile_num,1,1)==1, str_sub(module1$mobile_num,2,11), module1$mobile_num)) 
alt_mb <- alt_mobile %>% filter(!is.na(alt_mobile$mobile) & nchar(alt_mobile$mobile)!=10) %>% 
  select(Site, Connect_ID, mobile ) %>%  sort_by(Site)


colnames(alt_mb) <- c("Site", "Connect ID", "SrvBOH_AltContCell_v1r0")
knitr::kable(alt_mb)  %>% kable_styling(latex_options = "HOLD_position")

```


\FloatBarrier
### 9. Alternative contact home number must be numeric and 10 digits
```{r alt_home_phone, echo=FALSE, warning=FALSE, message=FALSE}


module1 <- module1   %>% mutate(home_num= gsub("[^0-9]", "", D_285718391_D_318130543))

alt_home <- module1 %>%  mutate(home= ifelse(nchar(module1$home_num)==11 & str_sub(module1$home_num,1,1)==1, str_sub(module1$home_num,2,11), module1$home_num)) 
alt_home <- alt_home %>% filter(!is.na(alt_home$home) & nchar(alt_home$home)!=10) %>% 
  select(Site, Connect_ID, home ) %>%  sort_by(Site)


colnames(alt_home) <- c("Site", "Connect ID", "SrvBOH_AltContCell_v1r0")
knitr::kable(alt_home)  %>% kable_styling(latex_options = "HOLD_position")

```


\FloatBarrier
### 10. Alternative ZIP code should be no more than 9 digits; 5 with primary ZIP code and 9 if full ZIP code given 
```{r zip, echo=FALSE, warning=FALSE, message=FALSE}



module1 <- module1   %>% mutate(zip_num= gsub("[^0-9]", "", D_857915436_D_379899229))
zipcode <- module1 %>% filter(!is.na(module1$zip_num) & (nchar(module1$zip_num)!=5 | nchar(module1$zip_num)!=9)) %>% 
  select(Site, Connect_ID, zip_num) %>%  sort_by(Site)

colnames(zipcode) <- c("Site", "Connect ID", "ZIP")

#table(nchar(zipcode$ZIP))

zipcodes <- zipcode %>%  filter(nchar(zipcode$ZIP)!=0 & nchar(zipcode$ZIP)!=5 & nchar(zipcode$ZIP)!=9)

knitr::kable(zipcodes)  %>% kable_styling(latex_options = "HOLD_position")

```



