---
title: "Risk prediction models using baseline survey data"
subtitle: "Univariate distributions of key variables"
author: "Kelsey Sanchez"
date: "`r Sys.Date()`"
header-includes:  
  \usepackage[labelformat=empty]{caption}
  \usepackage{placeins}
output:
  pdf_document:
    extra_dependencies: ["float"]
---

```{r libraries, include=FALSE}


#  pdf-engine: xelatex
#tinytex::install_tinytex()

library(bigrquery)
library(epiDisplay) ##recommended applied here crosstable, tab1
library(gmodels) ##recommended
library(arsenal)
library(gtsummary)
library(rio)



library(ggplot2)
library(gridExtra)
library(scales)
library(gt)
library(tinytex)
library(data.table) ###to write or read and data management 
library(tidyverse) ###for data management
library(dplyr) ###data management
library(lubridate) ###date time
library(stringr) ###to work on patterns, charaters
library(knitr)
library(kableExtra)
options(tinytex.verbose = TRUE)

bq_auth()
```


```{r merge1, include=FALSE, warning=FALSE}

## MERGE MOD1V1, MOD1V2


dictionary <- rio::import("https://episphere.github.io/conceptGithubActions/aggregate.json",format = "json")
dd <- dplyr::bind_rows(dictionary,.id="CID")
dd <-rbindlist(dictionary,fill=TRUE,use.names=TRUE,idcol="CID")
dd$`Variable Label`[is.na(dd$`Variable Label`)] <- replace_na(dd$'Variable Name')

dd <- as.data.frame.matrix(do.call("rbind",dictionary)) 
dd$CID <- rownames(dd)
#https://shaivyakodan.medium.com/7-useful-r-packages-for-analysis-7f60d28dca98
#devtools::install_github("tidyverse/reprex")

project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" ##project and billing should be consistent
##517311251 Date/time Status of Completion of Background and Overall Health                         SrvBOH_TmComplete_v1r0
##949302066 Flag for Baseline Module Background and Overall Health                        SrvBOH_BaseStatus_v1r0
recr_M1 <- bq_project_query(project, query="SELECT token,Connect_ID, d_821247024, d_914594314,  d_827220437,d_512820379,
                            d_949302066 , d_517311251  FROM  `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` WHERE  d_821247024='197316935'")
recr_m1 <- bq_table_download(recr_M1,bigint = "integer64",n_max = Inf, page_size = 10000)
cnames <- names(recr_m1)
# Check that it doesn't match any non-number
numbers_only <- function(x) !grepl("\\D", x)
# to check variables in recr_noinact_wl1
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(recr_m1,varname)
  recr_m1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}

sql_M1_1 <- bq_project_query(project, query="SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v1_JP` where Connect_ID is not null")
sql_M1_2 <- bq_project_query(project, query="SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module1_v2_JP` where Connect_ID is not null")


M1_V1 <- bq_table_download(sql_M1_1,bigint = "integer64") #1436 #1436 vars: 1507 01112023 
M1_V2 <- bq_table_download(sql_M1_2,bigint = "integer64") #2333 #3033 01112023 var:1531 #6339 obs 1893 vars 05022023

mod1_v1 <- M1_V1
cnames <- names(M1_V1)
###to check variables and convert to numeric
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(mod1_v1,varname)
  mod1_v1[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}
mod1_v2 <- M1_V2
cnames <- names(M1_V2)
###to check variables and convert to numeric
for (i in 1: length(cnames)){
  varname <- cnames[i]
  var<-pull(mod1_v2,varname)
  mod1_v2[,cnames[i]] <- ifelse(numbers_only(var), as.numeric(as.character(var)), var)
}

M1_V1.var <- colnames(M1_V1)
M1_V2.var <- colnames(M1_V2)
var.matched <- M1_V1.var[which(M1_V1.var %in% M1_V2.var)]
length(var.matched)  #1275 #1278 vars 01112023 #1348 vars 05022023

V1_only_vars <- colnames(M1_V1)[colnames(M1_V1) %nin% var.matched] #232 #229 01112023 #159 05022023
V2_only_vars <- colnames(M1_V2)[colnames(M1_V2) %nin% var.matched] #253 #253 01112023 #545 05022023

length(M1_V1$Connect_ID[M1_V1$Connect_ID %in% M1_V2$Connect_ID])
#[1] 59 with the completion of two versions of Module1 
#[1] 62 with completing both versions of M1 ###double checked 03/28/2023
#68 double checked 05/02/2023

common.IDs <- M1_V1$Connect_ID[M1_V1$Connect_ID %in% M1_V2$Connect_ID]
M1_V1_common <- mod1_v1[,var.matched]

M1_V2_common <- mod1_v2[,var.matched]
M1_V1_common$version <- 1
M1_V2_common$version <- 2

##to check the completion of M1 among these duplicates
partM1_dups <- recr_m1[which(recr_m1$Connect_ID %in% common.IDs),]
table(partM1_dups$d_949302066)

M1_common  <- rbind(M1_V1_common, M1_V2_common) #including 136 duplicates (version 1 and version 2) from 68 participants 05022023
#M1_response <- matrix(data=NA, nrow=118, ncol=967)

m1_v1_only <- mod1_v1[,c("Connect_ID", V1_only_vars)] #230 vars 03282023 #160 vars 05/02/2023
m1_v2_only <- mod1_v2[,c("Connect_ID", V2_only_vars)] #255 vars 03282023 #546 vars 05/02/2023
m1_v1_only$version <- 1
m1_v2_only$version <- 2
#for (i in 1:length)
##to check the completion in each version
length(recr_m1$Connect_ID[which(recr_m1$Connect_ID %in% m1_v1_only$Connect_ID & recr_m1$d_949302066 ==231311385)]) #1364 03282023 # 1370 05022023
length(recr_m1$Connect_ID[which(recr_m1$Connect_ID %in% m1_v2_only$Connect_ID & recr_m1$d_949302066 ==231311385)]) #4870 03282023 # 5731 05022023


m1_common <- rbind(M1_V1_common,M1_V2_common)
m1_common_v1 <- base::merge(m1_common, m1_v1_only, by=c("Connect_ID","version"),all.x=TRUE)
m1_combined_v1v2 <- base::merge(m1_common_v1,m1_v2_only,by=c("Connect_ID","version"),all.x=TRUE)
m1_complete <- m1_combined_v1v2[which(m1_combined_v1v2$Connect_ID %in% recr_m1$Connect_ID[which(recr_m1$d_949302066 ==231311385 )]),] #7289 including duplicates 05022023

m1_complete <- m1_complete %>% arrange(desc(version)) 


m1_complete_nodup <- m1_complete[!duplicated(m1_complete$Connect_ID),] 
table(m1_complete_nodup$version)




# parts <- "SELECT Connect_ID, token, D_512820379, D_471593703, state_d_934298480, D_230663853,
# D_335767902, D_982402227, D_919254129, D_699625233, D_564964481, D_795827569, D_544150384,
# D_371067537, D_430551721, D_821247024, D_914594314,  state_d_725929722, d_126331570, d_536735468, 
# d_663265240, d_878865966, d_684635302, d_167958071,
# d_949302066 , D_517311251, D_205553981, D_117249500, d_976570371, d_914639140, d_311580100, d_371067537 FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP`  
# where Connect_ID IS NOT NULL"
parts <- "SELECT Connect_ID, token, d_512820379, D_471593703, state_d_934298480, D_230663853,D_335767902, D_982402227, D_919254129, D_699625233, D_564964481, D_795827569, D_544150384,D_371067537, D_430551721, D_821247024, D_914594314,  state_d_725929722, d_126331570, d_536735468, d_663265240, d_878865966, d_684635302, d_167958071, d_949302066 , D_517311251, D_205553981, D_117249500, d_976570371, d_914639140, d_311580100, d_371067537 FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` where Connect_ID IS NOT NULL and (d_512820379='486306141' OR d_512820379='854703046') and (D_919254129='353358909') and (D_699625233='353358909') and (d_949302066='231311385')" 
parts_table <- bq_project_query(project, parts)
parts_data <- bq_table_download(parts_table, bigint = "integer64",n_max = Inf, page_size = 10000)

parts_data$Connect_ID <- as.numeric(parts_data$Connect_ID)


merged= left_join(m1_complete_nodup, parts_data, by="Connect_ID") #%>%  left_join(m3_data, by="Connect_ID")
dim(merged)




data_tib_m1 <- as_tibble(merged)
#dim(base_vars)

knitr::opts_chunk$set(comment = NA)


```





```{r function1, warning=FALSE, include=FALSE}

#Boxplot
boxp_funct <- function(CID,Title, Xlab) {
  CID_SYM <- rlang::ensym(CID)
  data_tib_m1 %>% mutate(!!CID_SYM:=as.numeric(!!CID_SYM)) %>%
    filter(!is.na(!!CID_SYM)) %>%
    ggplot(aes(x=!!CID_SYM))+
    xlab(Xlab) + geom_boxplot()+  ggtitle(Title)+
    theme(axis.text.y=element_blank(),  #remove y axis labels
        axis.ticks.y=element_blank()  #remove y axis ticks
        )
}


##GT TABLE: Questions that all participants asked, update dictionary as new answer options come up
dict <- list("104430631"="No", "353358909"="Yes", "589959753"="A little shorter", "623310018"="A lot shorter", "978204320"= "Grade School(Grades 1-8)", "935502060"="Some High School, No Diploma", "404564707"= "High School Graduate or GED", "432193665"="Some College, No Degree", "890756124"="Technical or Trade School After High School", "766964355"="Associate's Degree", "875342283"="Bachelor's Degree", "598242454"="Advanced Degree", "709650750"="Biological Child", "810290359"="Adopted Child", "509607548"="Step Child","784922042"="Related to me in some other way", "288105839"=" Yes, fraternal twins", "626558982"="Yes, triplets or higher multiple birth", "178420302"="Do not Know", "536341288"="Female", "576796184"="Intersex or Other", "654207589"="Male","555374628"="Full Sibling", "871673221"="Half Sibling, Same Mother",  "198654048"="Half Sibling, Same Father", "807835037"="Other", "274062548"="More than 3 months ago", "958538953"="In the past 3 months", "317567178"="In the past month", "484055234"="In the past year",  "802197176"="More than 1 year ago", "[]"="Answered with number", "[178420302]"="Answered Don't Know", "274062548"="More than 3 months ago","958538953"="In the past 3 months",  "490796638"="Not Flexible","719954633"="Extremely Flexible","929148006"="A Little Flexible","988873962"="Somewhat Flexible", "764708931"="Very flexible","0"="No", "1"="Yes", "536341288"="Female", "218837028"="Woman (New Response)", "983318667"="Man (New Response)"  , "654207589"="Male","746038746"="Declined", "805712793"="Genderqueer","486192236"="Non-Binary", "807835037"="Other","873138103"="Transgender Woman","405267600"="Transgender Man", "220083334"="Very Feminine","541300533"="Mostly Feminine","878286618"="Somewhat Feminine","910745276"="Equally feminine and masculine","915528806"="Very masculine","265452386"="Mostly Masculine","510148951"="Somewhat Masculine","271882746"="Straight or heterosexual", "903084185"="Lesbian, gay, or homosexual", "999994434"="Bisexual")

simple_funct1 <- function(CID, Title){  
  CID_SYM <- rlang::ensym(CID)
  dt_select <- data_tib_m1 %>%  select(Connect_ID, !!CID_SYM)
  gt_yn <- dt_select  %>% dplyr::group_by(!!CID_SYM) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup() %>% dplyr::mutate(answer=recode(!!CID_SYM, !!!dict)) %>% replace_na(list(answer="Skipped this Question")) %>%  dplyr::select(answer, n, percentage)
  
  gt_yn %>%  gt::gt(rowname_col = "row_lab")  %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md(Title)) %>% 
  cols_label(n= md("**Number of Participants**"), answer = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>%  
  # summary_rows(
  #   columns = c(n,percentage),    
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = answer,
    )
  ) 
}


#GT table with one filter/skip logic
one_logic_funct <- function(CID, CID_prev, Prev_Answer, Title){  
  CID_SYM <- rlang::ensym(CID)
  CID_SYM_P <- rlang::ensym(CID_prev)
  dt_select <- data_tib_m1 %>%  filter(!!CID_SYM_P == Prev_Answer) %>%  select(Connect_ID, !!CID_SYM) 
  gt_yn <- dt_select  %>% dplyr::group_by(!!CID_SYM) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup() %>% dplyr::mutate(answer=recode(!!CID_SYM, !!!dict)) %>% replace_na(list(answer="Skipped this Question")) %>%  dplyr::select(answer, n, percentage)
  
  gt_yn %>%  gt::gt(rowname_col = "row_lab")  %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md(Title)) %>% 
  cols_label(n= md("**Number of Participants**"),  answer = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows(
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = answer,
    )
  ) 
}


boxp_funct <- function(CID,Title, Xlab) {
  CID_SYM <- rlang::ensym(CID)
  merged %>% mutate(!!CID_SYM:=as.numeric(!!CID_SYM)) %>%
    filter(!is.na(!!CID_SYM)) %>%
    ggplot(aes(x=!!CID_SYM, fill=as.character(D_407056417)))+
    xlab(Xlab) + geom_boxplot()+  ggtitle(Title)+
    scale_fill_discrete(name = "Sex at Birth", labels=c("Female", "Male")) + 
    scale_y_continuous(labels = scales::number_format(accuracy = 0.01))
}


#GT table for siblings
sib_logic_funct <- function(CID, Sib_Num, Title){  
  CID_SYM <- rlang::ensym(CID)
  data_tib_m1$D_694265648 <- as.numeric(data_tib_m1$D_694265648)
  dt_select <- data_tib_m1 %>%  filter(D_694265648 >= Sib_Num) %>%  select(Connect_ID, !!CID_SYM) 
  gt_yn <- dt_select  %>% dplyr::group_by(!!CID_SYM) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup() %>% dplyr::mutate(answer=recode(!!CID_SYM, !!!dict)) %>% replace_na(list(answer="Skipped this Question")) %>%  dplyr::select(answer, n, percentage)
  
  gt_yn %>%  gt::gt(rowname_col = "row_lab")  %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md(Title)) %>% 
  cols_label(n= md("**Number of Participants**"),  answer = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows( groups=F,
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = answer,
    )
  ) 
}


#GT table for children
child_logic_funct <- function(CID, Child_Num, Title){  
  CID_SYM <- rlang::ensym(CID)
  data_tib_m1$D_446999144 <- as.numeric(data_tib_m1$D_446999144)
  dt_select <- data_tib_m1 %>%  filter(D_446999144 >= Child_Num) %>%  select(Connect_ID, !!CID_SYM) 
  gt_yn <- dt_select  %>% dplyr::group_by(!!CID_SYM) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup() %>% dplyr::mutate(answer=recode(!!CID_SYM, !!!dict)) %>% replace_na(list(answer="Skipped this Question")) %>%  dplyr::select(answer, n, percentage)
  
  gt_yn %>%  gt::gt(rowname_col = "row_lab")  %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md(Title)) %>% 
  cols_label(n= md("**Number of Participants**"),  answer = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows( groups=F,
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = answer,
    )
  ) 
}



```


```{r query3, include=FALSE}


querymod3 <- "SELECT * FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.module3_v1_JP` where Connect_ID IS NOT NULL"
mod3_table <- bq_project_query(project, querymod3)
mod3_data <- bq_table_download(mod3_table, bigint = "integer64")
mod3_data$Connect_ID <- as.numeric(mod3_data$Connect_ID)


data_all3= left_join( mod3_data,parts_data, by="Connect_ID")

data_all3 <- data_all3 %>% filter(d_976570371==231311385)

data_tib_m3 <- as_tibble(data_all3)


```

## Age at Enrollment
```{r age, warning=FALSE,echo=FALSE}

which_age= data_tib_m1 %>%  mutate(age= case_when(state_d_934298480==713781738 ~ "Age 30-34",
                                                  state_d_934298480==631272782 ~ "Age 35-39",
                                                  state_d_934298480==124276120 ~ "Age 40-45",
                                             state_d_934298480==450985724 ~ "Age 46-50",
                                             state_d_934298480==363147933 ~ "Age 51-55",
                                             state_d_934298480==636706443 ~ "Age 56-60",
                                             state_d_934298480==771230670 ~ "Age 61-65",
                                             state_d_934298480==722846087 ~ "Age 66-70",
                                            # !is.na(D_150344905) ~ "Answered with Corrected Age in Mod1",
                                             TRUE  ~ "Skipped this question"))
which_age$age <- factor(which_age$age,levels=c("Age 30-34", "Age 35-39", "Age 40-45", "Age 46-50","Age 51-55","Age 56-60", "Age 61-65", "Age 66-70", "Skipped this question"))

dt_all_ages_summary <- which_age  %>% dplyr::group_by(age) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(age, n, percentage)  


dt_all_ages_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Age of Participants at Recruitment")) %>% 
  cols_label(n= md("**Number of Participants**"), age = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows(
  #   column = c(participants,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = age,
    )
  ) 

```


## BMI
```{r bmi, echo=FALSE, warning=FALSE, message=FALSE}
data_tib_m1$D_114314839_D_340854069=as.numeric(data_tib_m1$D_114314839_D_340854069)
data_tib_m1$D_114314839_D_600462977=as.numeric(data_tib_m1$D_114314839_D_600462977)

data_tib_m1$in_D_inches= (ifelse(is.na(data_tib_m1$D_114314839_D_340854069), 0,(data_tib_m1$D_114314839_D_340854069*12)))+ 
  (ifelse(is.na(data_tib_m1$D_114314839_D_600462977), 0, (data_tib_m1$D_114314839_D_600462977))) 

data_tib_m1$D_746012894=as.numeric(data_tib_m1$D_746012894) 
data_tib_m1$D_746012894=round(data_tib_m1$D_746012894, digits=0)

data_tib_m1= data_tib_m1 %>%  mutate(BMI= (D_746012894/in_D_inches^2)*703)

bmi_box= data_tib_m1 %>%  filter(!is.na(BMI)) %>%  ggplot(aes(x=BMI))+
    xlab("Score") + geom_boxplot()+  ggtitle("BMI Distribution of Participants") + xlim(c(0,100))



which_age= data_tib_m1 %>%  mutate(BMI_range= case_when(BMI<18.5 ~ "Underweight",
                                             BMI<25 ~ "Healthy Weight",
                                             BMI<30 ~ "Overweight",
                                             BMI<35 ~ "Obesity Class I",
                                             BMI<40 ~ "Obesity Class II",
                                             BMI>=40 ~ "Obesity Class III",
                                             TRUE  ~ "Skipped this question"))
which_age$BMI_range <- factor(which_age$BMI_range,levels=c("Underweight", "Healthy Weight", "Overweight", "Obesity Class I","Obesity Class II","Obesity Class III", "Skipped this question"))

dt_all_ages_summary <- which_age  %>% dplyr::group_by(BMI_range) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(BMI_range, n, percentage)  


dt_all_ages_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("BMI of Participants Who Completed BOH")) %>% 
  cols_label(n= md("**Number of Participants**"), BMI_range = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows(
  #   column = c(participants,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = BMI_range,
    ) 
  )  %>% 
  tab_footnote(
    footnote = md("Skipped this question means either height or weight was skipped. \n BMI calculation of 703*(weight in lbs/ height in inches sqaured)."),
  locations = cells_column_labels(columns = BMI_range),
  placement = c("left")
)%>%
  tab_footnote(
    footnote = md("BMI ranges as follows: Underweight as under 18.5, Healthy weight as 18.5-24.9, Overweight as 25-29.9, Obesity Class I as 30-34.9, Obesity Class II as 35-39.9, Severely overweight as 40 or over."),
  locations = cells_column_labels(columns = BMI_range),
  placement = c("left")
)

# tab_footnote(
#   dt_all_ages_summary_gt,
#   md("Skipped this question means either height or weight was skipped. \n BMI calculation of 703*(weight in lbs/ height in inches sqaured). \n BMI ranges as follows: Underweight as under 18.5, Healthy weight as 18.5-24.9, Overweight as 25-29.9, Severely overweight as 30 or over. "),
#   locations = cells_column_labels(columns = BMI_range),
#   placement = c("left")
# )

# 
# 
# # Modify the table using gt functions
# gt_table <- gt_table |>
#   tab_footnote(
#     md("BMI calculation of 703*(weight in lbs/ height in inches squared). BMI ranges as follows: Underweight as under 18.5, Healthy weight as 18.5-24.9, Overweight as 25-29.9, overweight as 30 or over."),
#     locations = cells_column_labels(columns = "BMI_range"),
#     placement = "left"
#   )
# 
# gt_table

```


\newpage

## Frequency of Smoking

Currently a (Product) Smoker responded with the following: 

(1) 'Yes' to 'Have you ever used any of these tobacco products, even once?' 

(2)  Either ‘50-99’ or ‘100+’ to 'How many (products) have you smoked in your entire life? 

(3) ‘In the past month’ to 'When was the last time you smoked (products)?'


    
    
Formerly a (Product) Smoker responded with the following: 

(1) 'Yes' to 'Have you ever used any of these tobacco products, even once?', 

(2) Either ‘50-99’ or ‘100+’ to 'How many (products) have you smoked in your entire life?', 

(3) Either ‘More than a month ago, but in the past year’ or ‘More than 1 year ago’ to 'When was the last time you smoked (products)?'


### Cigarettes

```{r cigerette, echo=FALSE, warning=FALSE, message=FALSE}

cig_frequency= data_tib_m3  %>% 
  mutate(often= case_when((D_947205597_D_712653855==0 | (D_947205597_D_712653855==1 & (D_763164658==151488193| D_763164658==805449318)))~"Never a Cigarette Smoker",
                             (D_947205597_D_712653855==1 & (D_763164658==486319890| D_763164658==132232896) & D_798549704==317567178)~"Currently a Cigarette Smoker",
                             (D_947205597_D_712653855==1 & (D_763164658==486319890| D_763164658==132232896)  & (D_798549704==484055234 | D_798549704==802197176))~"Formerly a Cigarette Smoker",
                             TRUE~"Skipped all these questions"))

dt_cig_frequency_summary <- cig_frequency %>% group_by(often) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(often, n, percentage)


dt_cig_frequency_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Frequency of Cigarette Smoking of Participants Who Completed SAS")) %>% 
  cols_label(n= md("**Number of Participants**"), often = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows(
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = often,
    )
  )  
#   tab_footnote(
#     footnote = md("Currently a Cigarette Smoker repsonded with the following: 
#     'Yes' to 'Have you ever used any of these tobacco products, even once?', 
#     either ‘50-99’ or ‘100+’ to 'How many cigarettes have you smoked in your entire life?',
#     and ‘in the past month’ to 'When was the last time you smoked cigarettes?' "),
#   locations = cells_column_labels(columns = often),
#   placement = c("left")
# )%>%
#   tab_footnote(
#     footnote = md("Formerly a Cigarette Smoker repsonded with the following: 
#     'Yes' to 'Have you ever used any of these tobacco products, even once?', 
#     either ‘50-99’ or ‘100+’ to 'How many cigarettes have you smoked in your entire life?',
#     and either ‘More than a month ago, but in the past year’ or ‘More than 1 year ago’ to 'When was the last time you smoked cigarettes?' "),
#   locations = cells_column_labels(columns = often),
#   placement = c("left")
# )


```



### Cigar 

```{r cigar, echo=FALSE, warning=FALSE, message=FALSE}


cigar_frequency= data_tib_m3  %>% 
  mutate(often= case_when(D_947205597_D_198133418==0 | (D_947205597_D_198133418==1 & (D_182431332==151488193| D_182431332==805449318))~"Never a Cigar Smoker",
                             D_947205597_D_198133418==1 & (D_182431332==486319890| D_182431332==132232896) & D_798549704==317567178~"Currently a Cigar Smoker",
                             D_947205597_D_198133418==1 & (D_182431332==486319890| D_182431332==132232896)  & (D_789271762==484055234 | D_789271762==802197176)~"Formerly a Cigar Smoker",
                             TRUE~"Skipped all These Questions"))



dt_cigar_frequency_summary <- cigar_frequency %>% group_by(often) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(often, n, percentage)

dt_cigar_frequency_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Frequency of Cigar Smoking of Participants Who Completed SAS")) %>% 
  cols_label(n= md("**Number of Participants**"), often = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows(
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = often,
    )
  ) 


```


\newpage

### E-cigarette 

```{r ecig, echo=FALSE, warning=FALSE, message=FALSE}


e_cig_frequency= data_tib_m3  %>% 
  mutate(often= case_when(D_947205597_D_706254326==0 | (D_947205597_D_706254326==1 & (D_624111331==151488193| D_624111331==805449318))~"Never a E-cigarette Smoker",
                             D_947205597_D_706254326==1 & (D_624111331==486319890| D_624111331==132232896) & D_238422161==317567178~"Currently a E-cigarette Smoker",
                             D_947205597_D_706254326==1 & (D_624111331==486319890| D_624111331==132232896)  & (D_238422161==484055234 | D_238422161==802197176)~"Formerly a E-cigarette Smoker",
                             TRUE~"Skipped all These Questions"))



dt_e_cig_frequency_summary <- e_cig_frequency %>% group_by(often) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(often, n, percentage)

dt_e_cig_frequency_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Frequency of Electronic Cigarette Smoking of Participants Who Completed SAS")) %>% 
  cols_label(n= md("**Number of Participants**"), often = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows(
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = often,
    )
  ) 


```


\newpage

## Primary Relative Diagnosed with Cancer
### Parents
```{r PrimRelCancerMomDad, echo=FALSE, warning=FALSE, message=FALSE}

# degree1_cancer= module3 %>%  filter(ifelse(D_276353712==353358909 | D_659784914==353358909 | D_607773106_1_1==353358909 | D_607773106_2_2==353358909 | 
#                                       D_607773106_3_3==353358909 | D_607773106_4_4==353358909 | D_607773106_5_5==353358909 | D_607773106_6_6==353358909 |
#                                       D_607773106_7_7==353358909| D_607773106_8_8==353358909 | D_607773106_9_9==353358909| D_607773106_10_10==353358909 |
#                                       D_607773106_11_11==353358909 | D_607773106_12_12==353358909 | D_607773106_13_13==353358909 | D_718867914_1_1==353358909 | 
#                                       D_718867914_2_2==353358909 | D_718867914_3_3==353358909 | D_718867914_4_4==353358909 | D_718867914_5_5==353358909 |
#                                       D_718867914_6_6==353358909 | D_718867914_7_7==353358909 | D_718867914_8_8==353358909 | D_718867914_9_9==353358909 |
#                                       D_718867914_10_10==353358909), 1, 0)


family= data_tib_m1  %>%  mutate(status= case_when((D_276353712==353358909 | D_659784914==353358909) ~ "Yes", 
                                                    TRUE ~ "No"))
# family$percentage <- round(family$percentage, digits=2)
# dt_fam_canc_summary <- family %>% group_by(status) %>%   summarize_at(c("freq", "percentage"), sum, na.rm = TRUE)
# 
# knitr::kable(dt_fam_canc_summary,col.names=c("Diagnosed","Number of Participants" , "Percentage of Participants"), caption='Primary Relative(s) Diagnosed With Cancer')
# #,row.names=FALSE, align=c("l","c","c","c"), booktabs = TRUE )
# 
# dt_fam_canc_summary %>%  gt::gt() %>%  ## why is this not a proper gt_tbl??
#   fmt_number(columns = "percentage", decimals = 2) %>%
#   tab_header(title = md("Primary Relative(s) Diagnosed With Cancer")) %>%
#   cols_label(status = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>%
#     summary_rows(
#     column = percentage,
#     fns= list(
#       Sum= ~sum(.)
#     ), decimals=0) %>%
#   tab_options(
#       stub.font.weight = "bold"
#     ) %>%
#   tab_style(
#     style = list(
#       cell_text(weight = "bold")
#     ),
#     locations = cells_body(
#       columns = status,
#     )
#   ) 



dt_fam_canc_summary <- family %>% group_by(status) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(status, n, percentage)


dt_fam_canc_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Primary Relative(s) Diagnosed With Cancer of Participants Who Completed BOH")) %>% 
  cols_label(n= md("**Number of Participants**"), status = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows(
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = status,
    )
  ) 

```



### Siblings
```{r PrimRelCancerSib, echo=FALSE, warning=FALSE, message=FALSE}

family= data_tib_m1  %>%  mutate(status= case_when((D_607773106_1_1==353358909 | D_607773106_2_2==353358909 | 
                                      D_607773106_3_3==353358909 | D_607773106_4_4==353358909 | D_607773106_5_5==353358909 | D_607773106_6_6==353358909 |
                                      D_607773106_7_7==353358909| D_607773106_8_8==353358909 | D_607773106_9_9==353358909| D_607773106_10_10==353358909 |
                                      D_607773106_11_11==353358909 | D_607773106_12_12==353358909 | D_607773106_13_13==353358909 | D_607773106_14_14==353358909 |
                                        D_607773106_15_15==353358909 | D_607773106_16_16==353358909 | D_607773106_17_17==353358909 |
                                        D_607773106_18_18==353358909 | D_607773106_19_19==353358909 | D_607773106_20_20==353358909 | D_607773106_21_21==353358909 |
                                        D_607773106_22_22==353358909 | D_607773106_23_23==353358909 | D_607773106_24_24==353358909) ~ "Yes", 
                                                    TRUE ~ "No"))
# family$percentage <- round(family$percentage, digits=2)
# dt_fam_canc_summary <- family %>% group_by(status) %>%   summarize_at(c("freq", "percentage"), sum, na.rm = TRUE)
# 
# knitr::kable(dt_fam_canc_summary,col.names=c("Diagnosed","Number of Participants" , "Percentage of Participants"), caption='Primary Relative(s) Diagnosed With Cancer')
# #,row.names=FALSE, align=c("l","c","c","c"), booktabs = TRUE )
# 
# dt_fam_canc_summary %>%  gt::gt() %>%  ## why is this not a proper gt_tbl??
#   fmt_number(columns = "percentage", decimals = 2) %>%
#   tab_header(title = md("Primary Relative(s) Diagnosed With Cancer")) %>%
#   cols_label(status = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>%
#     summary_rows(
#     column = percentage,
#     fns= list(
#       Sum= ~sum(.)
#     ), decimals=0) %>%
#   tab_options(
#       stub.font.weight = "bold"
#     ) %>%
#   tab_style(
#     style = list(
#       cell_text(weight = "bold")
#     ),
#     locations = cells_body(
#       columns = status,
#     )
#   ) 



dt_fam_canc_summary <- family %>% group_by(status) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(status, n, percentage)


dt_fam_canc_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Primary Relative(s) Diagnosed With Cancer of Participants Who Completed BOH ")) %>% 
  cols_label(n= md("**Number of Participants**"), status = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows(
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = status,
    )
  ) 

```



### Children
```{r PrimRelCancerChild, echo=FALSE, warning=FALSE, message=FALSE}

# degree1_cancer= module3 %>%  filter(ifelse(D_276353712==353358909 | D_659784914==353358909 | D_607773106_1_1==353358909 | D_607773106_2_2==353358909 | 
#                                       D_607773106_3_3==353358909 | D_607773106_4_4==353358909 | D_607773106_5_5==353358909 | D_607773106_6_6==353358909 |
#                                       D_607773106_7_7==353358909| D_607773106_8_8==353358909 | D_607773106_9_9==353358909| D_607773106_10_10==353358909 |
#                                       D_607773106_11_11==353358909 | D_607773106_12_12==353358909 | D_607773106_13_13==353358909 | D_718867914_1_1==353358909 | 
#                                       D_718867914_2_2==353358909 | D_718867914_3_3==353358909 | D_718867914_4_4==353358909 | D_718867914_5_5==353358909 |
#                                       D_718867914_6_6==353358909 | D_718867914_7_7==353358909 | D_718867914_8_8==353358909 | D_718867914_9_9==353358909 |
#                                       D_718867914_10_10==353358909), 1, 0)



family= data_tib_m1  %>%  mutate(status= case_when((D_718867914_1_1==353358909 | 
                                      D_718867914_2_2==353358909 | D_718867914_3_3==353358909 | D_718867914_4_4==353358909 | D_718867914_5_5==353358909 |
                                      D_718867914_6_6==353358909 | D_718867914_7_7==353358909 | D_718867914_8_8==353358909 | D_718867914_9_9==353358909 |
                                      D_718867914_10_10==353358909 | D_718867914_11_11==353358909 | D_718867914_12_12==353358909 |
                                      D_718867914_13_13==353358909| D_718867914_14_14==353358909) ~ "Yes", 
                                                    TRUE ~ "No"))
# family$percentage <- round(family$percentage, digits=2)
# dt_fam_canc_summary <- family %>% group_by(status) %>%   summarize_at(c("freq", "percentage"), sum, na.rm = TRUE)
# 
# knitr::kable(dt_fam_canc_summary,col.names=c("Diagnosed","Number of Participants" , "Percentage of Participants"), caption='Primary Relative(s) Diagnosed With Cancer')
# #,row.names=FALSE, align=c("l","c","c","c"), booktabs = TRUE )
# 
# dt_fam_canc_summary %>%  gt::gt() %>%  ## why is this not a proper gt_tbl??
#   fmt_number(columns = "percentage", decimals = 2) %>%
#   tab_header(title = md("Primary Relative(s) Diagnosed With Cancer")) %>%
#   cols_label(status = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>%
#     summary_rows(
#     column = percentage,
#     fns= list(
#       Sum= ~sum(.)
#     ), decimals=0) %>%
#   tab_options(
#       stub.font.weight = "bold"
#     ) %>%
#   tab_style(
#     style = list(
#       cell_text(weight = "bold")
#     ),
#     locations = cells_body(
#       columns = status,
#     )
#   ) 



dt_fam_canc_summary <- family %>% group_by(status) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(status, n, percentage)


dt_fam_canc_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Primary Relative(s) Diagnosed With Cancer  of Participants Who Completed BOH")) %>% 
  cols_label(n= md("**Number of Participants**"), status = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows(
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
  grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
    stub.font.weight = "bold"
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = status,
    )
  ) 

```

\newpage

## RACE
```{r Race, warning=FALSE, echo=FALSE, message=FALSE}


## Multi-racial

multi_race=0    
for (i in 1:length(data_tib_m1$Connect_ID)){
  AI=ifelse((data_tib_m1$D_384191091_D_384191091_D_583826374[[i]]==1 & (data_tib_m1$D_384191091_D_384191091_D_636411467[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_458435048[[i]]==1|
                                               data_tib_m1$D_384191091_D_384191091_D_706998638[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                               data_tib_m1$D_384191091_D_384191091_D_586825330[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                               data_tib_m1$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  As=ifelse((data_tib_m1$D_384191091_D_384191091_D_636411467[[i]]==1 & (data_tib_m1$D_384191091_D_384191091_D_583826374[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_458435048[[i]]==1|
                                                        data_tib_m1$D_384191091_D_384191091_D_706998638[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_586825330[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Bl=ifelse((data_tib_m1$D_384191091_D_384191091_D_458435048[[i]]==1 & (data_tib_m1$D_384191091_D_384191091_D_583826374[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        data_tib_m1$D_384191091_D_384191091_D_706998638[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_586825330[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Hs=ifelse((data_tib_m1$D_384191091_D_384191091_D_706998638[[i]]==1 & (data_tib_m1$D_384191091_D_384191091_D_583826374[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        data_tib_m1$D_384191091_D_384191091_D_458435048[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_586825330[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Me=ifelse((data_tib_m1$D_384191091_D_384191091_D_973565052[[i]]==1 & (data_tib_m1$D_384191091_D_384191091_D_583826374[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        data_tib_m1$D_384191091_D_384191091_D_458435048[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_586825330[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Hw=ifelse((data_tib_m1$D_384191091_D_384191091_D_586825330[[i]]==1 & (data_tib_m1$D_384191091_D_384191091_D_583826374[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        data_tib_m1$D_384191091_D_384191091_D_458435048[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_973565052[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_412790539[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Wh=ifelse((data_tib_m1$D_384191091_D_384191091_D_412790539[[i]]==1 & (data_tib_m1$D_384191091_D_384191091_D_583826374[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        data_tib_m1$D_384191091_D_384191091_D_458435048[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_586825330[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_807835037[[i]]==1)), 1, 0)
  Ot=ifelse((data_tib_m1$D_384191091_D_384191091_D_807835037[[i]]==1 & (data_tib_m1$D_384191091_D_384191091_D_583826374[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_636411467[[i]]==1|
                                                        data_tib_m1$D_384191091_D_384191091_D_458435048[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_706998638[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_586825330[[i]]==1 | data_tib_m1$D_384191091_D_384191091_D_973565052[[i]]==1 |
                                                        data_tib_m1$D_384191091_D_384191091_D_412790539[[i]]==1)), 1, 0)
  multi_race= multi_race + sum(AI+As+Bl+Hs+Me+Hw+Wh+Ot, na.rm=T)

}

#cat("Percentage of multirace participants:", (multi_race/(dim(data_tib_m1)[1]))*100)
   
   

data_tib_m1$multi_racial <- c(rep(1, times=multi_race), rep(0, times=(dim(data_tib_m1)[1]- multi_race)))



## RACE

which_race= data_tib_m1 %>%  mutate(race= case_when(multi_racial==1 ~ "Multi-Racial",
                                                     D_384191091_D_384191091_D_583826374==1 ~ "American Indian or Native American",
                                                     D_384191091_D_384191091_D_636411467==1 ~ "Asian/Asian American",
                                                     D_384191091_D_384191091_D_458435048==1 ~ "Black, African American, or African",
                                                     D_384191091_D_384191091_D_706998638==1 ~ "Hispanic, Latino, or Spanish",
                                                     D_384191091_D_384191091_D_973565052==1 ~ "Middle Eastern or North African",
                                                     D_384191091_D_384191091_D_586825330==1 ~ "Hawaiian or Pacific Islander",
                                                     D_384191091_D_384191091_D_412790539==1 ~ "White",
                                                     (D_384191091_D_384191091_D_807835037==1 | !is.na(D_384191091_D_747350323)) ~ "Other",
                                                     D_384191091_D_384191091_D_746038746==1 ~ "Prefer Not to Answer",
                                                     TRUE  ~ "Skipped this question"))

dt_all_races_summary <- which_race  %>% dplyr::group_by(race) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.)) %>% dplyr::ungroup()  %>%  dplyr::select(race, n, percentage)

dt_all_races_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Race/Ethnicity of Participants Who Completed BOH")) %>% 
  cols_label(n= md("**Number of Participants**"), race = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows( groups=F,
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = race,
    )
  )

```


\FloatBarrier
```{r RaceByAge, warning=FALSE, echo=FALSE, message=FALSE}
race_age= which_race %>%  mutate(age= case_when(state_d_934298480==713781738 ~ "Age 30-34",
                                                  state_d_934298480==631272782 ~ "Age 35-39",
                                                  state_d_934298480==124276120 ~ "Age 40-45",
                                             state_d_934298480==450985724 ~ "Age 46-50",
                                             state_d_934298480==363147933 ~ "Age 51-55",
                                             state_d_934298480==636706443 ~ "Age 56-60",
                                             state_d_934298480==771230670 ~ "Age 61-65",
                                             state_d_934298480==722846087 ~ "Age 66-70",
                                            # !is.na(D_150344905) ~ "Answered with Corrected Age in Mod1",
                                             TRUE  ~ "Skipped this question"))
race_age$age <- factor(race_age$age,levels=c("Age 30-34", "Age 35-39", "Age 40-45", "Age 46-50","Age 51-55","Age 56-60", "Age 61-65", "Age 66-70", "Skipped this question"))

race_age_tbl <- race_age %>% 
tbl_cross(
    row = race,
    col = age,
    digits=c(0,1),
    percent = "row",
    label=list(race="Race",
               age = "Age"),
    missing="ifany",
    margin_text="Total Participants") 

# status_elg_df <- as.data.frame(race_age_tbl)
# status_elg_df <- status_elg_df[c(-1),]

race_age_tbl %>%
  #bold_labels() %>%
  #italicize_levels() %>%
  modify_header(stat_0 = "Total") %>%
  modify_caption("Distrubiution of Race/Ethnicity by Age Groups of Participants Who Completed BOH") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>%  kable_styling(latex_options = "scale_down")




age_race_tbl <- race_age %>% 
tbl_cross(
    row = race, 
    col = age,
    digits=c(0,1),
    percent = "col",
    label=list(race="Race",
               age = "Age"),
    missing="ifany",
    margin_text="Total Participants") 

# status_elg_df <- as.data.frame(status_elg)
# status_elg_df <- status_elg_df[c(-1),]

age_race_tbl %>%
  #bold_labels() %>%
  #italicize_levels() %>%
  modify_header(stat_0 = "Total") %>%
  modify_caption("Distrubiution of Race/Ethnicity by Age Groups of Participants Who Completed BOH") %>%
  as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>%  kable_styling(latex_options = "scale_down")


```



## RACEETH2-8 (Ethnicity)
```{r Ethnicity1, warning=FALSE, echo=FALSE, message=FALSE}


#American Indian/Native American
dt_am_ind_ethn= data_tib_m1 %>%  filter(data_tib_m1$D_384191091_D_384191091_D_583826374==1)  


dt_am_ind_ethn= dt_am_ind_ethn %>%  mutate(multb2 = ifelse(D_362270886_D_362270886_D_249603425==1, 1, 0) + ifelse(D_362270886_D_362270886_D_530063091==1, 1, 0) + ifelse(D_362270886_D_362270886_D_643489668==1, 1, 0) + 
                                             ifelse(D_362270886_D_362270886_D_807835037==1, 1, 0) + ifelse(D_362270886_D_362270886_D_746038746==1, 1, 0))


amer_eth= dt_am_ind_ethn %>%  mutate(ethnicity= case_when(as.numeric(multb2)>1 ~ "Multi-Ethnic",
                                                          D_362270886_D_362270886_D_249603425==1 ~ "American Indian",
                                             D_362270886_D_362270886_D_530063091==1 ~ "Alaska Native",
                                             D_362270886_D_362270886_D_643489668==1 ~ "Central or South American Indian",
                                             (D_362270886_D_362270886_D_807835037==1 | !is.na(D_362270886_D_650100414)) ~ "Other",
                                             D_362270886_D_362270886_D_746038746==1 ~ "Prefer Not to Answer",
                                             TRUE ~ "Skipped this question"))

dt_am_ind_ethn_summary <- amer_eth %>% group_by(ethnicity) %>%    dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(ethnicity, n, percentage) 
gtm3_print <- gt::gt(dt_am_ind_ethn_summary)


dt_ethnic1 <- dt_am_ind_ethn_summary %>%  gt::gt(rowname_col = "row_lab") %>%
  fmt_number(columns = "percentage", decimals = 2) %>%
  tab_header(title = md("Ethnicity of American Indian/Native American Participants  of Participants Who Completed BOH")) %>%
  cols_label(n= md("**Number of Participants**"), ethnicity = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>%
  # summary_rows( groups=F,
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = ethnicity,
    )
  ) 
tab_footnote(
  dt_ethnic1,
  md("The denomination of this table is all participants who selected this race/ethnicity only, as well as multi-racial participants that selected this race/ethnicity as well as other race/ethnicities. \n Multi-ethnic in this table is defined as participants that selected multiple ethnicity responses."),
  locations = cells_column_labels(columns = n),
  placement = c("left")
)

```

\newpage
```{r Ethnicity2_3, warning=FALSE, echo=FALSE, message=FALSE}
#Asian/Asian American
dt_asian= data_tib_m1 %>% filter(data_tib_m1$D_384191091_D_384191091_D_636411467==1)  

dt_asian= dt_asian %>%  mutate(multb2 = ifelse(D_525535977_D_525535977_D_773844957==1, 1, 0) + ifelse(D_525535977_D_525535977_D_901439277==1, 1, 0) + ifelse(D_525535977_D_525535977_D_750168061==1, 1, 0) + 
                                             ifelse(D_525535977_D_525535977_D_326604981==1, 1, 0) + ifelse(D_525535977_D_525535977_D_469918550==1, 1, 0) + ifelse(D_525535977_D_525535977_D_288079668==1, 1, 0) + ifelse(D_525535977_D_525535977_D_240721579==1, 1, 0) + ifelse(D_525535977_D_525535977_D_571633051==1, 1, 0) + ifelse(D_525535977_D_525535977_D_964924704==1, 1, 0) + ifelse(D_525535977_D_525535977_D_807835037==1, 1, 0) + ifelse(D_525535977_D_525535977_D_746038746==1, 1, 0))


                                                          
which_eth= dt_asian %>%  mutate(ethnicity= case_when(as.numeric(multb2)>1 ~ "Multi-Ethnic",
                                                     D_525535977_D_525535977_D_773844957==1 ~ "Asian indian",
                                             D_525535977_D_525535977_D_901439277==1 ~ "Cambodian",
                                             D_525535977_D_525535977_D_750168061==1 ~ "Chinese",
                                             D_525535977_D_525535977_D_326604981==1 ~ "Filipino",
                                             D_525535977_D_525535977_D_469918550==1 ~ "Hmong",
                                             D_525535977_D_525535977_D_288079668==1 ~ "Japanese",
                                             D_525535977_D_525535977_D_240721579==1 ~ "Korean",
                                             D_525535977_D_525535977_D_571633051==1 ~ "Pakastani",
                                             D_525535977_D_525535977_D_964924704==1 ~ "Vietnamese",
                                             (D_525535977_D_525535977_D_807835037==1 | !is.na(D_525535977_D_396618548)) ~ "Other",
                                             D_525535977_D_525535977_D_746038746==1 ~ "Prefer Not to Answer",
                                             TRUE ~ "Skipped this question"))

dt_asian_summary <- which_eth %>% group_by(ethnicity) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(ethnicity, n, percentage) 

dt_ethnic2 <- dt_asian_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Ethnicity of Asian and Asian American Participants  of Participants Who Completed BOH")) %>% 
  cols_label(n= md("**Number of Participants**"), ethnicity = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows( groups=F,
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = ethnicity,
    )
  ) 
tab_footnote(
  dt_ethnic2,
  md("The denomination of this table is all participants who selected this race/ethnicity only, as well as multi-racial participants that selected this race/ethnicity as well as other race/ethnicities. \n Multi-ethnic in this table is defined as participants that selected multiple ethnicity responses."),
  locations = cells_column_labels(columns = n),
  placement = c("left")
)



#Black/African/African American 
dt_black= data_tib_m1 %>% filter(data_tib_m1$D_384191091_D_384191091_D_458435048==1)  

dt_black= dt_black %>%  mutate(multb2 = ifelse(D_976808005_D_976808005_D_704774349==1, 1, 0) + ifelse(D_976808005_D_976808005_D_240854115==1, 1, 0) + ifelse(D_976808005_D_976808005_D_280957170==1, 1, 0) + 
                                             ifelse(D_976808005_D_976808005_D_533776046==1, 1, 0) + ifelse(D_976808005_D_976808005_D_647105074==1, 1, 0) + ifelse(D_976808005_D_976808005_D_618222258==1, 1, 0) + ifelse(D_976808005_D_976808005_D_487027241==1, 1, 0) + ifelse(D_976808005_D_976808005_D_900838463==1, 1, 0) + ifelse(D_976808005_D_976808005_D_379093069==1, 1, 0) + ifelse(D_976808005_D_976808005_D_304643362==1, 1, 0) + ifelse(D_976808005_D_976808005_D_151821009==1, 1, 0) + ifelse(D_976808005_D_976808005_D_807835037==1, 1, 0) + ifelse(D_976808005_D_976808005_D_746038746==1, 1, 0))



which_eth= dt_black %>%  mutate(ethnicity= case_when(as.numeric(multb2)>1 ~ "Multi-Ethnic",
                                                     D_976808005_D_976808005_D_704774349==1 ~ "African American",
                                             D_976808005_D_976808005_D_240854115==1 ~ "Barbadian",
                                             D_976808005_D_976808005_D_280957170==1 ~ "Caribbean",
                                             D_976808005_D_976808005_D_533776046==1 ~ "Ethiopian",
                                             D_976808005_D_976808005_D_647105074==1 ~ "Ghanauin",
                                             D_976808005_D_976808005_D_618222258==1 ~ "Haitian",
                                             D_976808005_D_976808005_D_487027241==1 ~ "Jamaican",
                                             D_976808005_D_976808005_D_900838463==1 ~ "Liberian",
                                             D_976808005_D_976808005_D_379093069==1 ~ "Nigerian",
                                             D_976808005_D_976808005_D_304643362==1 ~ "Somali",
                                             D_976808005_D_976808005_D_151821009==1 ~ "South African",
                                             (D_976808005_D_976808005_D_807835037==1 | !is.na(D_976808005_D_852296096)) ~ "Other",
                                             D_976808005_D_976808005_D_746038746==1 ~ "Prefer Not to Answer",
                                             TRUE   ~ "Skipped this question"))



dt_black_summary <- which_eth %>% group_by(ethnicity) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(ethnicity, n, percentage)
dt_ethnic3 <- dt_black_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Ethnicity of Black/African/African American Participants  of Participants Who Completed BOH")) %>% 
  cols_label(n= md("**Number of Participants**"), ethnicity = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows( groups=F,
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = ethnicity,
    )
  ) 
tab_footnote(
  dt_ethnic3,
  md("The denomination of this table is all participants who selected this race/ethnicity only, as well as multi-racial participants that selected this race/ethnicity as well as other race/ethnicities. \n Multi-ethnic in this table is defined as participants that selected multiple ethnicity responses."),
  locations = cells_column_labels(columns = n),
  placement = c("left")
)

```
\newpage

```{r Ethnicity4_5, warning=FALSE, echo=FALSE, message=FALSE}
#Hispanic/Latino/Spanish
dt_hisp= data_tib_m1  %>% filter(data_tib_m1$D_384191091_D_384191091_D_706998638==1) 

dt_hisp= dt_hisp %>%  mutate(multb2 = ifelse(D_308014437_D_308014437_D_810637250==1, 1, 0) + ifelse(D_308014437_D_308014437_D_248444252==1, 1, 0) + ifelse(D_308014437_D_308014437_D_764331628==1, 1, 0) + 
                                             ifelse(D_308014437_D_308014437_D_412757551==1, 1, 0) + ifelse(D_308014437_D_308014437_D_981774939==1, 1, 0) + ifelse(D_308014437_D_308014437_D_432305109==1, 1, 0) + ifelse(D_308014437_D_308014437_D_862718552==1, 1, 0) + ifelse(D_308014437_D_308014437_D_988121468==1, 1, 0) + ifelse(D_308014437_D_308014437_D_773342525==1, 1, 0) + ifelse(D_308014437_D_308014437_D_807835037==1, 1, 0) + ifelse(D_308014437_D_308014437_D_746038746==1, 1, 0))



which_eth= dt_hisp %>%  mutate(ethnicity= case_when(as.numeric(multb2)>1 ~ "Multi-Ethnic",
                                                    D_308014437_D_308014437_D_810637250==1 ~ "Columbian",
                                             D_308014437_D_308014437_D_248444252==1 ~ "Cuban",
                                             D_308014437_D_308014437_D_764331628==1 ~ "Dominican",
                                             D_308014437_D_308014437_D_412757551==1 ~ "Ecuadorian",
                                             D_308014437_D_308014437_D_981774939==1 ~ "Hondurian",
                                             D_308014437_D_308014437_D_432305109==1 ~ "Mexican or Mexican American",
                                             D_308014437_D_308014437_D_862718552==1 ~ "Puerto Rican",
                                             D_308014437_D_308014437_D_988121468==1 ~ "Salvadorian",
                                             D_308014437_D_308014437_D_773342525==1 ~ "Spanish",
                                             (D_308014437_D_308014437_D_807835037==1 | !is.na(D_308014437_D_440307926)) ~ "Other",
                                             D_308014437_D_308014437_D_746038746==1 ~ "Prefer Not to Answer",
                                             TRUE   ~ "Skipped this question"))

dt_hisp_summary <- which_eth %>% group_by(ethnicity) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(ethnicity, n, percentage)

dt_ethnic4 <- dt_hisp_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Ethnicity of Hispanic/Latino/Spanish Participants of Those Who Completed BOH")) %>% 
  cols_label(n= md("**Number of Participants**"), ethnicity = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows( groups=F,
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = ethnicity,
    )
  ) 
tab_footnote(
  dt_ethnic4,
  md("The denomination of this table is all participants who selected this race/ethnicity only, as well as multi-racial participants that selected this race/ethnicity as well as other race/ethnicities. \n Multi-ethnic in this table is defined as participants that selected multiple ethnicity responses."),
  locations = cells_column_labels(columns = n),
  placement = c("left")
)



#Middle Eastern or North African
dt_mideast= data_tib_m1 %>%  filter(data_tib_m1$D_384191091_D_384191091_D_973565052==1)  

dt_mideast= dt_mideast %>%  mutate(multb2 = ifelse(D_351657815_D_351657815_D_190152384==1, 1, 0) + ifelse(D_351657815_D_351657815_D_119632587==1, 1, 0) + ifelse(D_351657815_D_351657815_D_578616917==1, 1, 0) + 
                                             ifelse(D_351657815_D_351657815_D_834030167==1, 1, 0) + ifelse(D_351657815_D_351657815_D_680575651==1, 1, 0) + ifelse(D_351657815_D_351657815_D_144320785==1, 1, 0) + ifelse(D_351657815_D_351657815_D_214951746==1, 1, 0) + ifelse(D_351657815_D_351657815_D_932563284==1, 1, 0) + ifelse(D_351657815_D_351657815_D_336596477==1, 1, 0) + ifelse(D_351657815_D_351657815_D_380583570==1, 1, 0) + ifelse(D_351657815_D_351657815_D_807835037==1, 1, 0) + ifelse(D_351657815_D_351657815_D_746038746==1, 1, 0))


                                                    
which_eth= dt_mideast %>%  mutate(ethnicity= case_when(as.numeric(multb2)>1 ~ "Multi-Ethnic",
                                                       D_351657815_D_351657815_D_190152384==1 ~ "Afghan",
                                             D_351657815_D_351657815_D_119632587==1 ~ "Algerian",
                                             D_351657815_D_351657815_D_578616917==1 ~ "Egyptian",
                                             D_351657815_D_351657815_D_834030167==1 ~ "Iranian",
                                             D_351657815_D_351657815_D_680575651==1 ~ "Iraqi",
                                             D_351657815_D_351657815_D_144320785==1 ~ "Israeli",
                                             D_351657815_D_351657815_D_214951746==1 ~ "Lebanese",
                                             D_351657815_D_351657815_D_932563284==1 ~ "Moroccan",
                                             D_351657815_D_351657815_D_336596477==1 ~ "Syrian",
                                             D_351657815_D_351657815_D_380583570==1 ~ "Tunisian",
                                             (D_351657815_D_351657815_D_807835037==1 | !is.na(D_351657815_D_576646485)) ~ "Other",
                                             D_351657815_D_351657815_D_746038746==1 ~ "Prefer Not to Answer",
                                             TRUE   ~ "Skipped this question"))

dt_mideast_summary <- which_eth %>% group_by(ethnicity) %>%   dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(ethnicity, n, percentage)

dt_ethnic5 <- dt_mideast_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Ethnicity of Middle Eastern or North African Participants of Those Who Completed BOH")) %>% 
  cols_label(n= md("**Number of Participants**"), ethnicity = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows( groups=F,
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = ethnicity,
    )
  ) 
tab_footnote(
  dt_ethnic5,
  md("The denomination of this table is all participants who selected this race/ethnicity only, as well as multi-racial participants that selected this race/ethnicity as well as other race/ethnicities. \n Multi-ethnic in this table is defined as participants that selected multiple ethnicity responses."),
  locations = cells_column_labels(columns = n),
  placement = c("left")
)
```
\newpage

```{r Ethnicity6_7, warning=FALSE, echo=FALSE, message=FALSE}
#Hawaiian/ Pacific Islander
dt_hawi= data_tib_m1 %>%  filter(data_tib_m1$D_384191091_D_384191091_D_586825330==1)  

dt_hawi= dt_hawi %>%  mutate(multb2 = ifelse(D_115616118_D_115616118_D_664730658==1, 1, 0) + ifelse(D_115616118_D_115616118_D_949727109==1, 1, 0) + ifelse(D_115616118_D_115616118_D_496132363==1, 1, 0) + 
                                             ifelse(D_115616118_D_115616118_D_453456270==1, 1, 0) + ifelse(D_115616118_D_115616118_D_819018322==1, 1, 0) + ifelse(D_115616118_D_115616118_D_685406566==1, 1, 0) + ifelse(D_115616118_D_115616118_D_786290435==1, 1, 0) + ifelse(D_115616118_D_115616118_D_167028305==1, 1, 0) + ifelse(D_115616118_D_115616118_D_345861266==1, 1, 0) +  ifelse(D_115616118_D_115616118_D_807835037==1, 1, 0) + ifelse(D_115616118_D_115616118_D_746038746==1, 1, 0))

                                                       
which_eth= dt_hawi %>%  mutate(ethnicity= case_when(as.numeric(multb2)>1 ~ "Multi-Ethnic",
                                                    D_115616118_D_115616118_D_664730658==1 ~ "Chamorro",
                                             D_115616118_D_115616118_D_949727109==1 ~ "Chuukese",
                                             D_115616118_D_115616118_D_496132363==1 ~ "Fijian",
                                             D_115616118_D_115616118_D_453456270==1 ~ "Marshallese",
                                             D_115616118_D_115616118_D_819018322==1 ~ "Hawaiian",
                                             D_115616118_D_115616118_D_685406566==1 ~ "Palauan",
                                             D_115616118_D_115616118_D_786290435==1 ~ "Samoan",
                                             D_115616118_D_115616118_D_167028305==1 ~ "Tahitian",
                                             D_115616118_D_115616118_D_345861266==1 ~ "Tongan",
                                             (D_115616118_D_115616118_D_807835037==1 | !is.na(D_115616118_D_403180970)) ~ "Other",
                                             D_115616118_D_115616118_D_746038746==1 ~ "Prefer Not to Answer",
                                             TRUE   ~ "Skipped this question"))

dt_hawi_summary <- which_eth %>% group_by(ethnicity) %>% dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(ethnicity, n, percentage)

dt_ethnic6 <- dt_hawi_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Ethnicity of Hawaiian or Pacific Islander Participants of Those Who Completed BOH")) %>% 
  cols_label(n= md("**Number of Participants**"), ethnicity = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows( groups=F,
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = ethnicity,
    )
  ) 
tab_footnote(
  dt_ethnic6,
  md("The denomination of this table is all participants who selected this race/ethnicity only, as well as multi-racial participants that selected this race/ethnicity as well as other race/ethnicities.\n Multi-ethnic in this table is defined as participants that selected multiple ethnicity responses."),
  locations = cells_column_labels(columns = n),
  placement = c("left")
)



#White
dt_white= data_tib_m1 %>% filter(data_tib_m1$D_384191091_D_384191091_D_412790539==1) 

dt_white= dt_white %>%  mutate(multb2 = ifelse(D_797626610_D_797626610_D_664571574==1, 1, 0) + ifelse(D_797626610_D_797626610_D_163149180==1, 1, 0) + ifelse(D_797626610_D_797626610_D_192776753==1, 1, 0) + 
                                             ifelse(D_797626610_D_797626610_D_733789220==1, 1, 0) + ifelse(D_797626610_D_797626610_D_418464677==1, 1, 0) + ifelse(D_797626610_D_797626610_D_859329001==1, 1, 0) + ifelse(D_797626610_D_797626610_D_267472307==1, 1, 0) + ifelse(D_797626610_D_797626610_D_918190932==1, 1, 0) + ifelse(D_797626610_D_797626610_D_381749264==1, 1, 0) + ifelse(D_797626610_D_797626610_D_704661219==1, 1, 0) + ifelse(D_797626610_D_797626610_D_773342525==1, 1, 0) +  ifelse(D_797626610_D_797626610_D_807835037==1, 1, 0) + ifelse(D_797626610_D_797626610_D_746038746==1, 1, 0))


which_eth= dt_white %>%  mutate(ethnicity= case_when(as.numeric(multb2)>1 ~ "Multi-Ethnic",
                                                     D_797626610_D_797626610_D_664571574==1 ~ "Ducth",
                                             D_797626610_D_797626610_D_163149180==1 ~ "English",
                                             D_797626610_D_797626610_D_192776753==1 ~ "European",
                                             D_797626610_D_797626610_D_733789220==1 ~ "French",
                                             D_797626610_D_797626610_D_418464677==1 ~ "German",
                                             D_797626610_D_797626610_D_859329001==1 ~ "Irish",
                                             D_797626610_D_797626610_D_267472307==1 ~ "Italian",
                                             D_797626610_D_797626610_D_918190932==1 ~ "Norwegian",
                                             D_797626610_D_797626610_D_381749264==1 ~ "Polish",
                                             D_797626610_D_797626610_D_704661219==1 ~ "Scottish",
                                             D_797626610_D_797626610_D_773342525==1 ~ "Spanish",
                                             (D_797626610_D_797626610_D_807835037==1 | !is.na(D_797626610_D_774928994)) ~ "Other",
                                             D_797626610_D_797626610_D_746038746==1 ~ "Prefer Not to Answer",
                                             TRUE   ~ "Skipped this question"))

dt_white_summary <- which_eth %>% group_by(ethnicity) %>%  dplyr::summarize(n=n(), percentage=100*n/nrow(.))  %>% dplyr::ungroup() %>%  dplyr::select(ethnicity, n, percentage)
gtm3_print <- gt::gt(dt_white_summary)

dt_ethnic7 <- dt_white_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("Ethnicity of White Participants of Those Who Completed BOH")) %>% 
  cols_label(n= md("**Number of Participants**"), ethnicity = md("**Answer**"), percentage = md("**Percentage of Participants**")) %>% 
  # summary_rows( groups=F,
  #   column = c(n,percentage),
  #   fns= list(
  #     Sum= ~sum(.)
  #   ), decimals=0) %>%
    grand_summary_rows(columns=c(n, percentage),fns = ~sum(.,na.rm = T))|>
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = ethnicity,
    )
  ) 
tab_footnote(
  dt_ethnic7,
  md("The denomination of this table is all participants who selected this race/ethnicity only, as well as multi-racial participants that selected this race/ethnicity as well as other race/ethnicities. \n Multi-ethnic in this table is defined as participants that selected multiple ethnicity responses."),
  locations = cells_column_labels(columns = n),
  placement = c("left")
)


```


\newpage
## SEX
```{r SGM, warning=FALSE,echo=FALSE}
simple_funct1(D_407056417, "Sex at birth of Participants Who Completed BOH")
```



## Comorbitity 
```{r, include=FALSE}

#somehow answers that don't exist are in the flattened table. Removing
data_tib_m1 <- data_tib_m1 %>%  select(-D_894259747_D_445446905, -D_900541533_D_599063442, -D_874046190_D_870244556, 
                                       -D_543728565_D_251231642, -D_180961306_D_473901019,-D_874709643_D_572909251,
                                       -D_725626004_D_522161060, -D_624179836_D_668434958)

```

### Cardiovascular Disease
```{r MHGroup1, warning=FALSE, echo=FALSE, message=FALSE}


skipped_count <- data_tib_m1 %>%
  rowwise() %>%
  mutate(SkippedAll = all(is.na(c_across(starts_with("D_167101091_D_"))))) %>%
  ungroup() %>%
  filter(SkippedAll) %>%
  summarise(Answer = "Skipped this question", n = n())

cardiov_long <- data_tib_m1 %>%
  pivot_longer(cols = starts_with("D_167101091_D_"), names_to = "AnswerCode", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  mutate(Answer = case_when(
    AnswerCode == "D_167101091_D_698944820" ~ "B-12 Deficiency",
    AnswerCode == "D_167101091_D_838744325" ~ "Coronary Artery",
    AnswerCode == "D_167101091_D_769790179" ~ "Congestive Heart Failure",
    AnswerCode == "D_167101091_D_699553344" ~ "High Cholesterol",
    AnswerCode == "D_167101091_D_700811160" ~ "Heart Attack",
    AnswerCode == "D_167101091_D_336505365" ~ "Abnormal Heart Rhythm",
    AnswerCode == "D_167101091_D_132548932" ~ "Chest Pain",
    AnswerCode == "D_167101091_D_747787163" ~ "Heart Valve Problems",
    AnswerCode == "D_167101091_D_693851465" ~ "High Blood Pressure",
    AnswerCode == "D_167101091_D_512012656" ~ "Blood Clots",
    AnswerCode == "D_167101091_D_619337095" ~ "Stroke",
    AnswerCode == "D_167101091_D_535003378" ~ "None",
    #is.na(AnswerCode) ~ "Skipped this question"
  )) %>%
  count(Answer)

final_count <- bind_rows(cardiov_long, skipped_count)

dt_cardiov_summary <- final_count %>%  mutate(percentage = paste0(round(100*n/nrow(data_tib_m1), digits=2), "%"))

gt_mh1<- dt_cardiov_summary %>%  gt::gt(rowname_col = "row_lab") %>%  
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("MHGROUP1: Diagnosed Cardiovascular Conditions of Participants Who Completed BOH")) %>% 
  cols_label(Answer = md("**Answer**"), n= md("**Number of Participants**"),percentage = md("**Percentage of Participants**")) %>% 
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Answer,
    )
  ) 
tab_footnote(
  gt_mh1,
  md("As this is a select all question, participants may select multiple responses."),
  locations = cells_column_labels(columns = percentage),
  placement = c("left")
)


```



### Respiratory Problems 
```{r MHGroup2, warning=FALSE, echo=FALSE, message=FALSE}

skipped_count <- data_tib_m1 %>%
  rowwise() %>%
  mutate(SkippedAll = all(is.na(c_across(starts_with("D_894259747_D_"))))) %>%
  ungroup() %>%
  filter(SkippedAll) %>%
  summarise(Answer = "Skipped this question", n = n())

respir_long <- data_tib_m1 %>%
  pivot_longer(cols = starts_with("D_894259747_D_"), names_to = "AnswerCode", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  mutate(Answer = case_when(
    AnswerCode == "D_894259747_D_359025642" ~ "Chronic Lung Disease",
    AnswerCode == "D_894259747_D_407340134" ~ "Asthma",
    AnswerCode == "D_894259747_D_427219143" ~ "Hay Fever",
    AnswerCode == "D_894259747_D_535003378" ~ "None"
    #TRUE ~ "Skipped this question"
  )) %>%
  count(Answer)

final_count <- bind_rows(respir_long, skipped_count)

final_count <- final_count %>%
  mutate(Answer = ifelse(is.na(Answer), "Skipped this question", Answer))

dt_respir_summary <- final_count %>%  mutate(percentage = paste0(round(100*n/nrow(data_tib_m1), digits=2), "%"))

gt_mh2<- dt_respir_summary %>%  gt::gt(rowname_col = "row_lab") %>%   
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("MHGROUP2: Diagnosed Respiratory Conditions  of Participants Who Completed BOH")) %>% 
  cols_label(Answer = md("**Answer**"), n= md("**Number of Participants**"),percentage = md("**Percentage of Participants**")) %>% 
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Answer,
    )
  ) 
tab_footnote(
  gt_mh2,
  md("As this is a select all question, participants may select multiple responses."),
  locations = cells_column_labels(columns = percentage),
  placement = c("left")
)

```


### Digestive System Problems 
```{r MHGroup3, warning=FALSE, echo=FALSE, message=FALSE}

skipped_count <- data_tib_m1 %>%
  rowwise() %>%
  mutate(SkippedAll = all(is.na(c_across(starts_with("D_180961306_D_"))))) %>%
  ungroup() %>%
  filter(SkippedAll) %>%
  summarise(Answer = "Skipped this question", n = n())

digest_long <- data_tib_m1 %>%
  pivot_longer(cols = starts_with("D_180961306_D_"), names_to = "AnswerCode", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  mutate(Answer = case_when(
    AnswerCode == "D_180961306_D_406890409" ~ "Esophageal Acid Reflex",
    AnswerCode == "D_180961306_D_704544306" ~ "Barrett's Esophagus",
    AnswerCode == "D_180961306_D_691766591" ~ "Irritable Bowel Syndrome",
    AnswerCode == "D_180961306_D_308645635" ~ "Inflammatory Bowel Disease",
    AnswerCode == "D_180961306_D_731115613" ~ "Diverticulitis or Diverticulosis",
    AnswerCode == "D_180961306_D_567284980" ~ "Ulcerative Colitis",
    AnswerCode == "D_180961306_D_986548173" ~ "Crohn's Disease",
    AnswerCode == "D_180961306_D_285995100" ~ "Celiac Disease",
    AnswerCode == "D_180961306_D_545628561" ~ "Gallstones",
    AnswerCode == "D_180961306_D_709786039" ~ "Liver Cirrhosis",
    AnswerCode == "D_180961306_D_984479578" ~ "Pancreatitis",
    AnswerCode == "D_180961306_D_535003378" ~ "None",
    TRUE ~ "Skipped this question"
  )) %>%
  count(Answer)

final_count <- bind_rows(digest_long, skipped_count)

dt_digest_summary <- final_count %>%  mutate(percentage = paste0(round(100*n/nrow(data_tib_m1), digits=2), "%"))

gt_mh3<- dt_digest_summary %>%  gt::gt(rowname_col = "row_lab") %>%   
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("MHGROUP3: Diagnosed Digestive System Problems  of Participants Who Completed BOH")) %>% 
  cols_label(Answer = md("**Answer**"), n= md("**Number of Participants**"),percentage = md("**Percentage of Participants**")) %>% 
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Answer,
    )
  ) 
tab_footnote(
  gt_mh3,
  md("As this is a select all question, participants may select multiple responses."),
  locations = cells_column_labels(columns = percentage),
  placement = c("left")
)


```


### Thyroid, Dibetes, and Grave's Disease 
```{r MHGroup4, warning=FALSE, echo=FALSE, message=FALSE}

skipped_count <- data_tib_m1 %>%
  rowwise() %>%
  mutate(SkippedAll = all(is.na(c_across(starts_with("D_900541533_D_"))))) %>%
  ungroup() %>%
  filter(SkippedAll) %>%
  summarise(Answer = "Skipped this question", n = n())

thy_db_gv_long <- data_tib_m1 %>%
  pivot_longer(cols = starts_with("D_900541533_D_"), names_to = "AnswerCode", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  mutate(Answer = case_when(
    AnswerCode == "D_900541533_D_726539692" ~ "Thyroid Disorder",
    AnswerCode == "D_900541533_D_158044532" ~ "Diabetes",
    AnswerCode == "D_900541533_D_943054522" ~ "Graves' Disease",
    AnswerCode == "D_900541533_D_535003378" ~ "None",
    #TRUE ~ "Skipped this question"
  )) %>%
  count(Answer)

final_count <- bind_rows(thy_db_gv_long, skipped_count)

dt_thy_db_gv_summary <- final_count %>%  mutate(percentage = paste0(round(100*n/nrow(data_tib_m1), digits=2), "%"))

gt_mh4<- dt_thy_db_gv_summary %>%  gt::gt(rowname_col = "row_lab") %>%   
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("MHGROUP4: Diagnosed with Any of These Conditions  of Participants Who Completed BOH")) %>% 
  cols_label(Answer = md("**Answer**"), n= md("**Number of Participants**"),percentage = md("**Percentage of Participants**")) %>% 
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Answer,
    )
  ) 
tab_footnote(
  gt_mh4,
  md("As this is a select all question, participants may select multiple responses."),
  locations = cells_column_labels(columns = percentage),
  placement = c("left")
)



```



### Kidney 
```{r MHGroup5, warning=FALSE, echo=FALSE, message=FALSE}
skipped_count <- data_tib_m1 %>%
  rowwise() %>%
  mutate(SkippedAll = all(is.na(c_across(starts_with("D_874046190_D_"))))) %>%
  ungroup() %>%
  filter(SkippedAll) %>%
  summarise(Answer = "Skipped this question", n = n())

kidney_long <- data_tib_m1 %>%
  pivot_longer(cols = starts_with("D_874046190_D_"), names_to = "AnswerCode", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  mutate(Answer = case_when(
    AnswerCode == "D_874046190_D_827542780" ~ "Kidney Stones",
    AnswerCode == "D_874046190_D_167238688" ~ "Chronic Kindey Disease",
    AnswerCode == "D_874046190_D_535003378" ~ "None",
    TRUE ~ "Skipped this question"
  )) %>%
  count(Answer)

final_count <- bind_rows(kidney_long, skipped_count)

dt_kidney_summary <- final_count %>%  mutate(percentage = paste0(round(100*n/nrow(data_tib_m1), digits=2), "%"))

gt_mh5<- dt_kidney_summary %>%  gt::gt(rowname_col = "row_lab") %>%   
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("MHGROUP5: Diagnosed with Kidney Conditions of Participants Who Completed BOH")) %>% 
  cols_label(Answer = md("**Answer**"), n= md("**Number of Participants**"),percentage = md("**Percentage of Participants**")) %>% 
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Answer,
    )
  ) 
tab_footnote(
  gt_mh5,
  md("As this is a select all question, participants may select multiple responses."),
  locations = cells_column_labels(columns = percentage),
  placement = c("left")
)

```


### Systemic and Other Problems
```{r MHGroup6, warning=FALSE, echo=FALSE, message=FALSE}
skipped_count <- data_tib_m1 %>%
  rowwise() %>%
  mutate(SkippedAll = all(is.na(c_across(starts_with("D_543728565_D_"))))) %>%
  ungroup() %>%
  filter(SkippedAll) %>%
  summarise(Answer = "Skipped this question", n = n())

systemic_long <- data_tib_m1 %>%
  pivot_longer(cols = starts_with("D_543728565_D_"), names_to = "AnswerCode", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  mutate(Answer = case_when(
    AnswerCode == "D_543728565_D_636030086" ~ "Rheumatoid Arthritis",
    AnswerCode == "D_543728565_D_239687183" ~ "Lupus",
    AnswerCode == "D_543728565_D_134592375" ~ "Gout",
    AnswerCode == "D_543728565_D_535003378" ~ "None",
    TRUE ~ "Skipped this question"
  )) %>%
  count(Answer)

final_count <- bind_rows(systemic_long, skipped_count)

dt_systemic_summary <- final_count %>%  mutate(percentage = paste0(round(100*n/nrow(data_tib_m1), digits=2), "%"))

gt_mh6<- dt_systemic_summary %>%  gt::gt(rowname_col = "row_lab") %>%   
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("MHGROUP6: Diagnosed with Systemic Conditions of Participants Who Completed BOH")) %>% 
  cols_label(Answer = md("**Answer**"), n= md("**Number of Participants**"),percentage = md("**Percentage of Participants**")) %>% 
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Answer,
    )
  ) 
tab_footnote(
  gt_mh6,
  md("As this is a select all question, participants may select multiple responses."),
  locations = cells_column_labels(columns = percentage),
  placement = c("left")
)

```


### Sexually Transmitted Diseases and Infections
```{r MHGroup7, warning=FALSE, echo=FALSE, message=FALSE}
skipped_count <- data_tib_m1 %>%
  rowwise() %>%
  mutate(SkippedAll = all(is.na(c_across(starts_with("D_874709643_D_"))))) %>%
  ungroup() %>%
  filter(SkippedAll) %>%
  summarise(Answer = "Skipped this question", n = n())

STDI_long <- data_tib_m1 %>%
  pivot_longer(cols = starts_with("D_874709643_D_"), names_to = "AnswerCode", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  mutate(Answer = case_when(
    AnswerCode == "D_874709643_D_164910211" ~ "Mono",
    AnswerCode == "D_874709643_D_796616844" ~ "Shingles",
    AnswerCode == "D_874709643_D_436689514" ~ "Chronic Hepatitus B or C",
    AnswerCode == "D_874709643_D_296357383" ~ "Gonorrhea",
    AnswerCode == "D_874709643_D_901077233" ~ "Chlamydia",
    AnswerCode == "D_874709643_D_136956596" ~ "Trich",
    AnswerCode == "D_874709643_D_455776698" ~ "Syphilis",
    AnswerCode == "D_874709643_D_155874194" ~ "Genital Warts",
    AnswerCode == "D_874709643_D_880962432" ~ "HPV",
    AnswerCode == "D_874709643_D_691450854" ~ "HIV/AIDS",
    AnswerCode == "D_874709643_D_535003378" ~ "None", 
    #TRUE ~ "Skipped this question"
  )) %>%
  count(Answer)

final_count <- bind_rows(STDI_long, skipped_count)

final_count <- final_count %>%
  mutate(Answer = ifelse(is.na(Answer), "Skipped this question", Answer))

dt_STDI_summary <- final_count %>%  mutate(percentage = paste0(round(100*n/nrow(data_tib_m1), digits=2), "%"))

gt_mh7<- dt_STDI_summary %>%  gt::gt(rowname_col = "row_lab") %>%   
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("MHGROUP7: Diagnosed Infections or Diseases of Participants Who Completed BOH")) %>% 
  cols_label(Answer = md("**Answer**"), n= md("**Number of Participants**"),percentage = md("**Percentage of Participants**")) %>% 
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Answer,
    )
  ) 
tab_footnote(
  gt_mh7,
  md("As this is a select all question, participants may select multiple responses."),
  locations = cells_column_labels(columns = percentage),
  placement = c("left")
)


```


### Urinary and Reproductive System Problems 
```{r MHGroup8, warning=FALSE, echo=FALSE, message=FALSE}

skipped_count <- data_tib_m1 %>%
  rowwise() %>%
  mutate(SkippedAll = all(is.na(c_across(starts_with("D_725626004_D_"))))) %>%
  ungroup() %>%
  filter(SkippedAll) %>%
  summarise(Answer = "Skipped this question", n = n())

STDI_long <- data_tib_m1 %>%
  pivot_longer(cols = starts_with("D_725626004_D_"), names_to = "AnswerCode", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  mutate(Answer = case_when(
    AnswerCode == "D_725626004_D_509721537" ~ "Uterine Fibroids",
    AnswerCode == "D_725626004_D_863286658" ~ "Endometriosis",
    AnswerCode == "D_725626004_D_386524148" ~ "Polycystic Ovary System",
    AnswerCode == "D_725626004_D_937208760" ~ "Enlarged Prostate",
    AnswerCode == "D_725626004_D_746542057" ~ "Fibrocystic Breast or Benign Breast isease",
    AnswerCode == "D_725626004_D_854945381" ~ "Ductal Carcinoma in situ",
    AnswerCode == "D_725626004_D_535003378" ~ "None", 
  )) %>%
  count(Answer)

final_count <- bind_rows(STDI_long, skipped_count)

final_count <- final_count %>%
  mutate(Answer = ifelse(is.na(Answer), "Skipped this question", Answer))

dt_STDI_summary <- final_count %>%  mutate(percentage = paste0(round(100*n/nrow(data_tib_m1), digits=2), "%"))

gt_mh8<- dt_STDI_summary %>%  gt::gt(rowname_col = "row_lab") %>%   
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("MHGROUP8: Diagnosed Urinary and Reproductive Problems of Participants \n Who Completed BOH")) %>% 
  cols_label(Answer = md("**Answer**"), n= md("**Number of Participants**"),percentage = md("**Percentage of Participants**")) %>% 
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Answer,
    )
  ) 
tab_footnote(
  gt_mh8,
  md("As this is a select all question, participants may select multiple responses."),
  locations = cells_column_labels(columns = percentage),
  placement = c("left"))



```


### Surgery 
```{r MHGroup9, warning=FALSE, echo=FALSE, message=FALSE}

skipped_count <- data_tib_m1 %>%
  rowwise() %>%
  mutate(SkippedAll = all(is.na(c_across(starts_with("D_624179836_D_"))))) %>%
  ungroup() %>%
  filter(SkippedAll) %>%
  summarise(Answer = "Skipped this question", n = n())

STDI_long <- data_tib_m1 %>%
  pivot_longer(cols = starts_with("D_624179836_D_"), names_to = "AnswerCode", values_to = "Selected") %>%
  filter(Selected == 1) %>%
  mutate(Answer = case_when(
    AnswerCode == "D_624179836_D_797189152" ~ "Tonsillectomy",
    AnswerCode == "D_624179836_D_633546100" ~ "Cholecystectomy",
    AnswerCode == "D_624179836_D_866002271" ~ "Appendectomy",
    AnswerCode == "D_624179836_D_118789503" ~ "Liposuction",
    AnswerCode == "D_624179836_D_715563991" ~ "Gastric Bypass",
    AnswerCode == "D_624179836_D_533491176" ~ "Breast Surgery",
    AnswerCode == "D_624179836_D_220755749" ~ "Hysterectomy",
    AnswerCode == "D_624179836_D_465318416" ~ "Tubal Ligation",
    AnswerCode == "D_624179836_D_630100221" ~ "Oophorectomy",
    AnswerCode == "D_624179836_D_692881833" ~ "Salpingectomy",
    AnswerCode == "D_624179836_D_654450030" ~ "Vasectomy",
    AnswerCode == "D_624179836_D_532603425" ~ "Orchiectomy or Orchidectomy",
    AnswerCode == "D_624179836_D_733236542" ~ "Prostatectomy",
    AnswerCode == "D_624179836_D_961987554" ~ "Penectomy",
    AnswerCode == "D_624179836_D_535003378" ~ "None", 
  )) %>%
  count(Answer)

final_count <- bind_rows(STDI_long, skipped_count)

final_count <- final_count %>%
  mutate(Answer = ifelse(is.na(Answer), "Skipped this question", Answer))

dt_STDI_summary <- final_count %>%  mutate(percentage = paste0(round(100*n/nrow(data_tib_m1), digits=2), "%"))

gt_mh9<- dt_STDI_summary %>%  gt::gt(rowname_col = "row_lab") %>%   
  fmt_number(columns = "percentage", decimals = 2) %>% 
  tab_header(title = md("MHGROUP9: Surgeries Had of Participants Who Completed BOH")) %>% 
  cols_label(Answer = md("**Answer**"), n= md("**Number of Participants**"),percentage = md("**Percentage of Participants**")) %>% 
  tab_options(
      stub.font.weight = "bold"
    ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_body(
      columns = Answer,
    )
  ) 
tab_footnote(
  gt_mh9,
  md("As this is a select all question, participants may select multiple responses."),
  locations = cells_column_labels(columns = percentage),
  placement = c("left"))


```
